### 2016-04-07 draft/draft.tex
all results are frozen, started latex outline, ready to write

% This is "sig-alternate.tex" V2.1 April 2013
% This file should be compiled with V2.5 of "sig-alternate.cls" May 2012
%
% This example file demonstrates the use of the 'sig-alternate.cls'
% V2.5 LaTeX2e document class file. It is for those submitting
% articles to ACM Conference Proceedings WHO DO NOT WISH TO
% STRICTLY ADHERE TO THE SIGS (PUBS-BOARD-ENDORSED) STYLE.
% The 'sig-alternate.cls' file will produce a similar-looking,
% albeit, 'tighter' paper resulting in, invariably, fewer pages.
%
% ----------------------------------------------------------------------------------------------------------------
% This .tex file (and associated .cls V2.5) produces:
%       1) The Permission Statement
%       2) The Conference (location) Info information
%       3) The Copyright Line with ACM data
%       4) NO page numbers
%
% as against the acm_proc_article-sp.cls file which
% DOES NOT produce 1) thru' 3) above.
%
% Using 'sig-alternate.cls' you have control, however, from within
% the source .tex file, over both the CopyrightYear
% (defaulted to 200X) and the ACM Copyright Data
% (defaulted to X-XXXXX-XX-X/XX/XX).
% e.g.
% \CopyrightYear{2007} will cause 2007 to appear in the copyright line.
% \crdata{0-12345-67-8/90/12} will cause 0-12345-67-8/90/12 to appear in the copyright line.
%
% ---------------------------------------------------------------------------------------------------------------
% This .tex source is an example which *does* use
% the .bib file (from which the .bbl file % is produced).
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission, you *NEED* to 'insert'
% your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
%
% ================= IF YOU HAVE QUESTIONS =======================
% Questions regarding the SIGS styles, SIGS policies and
% procedures, Conferences etc. should be sent to
% Adrienne Griscti (griscti@acm.org)
%
% Technical questions _only_ to
% Gerald Murray (murray@hq.acm.org)
% ===============================================================
%
% For tracking purposes - this is V2.0 - May 2012

\documentclass{sig-alternate-05-2015}

\begin{document}

% Copyright
\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
\doi{10.475/123_4}

% ISBN
\isbn{123-4567-24-567/08/06}

%Conference
\conferenceinfo{PLDI '13}{June 16--19, 2013, Seattle, WA, USA}

\acmPrice{\$15.00}

%
% --- Author Metadata here ---
\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

\title{ Mining HIV trends in Social Media Data}
%
% You need the command \numberofauthors to handle the 'placement
% and alignment' of the authors beneath the title.
%
% For aesthetic reasons, we recommend 'three authors at a time'
% i.e. three 'name/affiliation blocks' be placed beneath the title.
%
% NOTE: You are NOT restricted in how many 'rows' of
% "name/affiliations" may appear. We just ask that you restrict
% the number of 'columns' to three.
%
% Because of the available 'opening page real-estate'
% we ask you to refrain from putting more than six authors
% (two rows with three columns) beneath the article title.
% More than six makes the first-page appear very cluttered indeed.
%
% Use the \alignauthor commands to handle the names
% and affiliations for an 'aesthetic maximum' of six authors.
% Add names, affiliations, addresses for
% the seventh etc. author(s) as the argument for the
% \additionalauthors command.
% These 'additional authors' will be output/set for you
% without further effort on your part as the last section in
% the body of your article BEFORE References or any Appendices.

\numberofauthors{2} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%
\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
Patrick Breen\\
       \affaddr{The Institute of Bioinformatics}\\
       \affaddr{The University of Georgia}\\
       \affaddr{Athens, Georgia}\\
       \email{pbreen@uga.edu}
% 2nd. author
\alignauthor
Shannon Quinn\titlenote{Corresponding author.}\\
       \affaddr{Institute of Computer Science}\\
       \affaddr{University of Georgia}\\
       \affaddr{Athens, Georgia}\\
       \email{squinn@cs.uga.edu}
}

\maketitle
\begin{abstract}

Here is the abstract.

\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
% TODO: this section
\begin{CCSXML}

\end{CCSXML}

%
% End generated code
%

%
%  Use this command to print the description
%
\printccsdesc

% We no longer use \terms command
%\terms{Theory}

\keywords{ Social Media, Topic Modelling, Document Embedding}

\section{Introduction}

Introduce and literature review of:
1) PrEP, HIV, Twitter

2) Word2Vec, Doc2Vec

3) Dynamic Topic models, Latent Dirichlet allocation

\section{Results}

High level, but more specific than intro, introduce the approach and methods used in this paper here.

\subsection{Word and Document Similarity}

\begin{table}
\centering
\caption{Cosine Similarity to 'prep'}
\begin{tabular}{|l|c|} \hline
Related Word & Cosine Similarity to 'prep'\\ \hline
truvada & 0.836507 \hline
benegative & 0.809185\\ \hline
charliesheen & 0.805214\\ \hline
hivtestweek & 0.797361\\ \hline
sexwork & 0.774867\\ \hline
gettested & 0.765772\\ \hline
hiv & 0.765389\\ \hline
icasa2015 & 0.749948\\ \hline
doingit & 0.749230\\ \hline
aids & 0.738572\\ \hline
\hline\end{tabular}
\end{table}

\begin{table}
\centering
\caption{Cosine Similarity to 'truvada'}
\begin{tabular}{|c|c|} \hline
Related Word & Cosine Similarity to 'truvada'\\ \hline
truvada & 0.836507 \hline
benegative & 0.809185\\ \hline
charliesheen & 0.805214\\ \hline
hivtestweek & 0.797361\\ \hline
sexwork & 0.774867\\ \hline
gettested & 0.765772\\ \hline
hiv & 0.765389\\ \hline
icasa2015 & 0.749948\\ \hline
doingit & 0.749230\\ \hline
aids & 0.738572\\ \hline
\hline\end{tabular}
\end{table}

\subsection{Time Domain}

\begin{figure}
\centering
\includegraphics[height=1in, width=1in]{fly}
\caption{Time domain plot.}
\end{figure}

\subsection{User Timeline Analysis}

\subsubsection{Sentiment Classification}

\section{Conclusions}

Conclusions go here.

Example citation (needed right now to compile):\cite{Lamport:LaTeX}

%\end{document}  % This is where a 'short' article might terminate

%ACKNOWLEDGMENTS are optional
\section{Acknowledgments}

Acknowledgements go here.

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
% no appendix for now...

\subsection{References}

\end{document}

### 2016-04-11 draft/draft.tex
start draft

@@
 
-\title{ Mining HIV trends in Social Media Data}
+\title{ Mining HIV Trends in Social Media Data}
 %
@@
 
-High level, but more specific than intro, introduce the approach and methods used in this paper here.
+1.2 Million tweets related to 'hiv', 'aids', 'truvada', 'prophylaxis', 'imtesting', 'sexwork', 'gay', 'PrEP', were collected from Twitter's streaming API.
+The tweets were restricted to English language, and the collection dates spanned from the 47th week of 2015 to the 7th week of 2016.
+The tweets were lowercased, and cleaned of exotic characters.
+
+Then a variety of analyses were run, each with their own additional preprocessing.
+These analyses sought to determine what things Twitter users were saying about HIV and PrEP, ultimately to determine how to coordinate public health efforts to promote PrEP adoption and adherence for at-risk individuals.
+
+While we excluded non-English tweets, we found that the subset of tweets that had geolocation data available came from around the world.
+Tweets were concentrated on English speaking areas with high population (Figure 1).
+
+\begin{figure}
+\centering
+\includegraphics[height=2.5in, width=3.5in]{map}
+\caption{Plot of geolocated tweets.}
+\end{figure}
 
@@
 
+The first analyses that we performed sought to identify certain keywords, and hashtags that users were users were mentioning in PrEP related contexts.
+Word2Vec and the refinement, Paragraph2Vec are unsupervised machine learning methods that have performed well at embedding natural language in a semantic vector space.
+
+We queried for the top 10 words that had the highest semantic similarity with the word 'truvada' (Table 1). We found many HIV related words, with the specific word 'prep' as the most similar.
+
+Next we preformed Paragraph clustering.
+In this application, a paragraph is equivalent to the text of a tweet.
+In this method, we identify the similarity between tweets, and tweet-level attributes such as hashtags.
+Querying for the Paragraph-Vectors with high similarity to '\#truvada' identifies '\#prep' as the top related hashtag (Table 2).
+Furthermore, we see hashtags related to prevention, and HIV in the results.
+
+The numeric entries in Table 2 correspond to tweet ID numbers.
+The top tweet associated with '\#truvada' has text: "\#girlsbelike if you see this 13 symptoms.
+do hiv test immediately.
+please read".
+This tweet is an HIV symptom related news update, which is representative of a large number of HIV related tweets on Twitter.
+
+The combined results from Word2Vec and Paragraph2Vec demonstrate that we can scan through the Twitter corpus and find words, hashtags, and tweets that are semantically related to our PrEP query terms.
+When HIV public health researchers identify an important keyword, or hashtag, they can quickly use this method to identify related keywords and specific relevant tweets.
+
+% table 1
 \begin{table}
 \centering
-\caption{Cosine Similarity to 'prep'}
+\caption{Cosine Similarity to 'truvada'}
 \begin{tabular}{|l|c|} \hline
-Related Word & Cosine Similarity to 'prep'\\ \hline
-truvada & 0.836507 \hline
-benegative & 0.809185\\ \hline
-charliesheen & 0.805214\\ \hline
+Related Word & Cosine Similarity to 'truvada'\\ \hline
+prep & 0.836507\\ \hline
+charliesheen & 0.774535\\ \hline
+worldaidsday & 0.759242\\ \hline
 hivtestweek & 0.797361\\ \hline
-sexwork & 0.774867\\ \hline
-gettested & 0.765772\\ \hline
-hiv & 0.765389\\ \hline
-icasa2015 & 0.749948\\ \hline
-doingit & 0.749230\\ \hline
-aids & 0.738572\\ \hline
+hiv & 0.744817\\ \hline
+hivaids & 0.730966\\ \hline
+aidsfreefuture & 0.721897\\ \hline
+icasa2015 & 0.713624\\ \hline
+benegative & 0.709129\\ \hline
+martinshkreli & 0.702565\\ \hline
 \hline\end{tabular}
@@
 
+% table 2
 \begin{table}
 \centering
-\caption{Cosine Similarity to 'truvada'}
-\begin{tabular}{|c|c|} \hline
-Related Word & Cosine Similarity to 'truvada'\\ \hline
-truvada & 0.836507 \hline
-benegative & 0.809185\\ \hline
-charliesheen & 0.805214\\ \hline
-hivtestweek & 0.797361\\ \hline
-sexwork & 0.774867\\ \hline
-gettested & 0.765772\\ \hline
-hiv & 0.765389\\ \hline
-icasa2015 & 0.749948\\ \hline
-doingit & 0.749230\\ \hline
-aids & 0.738572\\ \hline
+\caption{Cosine Similarity to '\#truvada'}
+\begin{tabular}{|l|c|} \hline
+Related Hashtag/Tweet & Cosine Similarity to '\#truvada'\\ \hline
+\#prep & 0.740855\\ \hline
+\#hiv & 0.646245\\ \hline
+685501883448963072 & 0.582529\\ \hline
+\#prevention & 0.0.578786\\ \hline
+\#potus & 0.561461\\ \hline
+688733331081527296 & 0.558048\\ \hline
+\#[Japanese "email friend"] & 0.557464\\ \hline
+\#[Japanese "sex friend"] & 0.556990\\ \hline
+\#bbbh & 0.547450\\ \hline
+\#cure & 	0.545497\\ \hline
 \hline\end{tabular}
@@
 
+Next we sought to identify some temporal trends in PrEP related trends.
+We used Dynamic Topic Modelling to identify how certain topics change over time.
+We specified 10 topics and plotted representative words from two of the topics.
+
+In topic 3 we see that the keyword 'prep' remains relatively constant, while 'prevention' and 'truvada' decline over time.
+'hivaids' increases and then decreases in magnitude over the course of the time series (Figure 2).
+These dynamics may indicate short term events in hivaids and PrEP-related conversation on twitter over the time period studied.
+
+We found that topic 5 captured several keywords related to World AIDS Day (Figure 3).
+We can see that all of these terms peak in the 47th week of 2015 and then decline into 2016.
+This correlates well with the actual date of World AIDS Day, December 1st.
+While we aren't specifically interested in World AIDS Day to inform our understanding of PrEP discussion, this observation validates our ability to identify temporal events using DTM.
+
+% figure 2
 \begin{figure}
 \centering
-\includegraphics[height=1in, width=1in]{fly}
-\caption{Time domain plot.}
+\includegraphics[height=2.5in, width=3.5in]{fig1}
+\caption{DTM topic 3 word prevalence over time. Date is YYYY-WW.}
+\end{figure}
+
+% figure 3
+\begin{figure}
+\centering
+\includegraphics[height=2.5in, width=3.5in]{fig2}
+\caption{DTM topic 5 word prevalence over time. Date is YYYY-WW.}
 \end{figure}
@@
 
-\subsubsection{Sentiment Classification}
+Using a Paragraph2Vec analysis, we queried for the top 500 users related to '\#prep' who had at least 200 words in the combined set of tweets in their timeline, up to 3000 tweets.
+The timelines of these users were concatenated into 500 large timeline-documents.
+We then performed LDA on the timeline documents and identified words associated with 10 topics (Table 3).
+We can see some political, news and social media related keywords and colloquialisms in the top 5 words per topic.
+
+A heatmap of Topics vs Users shows the distribution of topic assignment weighting over the 500 users (Figure 4).
+We can see that many of the users are mentioning things assigned to topics 2 and 8.
+Topic 2 appears to be related to certain geographic regions such as 'Nigeria' and 'Syria' that may be especially suffering from HIV.
+Topic 8 contains words such as 'giveaway' and 'startups' indicating that it may be related to social and economic coordination to combat HIV.
+
+% table 3
+\begin{table*}
+\centering
+\caption{Topics Present in 500 HIV/PrEP related Timelines}
+\begin{tabular}{|l|c|c|c|c|c|} \hline
+Topic ID & Word1 & Word2 & Word3 & Word4 & Word5\\ \hline
+0 & 0.002*que & 0.001*por & 0.001*para & 0.001*milan & 0.001*een\\ \hline
+1 & 0.001*yg & 0.001*ini & 0.001*yang & 0.000*aku & 0.000*breakingbad\\ \hline
+2 & 0.001*lmao & 0.001*nigeria & 0.000*syria & 0.000*nigga & 0.000*kca\\ \hline
+3 & 0.000*ntv & 0.000*inspiringthinkn & 0.000*ktnkenya & 0.000*haber & 0.000*tuscany\\ \hline
+4 & 0.003*gurmeetramrahim & 0.001*ang & 0.001*ng & 0.001*ji & 0.001*ako\\ \hline
+5 & 0.001*remedies & 0.000*tw & 0.000*mx & 0.000*rid & 0.000*momlife\\ \hline
+6 & 0.000*flipboard & 0.000*mongolia & 0.000*gettingtozero & 0.000*blackburn & 0.000*occupy\\ \hline
+7 & 0.002*newsbreakslive & 0.002*drudgereport & 0.000*woof & 0.000*und & 0.000*der\\ \hline
+8 & 0.001*giveaway & 0.001*xx & 0.001*photography & 0.001*startups & 0.001*anc\\ \hline
+9 & 0.001*realdonaldtrump & 0.001*lgbt & 0.001*hiring & 0.001*uniteblue & 0.001*tedcruz\\ \hline
+\hline\end{tabular}
+\end{table*}
+
+\begin{figure}
+\centering
+\includegraphics[height=2.5in, width=3.5in]{user_time}
+\caption{Heatmap of Topics vs. Users.}
+\end{figure}
+
+\subsection{Sentiment Classification}
+
+Lastly we sought to create a classification scheme to classify the sentiment of tweets either positive or negative.
+This classifier would allow us to quickly identify positive and negative PrEP related tweets to guide public health efforts.
+We first performed Paragraph2Vec on both our PrEP related tweet corpus and on another tweet corpus that had binary sentiment labels, positive, or negative.
+Then we trained a simple logistic regression classifier on the paragraph-vectors.
+We found that our classifier had an accuracy of 70\% on a validation set.
+
+We then used this classifier to classify our PrEP related tweets into positive or negative labels.
+We reported the most positive, and most negative tweets, by log(probability), on our full dataset, and on tweets that specifically mention either 'prep' or 'truvada' (Table 4).
+It seems that overall the classifier seems to capture the sentiment relatively well, however it clearly fails to recognise the sarcasm present in the most positive overall tweet.
+
+The sentiment results aren't perfect, but they do help us identify positive individials in PrEP and HIV public health such as user @greg0wen.
+The sentiment tweets also let us uncover some of the prevailing stigmas and negative sentiments surrounding PrEP usage.
+
+\begin{table*}
+\centering
+\caption{Example Positive and Negative Sentiment Tweets}
+\begin{tabular}{|l|p{10cm}|} \hline
+Description & Tweet Body\\ \hline
+Most Positive Overall & \#apple hey, apple, with your new headphone hack you are in the gouger camp of shkreli who hiked the hiv drug. nice going.\\ \hline
+Most Positive PrEP & @greg0wen hi greg, I'm a hiv doctor and health writer doing a piece on hivprep could i poss contact you for some info? thanks, verity x\\ \hline
+Most Positive Truvada & great skypeing the john grant just now about bowie , icelandic sagas and truvada! you're right elliot\_rose about the song disappointing!\\ \hline
+
+Most Negative Overall & hiv sucks big time!! and I f\#n hate it!! We're almost there until this one stupid infection brought him back to where he started. sh\#t!!!\\ \hline
+Most Negative PrEP & rt @SamNyembe can we attribute hivaids high rate in kzn to many men having not removed their prepuce? \\ \hline
+Most Negative Truvada & this \#truvada convo has me catching feelings coz majority of men feel 0 responsibility for their reproductive \& sexual health\\ \hline
+
+\hline\end{tabular}
+\end{table*}
 

### 2016-04-13 draft/draft.tex
fix git ignore

@@
 
+ - social impact issues, efficacy, adherence issues, other STDs, Austin (Scott County) Indiana Outbreak as example
+
+ - specifically other papers that did mining Twitter for HIV
+
 2) Word2Vec, Doc2Vec
 
+ - theory and application examples
+
 3) Dynamic Topic models, Latent Dirichlet allocation
+
+- theory and application examples
 
@@
 \centering
-\includegraphics[height=2.5in, width=3.5in]{map}
+\includegraphics[height=2.5in, width=3.5in]{map.pdf}
 \caption{Plot of geolocated tweets.}
@@
 \subsection{Word and Document Similarity}
+
+% show text of relevent tweets from d2v
+
+% talk a bit about pre processing
 
@@
 
-% table 1
+% table 1 - w2v truvada
 \begin{table}
@@
 
-% table 2
+% table 2 - d2v PrEP
 \begin{table}
@@
 
+% show PCA for each table above (remember to mention percent varience)
+
 \subsection{Time Domain}
+
+% PrEP related trends (2 topic time series worth)
+% World AIDs day as validation (1 topic time series)
 
@@
 
+% this will take time to complete
+
 Using a Paragraph2Vec analysis, we queried for the top 500 users related to '\#prep' who had at least 200 words in the combined set of tweets in their timeline, up to 3000 tweets.
@@
 
-% table 3
+% table 3 - top topics
 \begin{table*}
@@
 
+% top positive and negative example tweets
+% report accuracy
+% (potentially) report topic modeling on top postive and negative PrEP tweets
+
 Lastly we sought to create a classification scheme to classify the sentiment of tweets either positive or negative.
@@
 
-The sentiment results aren't perfect, but they do help us identify positive individials in PrEP and HIV public health such as user @greg0wen.
+The sentiment results aren't perfect, but they do help us identify positive individuals in PrEP and HIV public health such as user @greg0wen.
 The sentiment tweets also let us uncover some of the prevailing stigmas and negative sentiments surrounding PrEP usage.

### 2016-04-13 sm_w2v/__main__.py

@@ -79,13 +79,14 @@ def run_clean():
     with open('data/r_twitter.json') as f_in, open('data/c_twitter.json', 'w') as f_out:
         for i, l in enumerate(f_in):
             try:
-                twt = json.loads(l)
+                twt = json.loads(l.strip('\0'))
             except:
-                break
+                continue
 
+            #import pdb;pdb.set_trace()
             if relevant_twt(twt) and (twt['id'] not in ids):
                 ids.add(twt['id'])
-                cln_twt = clean_tweet(twt)
+                cln_twt = clean_tweet(twt, False)
                 f_out.write(json.dumps(cln_twt) + '\n')
     print("done cleaning.")
 

### 2016-04-13 sm_w2v/utils.py

@@ -7,7 +7,7 @@ class MakeIter(object):
     def __iter__(self):
         return self.generator_func(**self.kwargs)
 
-def clean_text(text):
+def clean_text(text, lower):
     clean = re.sub(r'http.*$', '', text)
     clean = re.sub(r'[^a-zA-Z,\.!?\'#0-9\s\-_]', '', clean)
 
@@ -18,16 +18,17 @@ def clean_text(text):
     clean = clean.replace('?', ' ? ')
     clean = clean.replace('!', ' ! ')
 
-    clean = clean.lower()
+    if lower:
+        clean = clean.lower()
     word_list = clean.split()
     words = " ".join(word_list)
     return  words
 
-def clean_tweet(twt):
+def clean_tweet(twt, lower):
     cln_twt = dict()
 
     cln_twt['id'] = twt['id']
-    cln_twt['text'] = clean_text(twt['text'])
+    cln_twt['text'] = clean_text(twt['text'], lower)
     cln_twt['user_id_str'] = twt['user']['id_str']
     cln_twt['tags'] = [twt['user']['name'] + '-*-' + cln_twt['user_id_str']] + \
         ['#' + hashtag['text'].lower() for hashtag in twt['entities']['hashtags']]
@@ -38,15 +39,24 @@ def clean_tweet(twt):
     return cln_twt
 
 def relevant_twt(twt):
-    key_words_lower = ['hiv', 'aids', 'truvada', 'prophylaxis',
-                       'imtesting', 'sexwork', 'gay']
-    key_words_w_case = ['PrEP']
+    key_words_lower = ['truvada', 'prophylaxis', 'imtesting']
+    key_words_w_case = ['PrEP', 'HIV', 'AIDS']
+    utc_offset = twt['user']['utc_offset']
 
+    if not utc_offset:
+        return False
+
+    right_timezone = (utc_offset >= -28800) and (utc_offset <= -18000)
+
+    if not right_timezone:
+        return False
+
+    text = clean_tweet(twt, False)['text'].split()
     for word in key_words_w_case:
-        if word in twt['text']:
+        if word in text:
             return True
 
-    lcase_txt = twt['text'].lower()
+    lcase_txt = [w.lower() for w in text]
 
     for word in key_words_lower:
         if word in lcase_txt:

### 2016-04-13 draft/draft.tex
too tired to continue today

--- 2016-04-07 draft/draft.tex
@@
 
+ - social impact issues, efficacy, adherence issues, other STDs, Austin (Scott County) Indiana Outbreak as example
+
+ - specifically other papers that did mining Twitter for HIV
+
 2) Word2Vec, Doc2Vec
+
+ - theory and application examples
 
@@
 
+- theory and application examples
+
 \section{Results}
 
-High level, but more specific than intro, introduce the approach and methods used in this paper here.
+We sought to determine trends in HIV and PrEP discourse on twitter, to inform and coordinate public health efforts to promote PrEP adoption and adherence for at-risk individuals.
+We collected 624,569 tweets related to 'HIV', 'AIDS', 'truvada', 'prophylaxis', 'imtesting', 'PrEP' from Twitter's streaming API.
+The tweets were restricted to English language, and the collection dates spanned from the 47th week of 2015 to the 14th week of 2016.
+The tweets were and cleaned of exotic characters.
+
+% Prior to topic modelling, tweets were cleaned of high and low frequency words, and transformed by Term Frequency Inverse Document Frequency (TFIDF) processing.
+
+We excluded non-English tweets, and also tweets that did not originate in Contiguous United States time zones.
+A subset of the tweets we collected had geolocation data available.
+We found that tweets were largely concentrated on US and Canadian metro areas (Figure 1).
+
+\begin{figure}
+\centering
+\includegraphics[height=2.5in, width=3.5in]{map}
+\caption{Plot of geolocated tweets.}
+\end{figure}
 
@@
 
+% show text of relevent tweets from d2v
+
+% talk a bit about pre processing
+
+The first analyses that we performed sought to identify certain keywords, hashtags, tweets and users, that were discussing HIV and PrEP related contexts.
+Word2Vec and the related method, Paragraph2Vec are unsupervised machine learning methods that have performed well at embedding natural language in a semantic vector space.
+In our analysis, Word2Vec allows us to determine semantically similar words, while Paragraph2Vec allows us to determine similar tweets, users and hashtags.
+
+% table 1 - w2v PrEP
 \begin{table}
 \centering
-\caption{Cosine Similarity to 'prep'}
+\caption{Cosine Similarity to 'truvada'}
 \begin{tabular}{|l|c|} \hline
-Related Word & Cosine Similarity to 'prep'\\ \hline
-truvada & 0.836507 \hline
-benegative & 0.809185\\ \hline
-charliesheen & 0.805214\\ \hline
-hivtestweek & 0.797361\\ \hline
-sexwork & 0.774867\\ \hline
-gettested & 0.765772\\ \hline
-hiv & 0.765389\\ \hline
-icasa2015 & 0.749948\\ \hline
-doingit & 0.749230\\ \hline
-aids & 0.738572\\ \hline
+Related Word & Cosine Similarity to 'truvada'\\ \hline
+truvada & 0.796666\\ \hline
+Truvada & 0.793999\\ \hline
+DoingIt & 0.738141\\ \hline
+WorldAidsDay & 0.728808\\ \hline
+WorldAIDSDay & 0.720910\\ \hline
+NancyReagan & 0.717667\\ \hline
+NBHAAD & 0.705061\\ \hline
+ART & 0.704300\\ \hline
+hiv & 0.702844\\ \hline
+HLM2016AIDS & 0.698698\\ \hline
 \hline\end{tabular}
@@
 
+% table 2 - d2v PrEP
 \begin{table}
 \centering
-\caption{Cosine Similarity to 'truvada'}
-\begin{tabular}{|c|c|} \hline
-Related Word & Cosine Similarity to 'truvada'\\ \hline
-truvada & 0.836507 \hline
-benegative & 0.809185\\ \hline
-charliesheen & 0.805214\\ \hline
-hivtestweek & 0.797361\\ \hline
-sexwork & 0.774867\\ \hline
-gettested & 0.765772\\ \hline
-hiv & 0.765389\\ \hline
-icasa2015 & 0.749948\\ \hline
-doingit & 0.749230\\ \hline
-aids & 0.738572\\ \hline
+\caption{Cosine Similarity to '\#truvada'}
+\begin{tabular}{|l|c|} \hline
+Related Hashtag/Tweet & Cosine Similarity to '\#truvada'\\ \hline
+\#lgbtmedia16 & 0.739128\\ \hline
+\#hiv & 0.727602\\ \hline
+\#whereisprep & 0.707165\\ \hline
+\#truvada & 0.696113\\ \hline
+\#hivprevention & 0.636068\\ \hline
+702179860983189504 & 0.630055\\ \hline
+user-711275699529764864 & 0.629254\\ \hline
+708519265540907010 & 0.628778\\ \hline
+712032637024653313 & 0.628646\\ \hline
+\#harrogatehour & 	0.628547\\ \hline
 \hline\end{tabular}
@@
 
+% show PCA for each table above (remember to mention percent varience)
+
 \subsection{Time Domain}
 
+% PrEP related trends (2 topic time series worth)
+% World AIDs day as validation (1 topic time series)
+
+Next we sought to identify some temporal trends in PrEP related trends.
+We used Dynamic Topic Modelling to identify how certain topics change over time.
+We specified 10 topics and plotted representative words from two of the topics.
+
+In topic 3 we see that the keyword 'prep' remains relatively constant, while 'prevention' and 'truvada' decline over time.
+'hivaids' increases and then decreases in magnitude over the course of the time series (Figure 2).
+These dynamics may indicate short term events in hivaids and PrEP-related conversation on twitter over the time period studied.
+
+We found that topic 5 captured several keywords related to World AIDS Day (Figure 3).
+We can see that all of these terms peak in the 47th week of 2015 and then decline into 2016.
+This correlates well with the actual date of World AIDS Day, December 1st.
+While we aren't specifically interested in World AIDS Day to inform our understanding of PrEP discussion, this observation validates our ability to identify temporal events using DTM.
+
+% figure 2
 \begin{figure}
 \centering
-\includegraphics[height=1in, width=1in]{fly}
-\caption{Time domain plot.}
+\includegraphics[height=2.5in, width=3.5in]{DTMfig1}
+\caption{DTM topic 3 word prevalence over time. Date is YYYY-WW.}
+\end{figure}
+
+% figure 3
+\begin{figure}
+\centering
+\includegraphics[height=2.5in, width=3.5in]{DTMfig2}
+\caption{DTM topic 5 word prevalence over time. Date is YYYY-WW.}
 \end{figure}
@@
 
-\subsubsection{Sentiment Classification}
+ this will take time to complete (running download, prob 5 days, so approx April 19th)
+
+1 figure (heatmap of users vs topics)
+
+1 table (top words for 10 topics)
+
+\subsection{Sentiment Classification}
+
+% top positive and negative example tweets
+% report accuracy
+% (potentially) report topic modeling on top postive and negative PrEP tweets
+
+Lastly we sought to create a classification scheme to classify the sentiment of tweets either positive or negative.
+This classifier would allow us to quickly identify positive and negative PrEP related tweets to guide public health efforts.
+We first performed Paragraph2Vec on both our PrEP related tweet corpus and on another tweet corpus that had binary sentiment labels, positive, or negative.
+Then we trained a simple logistic regression classifier on the paragraph-vectors.
+We found that our classifier had an accuracy of 70\% on a validation set.
+
+We then used this classifier to classify our PrEP related tweets into positive or negative labels.
+We reported the most positive, and most negative tweets, by log(probability), on our full dataset, and on tweets that specifically mention either 'prep' or 'truvada' (Table 4).
+It seems that overall the classifier seems to capture the sentiment relatively well, however it clearly fails to recognise the sarcasm present in the most positive overall tweet.
+
+The sentiment results aren't perfect, but they do help us identify positive individuals in PrEP and HIV public health such as user @greg0wen.
+The sentiment tweets also let us uncover some of the prevailing stigmas and negative sentiments surrounding PrEP usage.
+
+% do a top positive tweets table
+
+% do a top negative tweets table
 
@@
 
-Acknowledgements go here.
+Acknowledgements (optional) go here.
 

### 2016-04-14 draft/draft.tex
latest commit

@@
 \section{Introduction}
+Example citation (needed right now to compile):\cite{Lamport:LaTeX}
 
@@
 
-We sought to determine trends in HIV and PrEP discourse on twitter, to inform and coordinate public health efforts to promote PrEP adoption and adherence for at-risk individuals.
-We collected 624,569 tweets related to 'HIV', 'AIDS', 'truvada', 'prophylaxis', 'imtesting', 'PrEP' from Twitter's streaming API.
+We sought to determine trends in HIV and PrEP discourse on twitter, to inform and coordinate public health efforts aiming to promote PrEP adoption and adherence for at-risk individuals.
+We collected 624,569 tweets containing at least one of the following words 'HIV', 'AIDS', 'truvada', 'prophylaxis', 'imtesting', 'PrEP' from Twitter's streaming API.
 The tweets were restricted to English language, and the collection dates spanned from the 47th week of 2015 to the 14th week of 2016.
 The tweets were and cleaned of exotic characters.
-
-% Prior to topic modelling, tweets were cleaned of high and low frequency words, and transformed by Term Frequency Inverse Document Frequency (TFIDF) processing.
 
@@
 We found that tweets were largely concentrated on US and Canadian metro areas (Figure 1).
+
+% Prior to topic modelling, tweets were cleaned of high and low frequency words, and transformed by Term Frequency Inverse Document Frequency (TFIDF) processing.
 
@@
 
-% show text of relevent tweets from d2v
-
-% talk a bit about pre processing
-
 The first analyses that we performed sought to identify certain keywords, hashtags, tweets and users, that were discussing HIV and PrEP related contexts.
 Word2Vec and the related method, Paragraph2Vec are unsupervised machine learning methods that have performed well at embedding natural language in a semantic vector space.
-In our analysis, Word2Vec allows us to determine semantically similar words, while Paragraph2Vec allows us to determine similar tweets, users and hashtags.
+In our analysis, Word2Vec allows us to determine semantically similar words to a query word, while Paragraph2Vec allows us to determine similar tweets, users and hashtags to a query hashtag.
+
+% want to do a tSNE plot, but only on things that are relatively dissimilar. For example do HIV, truvada, STDs, testing related, awareness related, ... and throw away or merge labels
 
@@
 
+% might want to explain at a high level how DTM works here
+
 In topic 3 we see that the keyword 'prep' remains relatively constant, while 'prevention' and 'truvada' decline over time.
@@
 
-We found that topic 5 captured several keywords related to World AIDS Day (Figure 3).
+We found that topic 4 captured several keywords related to World AIDS Day (Figure 3).
 We can see that all of these terms peak in the 47th week of 2015 and then decline into 2016.
 This correlates well with the actual date of World AIDS Day, December 1st.
-While we aren't specifically interested in World AIDS Day to inform our understanding of PrEP discussion, this observation validates our ability to identify temporal events using DTM.
+Furthermore,while December 1st is World AIDS day, the whole month of Decemeber is AIDS Awarness month.
+We are clearly seeing the word 'awarness' peak later and last longer that the word 'WorldAIDSDay' implying that it is correlated to the whole month of December.
+While we aren't specifically interested in World AIDS Day, or AIDS awareness month, to inform our understanding of PrEP discussion, this observation validates our ability to identify temporal events using DTM.
+
+% breifly mention what was in the other topics (lots of AIDS related news announcements)
 
@@
 \includegraphics[height=2.5in, width=3.5in]{DTMfig1}
-\caption{DTM topic 3 word prevalence over time. Date is YYYY-WW.}
+\caption{DTM topic 5, word prevalence over time. Date is YYYY-WW.}
 \end{figure}
@@
 \includegraphics[height=2.5in, width=3.5in]{DTMfig2}
-\caption{DTM topic 5 word prevalence over time. Date is YYYY-WW.}
+\caption{DTM topic 5, word prevalence over time. Date is YYYY-WW.}
 \end{figure}
@@
 Then we trained a simple logistic regression classifier on the paragraph-vectors.
-We found that our classifier had an accuracy of 70\% on a validation set.
+We found that our classifier had an accuracy of 69\% on a validation set.
 
@@
 We reported the most positive, and most negative tweets, by log(probability), on our full dataset, and on tweets that specifically mention either 'prep' or 'truvada' (Table 4).
-It seems that overall the classifier seems to capture the sentiment relatively well, however it clearly fails to recognise the sarcasm present in the most positive overall tweet.
 
-The sentiment results aren't perfect, but they do help us identify positive individuals in PrEP and HIV public health such as user @greg0wen.
-The sentiment tweets also let us uncover some of the prevailing stigmas and negative sentiments surrounding PrEP usage.
+% do a top positive tweets table (also with tweet ID and log prob of classification)
 
-% do a top positive tweets table
-
-% do a top negative tweets table
+% do a top negative tweets table (also with tweet ID and log prob of classification)
 
@@
 Conclusions go here.
-
-Example citation (needed right now to compile):\cite{Lamport:LaTeX}
 

### 2016-04-19 draft/draft.tex
work more on draft, notebooks still not quite fixed, actually

@@
 
-Here is the abstract.
+Pre-Exposure Prophylaxis (PrEP) is a recently developed therapy for the prevention of Human Immunodeficiency Virus (HIV).
+The treatment is available as a pill named Truvada and is taken once a day for as much as 99\% protection from infection when exposed to HIV.
+While medically effective, PrEP suffers from high drug costs, HIV-related social stigma, and under-informed health providers and patients.
+This paper contributes a data mining and machine learning strategy that monitors Twitter social media data.
+Our results show that we can identify trends over time, and positive and negative PrEP related tweets.
+These results can be used by public health professionals to inform and protect at risk individuals from HIV.
+
+%These methods may also be useful to identify and preempt HIV outbreaks before they reach epidemic levels.
 
@@
 
+ - High cost of actual drug medication, and unclear health insurance situation.
+
+ - Many health providers do not know about drug.
+
  - specifically other papers that did mining Twitter for HIV
+
+ - Here is a paper that did twitter data mining for flu prediction:
+
+ %http://snap.stanford.edu/soma2010/papers/soma2010_16.pdf
+
+ Talk about how it's harder to get feedback/ account for HIV infections compared with CDC baseline data for flu.
 
@@
 
-We excluded non-English tweets, and also tweets that did not originate in Contiguous United States time zones.
+We excluded non-English tweets, and also tweets that did not originate in contiguous United States time zones.
 A subset of the tweets we collected had geolocation data available.
@@
 
+% TODO work this section Tuesday
+
 The first analyses that we performed sought to identify certain keywords, hashtags, tweets and users, that were discussing HIV and PrEP related contexts.
@@
 \centering
-\caption{Cosine Similarity to 'truvada'}
+\caption{Cosine Similarity to 'PrEP'}
 \begin{tabular}{|l|c|} \hline
-Related Word & Cosine Similarity to 'truvada'\\ \hline
-truvada & 0.796666\\ \hline
-Truvada & 0.793999\\ \hline
-DoingIt & 0.738141\\ \hline
-WorldAidsDay & 0.728808\\ \hline
-WorldAIDSDay & 0.720910\\ \hline
-NancyReagan & 0.717667\\ \hline
-NBHAAD & 0.705061\\ \hline
-ART & 0.704300\\ \hline
-hiv & 0.702844\\ \hline
-HLM2016AIDS & 0.698698\\ \hline
+Related Word & Cosine Similarity to 'PrEP'\\ \hline
 \hline\end{tabular}
@@
 Related Hashtag/Tweet & Cosine Similarity to '\#truvada'\\ \hline
-\#lgbtmedia16 & 0.739128\\ \hline
-\#hiv & 0.727602\\ \hline
-\#whereisprep & 0.707165\\ \hline
-\#truvada & 0.696113\\ \hline
-\#hivprevention & 0.636068\\ \hline
-702179860983189504 & 0.630055\\ \hline
-user-711275699529764864 & 0.629254\\ \hline
-708519265540907010 & 0.628778\\ \hline
-712032637024653313 & 0.628646\\ \hline
-\#harrogatehour & 	0.628547\\ \hline
 \hline\end{tabular}
@@
 
-% PrEP related trends (2 topic time series worth)
-% World AIDs day as validation (1 topic time series)
-
 Next we sought to identify some temporal trends in PrEP related trends.
-We used Dynamic Topic Modelling to identify how certain topics change over time.
-We specified 10 topics and plotted representative words from two of the topics.
+We used Dynamic Topic Modelling (DTM) to identify how certain topics change over time.
+In DTM, documents are grouped in several corpuses that represent different points in time.
+Latent Dirichlet Analysis (LDA) is then performed on each corpus, to extract a topic distribution.
+The posterior distribution from time $t_n$ is used as the prior for time $t_{n+1}$.
+We specified 10 topics and used each week's worth of tweets over a 30 week period as our time points.
 
@@
 
-In topic 3 we see that the keyword 'prep' remains relatively constant, while 'prevention' and 'truvada' decline over time.
-'hivaids' increases and then decreases in magnitude over the course of the time series (Figure 2).
+We identified two topics that showed relevant trends.
+In topic 5 we see that the keyword 'prep' remains relatively constant, while 'prevention' and 'truvada' decline over time.
+'hivaids' increases and then decreases in magnitude over the course of the time series (Figure 3).
 These dynamics may indicate short term events in hivaids and PrEP-related conversation on twitter over the time period studied.
 
-We found that topic 4 captured several keywords related to World AIDS Day (Figure 3).
-We can see that all of these terms peak in the 47th week of 2015 and then decline into 2016.
-This correlates well with the actual date of World AIDS Day, December 1st.
-Furthermore,while December 1st is World AIDS day, the whole month of Decemeber is AIDS Awarness month.
-We are clearly seeing the word 'awarness' peak later and last longer that the word 'WorldAIDSDay' implying that it is correlated to the whole month of December.
-While we aren't specifically interested in World AIDS Day, or AIDS awareness month, to inform our understanding of PrEP discussion, this observation validates our ability to identify temporal events using DTM.
-
-% breifly mention what was in the other topics (lots of AIDS related news announcements)
-
-% figure 2
+% figure 3
 \begin{figure}
@@
 
-% figure 3
+We found that topic 4 captured several keywords related to World AIDS Day (Figure 4).
+We can see that all of these terms peak in the 47th week of 2015 and then decline into 2016.
+This correlates well with the actual date of World AIDS Day, December 1st.
+Furthermore,while December 1st is World AIDS day, the whole month of December is AIDS Awareness month.
+We are clearly seeing the word 'awareness' peak later and last longer that the word 'WorldAIDSDay' implying that it is correlated to the whole month of December.
+While we aren't specifically interested in World AIDS Day, or AIDS awareness month, to inform our understanding of PrEP discussion, this observation validates our ability to identify temporal events using DTM.
+
+% figure 4
 \begin{figure}
@@
 
+These results demonstrate our ability to extract relevant HIV and PrEP related information from twitter that accurately captures time-dependant fluctuations.
+Public health professionals should be able to monitor these temporal trends to determine the relative interest in PrEP related social media discourse.
+This could lead to a system for early detection of HIV outbreak detection, or other serious developments.
+
 \subsection{User Timeline Analysis}
 
- this will take time to complete (running download, prob 5 days, so approx April 19th)
+% TODO work this section (re download and re-run) Tuesday
 
-1 figure (heatmap of users vs topics)
+We wanted to identify what Twitter users that mentioned PrEP were discussing in their other tweets.
+We identified users that were most similar to PrEP according to our Paragraph2Vec results, and downloaded their most recent 3000 tweets.
+We took the top 300 users that had at least 200 words in the combined tweets of their tweet history.
+For each user, we concatenated all of their tweets, and performed LDA topic modelling on the set of user-time line documents.
 
-1 table (top words for 10 topics)
+When we examine a clustermap of users vs.
+topics, we see that the majority of these users are discussing topics 5, 1, and 4 (Figure 5).
+When we look up the top words in the corresponding topic distributions, we see that topics 1 and 4 seem to be related to republican party politics.
+
+% figure 5
+\begin{figure}
+\centering
+\includegraphics[height=2.5in, width=3.5in]{user_timeline_clustermap}
+\caption{Clustermap of users vs. topics for the top 300 users related to PrEP.}
+\end{figure}
+
+% table 3
+\begin{table*}
+\centering
+\caption{Topic modeling on PrEP-related users\' timelines.}
+\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|c|} \hline
+Topic Number & Word 0 & Word 1 & Word 2 & Word 3 & Word 4 & Word 5 & Word 6 & Word 7 & Word 8 & Word 9\\ \hline
+0 & hivaids & condoms & bitcoin & stigma & cdcstd & kanyewest & nyhaad & entrepreneur & realestate & blacklivesmatter\\ \hline
+1 & ang & ng & tcot & ako & sa & ko & pjnet & realdonaldtrump & gopdebate & cruzcrew\\ \hline
+2 & fertility & infertility & meme & mxico & rp & deactivate & rail & roc & offensive & feedly\\ \hline
+3 & colombia & pozlivingbc & fe & repostapp & sprite & bccfe & thewalkingdead & npinchat & interior & wellness\\ \hline
+4 & businessinsider & stacks & noh & teaparty & sk & holi & alzheimers & caregiver & asa & guru\\ \hline
+5 & armenia & wordpress & georgia & topping & lgbtqia & yah & faction & checkout & narendramodi & examination\\ \hline
+6 & knitting & lista & naral & gust & worldbank & bigdata & haiku & vdeo & mhealth & hah\\ \hline
+7 & nigga & niggas & bernie & lmao & nhsengland & bitches & bae & uniteblue & il & gop\\ \hline
+8 & socialmedia & seo & socialmediamarketing & der & und & entrepreneur & ist & nowplaying & foxbusiness & enews\\ \hline
+9 & collage & mileycyrus & undetectable & ddlovato & casa & cnet & qotd & vacations & nashville & heros \\ \hline
+
+\hline\end{tabular}
+\end{table*}
+
+Together these results suggest that PrEP users are involved in political discussions, and are internationally focused.
 
@@
 
-% top positive and negative example tweets
-% report accuracy
-% (potentially) report topic modeling on top postive and negative PrEP tweets
+% TODO work this section Tuesday (give example positive and negative tweets)
 
-Lastly we sought to create a classification scheme to classify the sentiment of tweets either positive or negative.
-This classifier would allow us to quickly identify positive and negative PrEP related tweets to guide public health efforts.
-We first performed Paragraph2Vec on both our PrEP related tweet corpus and on another tweet corpus that had binary sentiment labels, positive, or negative.
-Then we trained a simple logistic regression classifier on the paragraph-vectors.
-We found that our classifier had an accuracy of 69\% on a validation set.
+Lastly we trained a classifier to classify the sentiment of HIV and PrEP related tweets either positive or negative.
+This classifier would allow public health professionals to quickly identify positive and negative PrEP related tweets to guide HIV prevention efforts.
+We obtained a set of 1.6 million tweets with sentiment labels, either positive or negative from Sanders Analytics (http://www.sananalytics.com/lab/twitter-sentiment/).
+Then we trained a simple logistic regression classifier on 1.2 million paragraph-vectors from the sentiment dataset.
+We found that our classifier had an accuracy of 69\% using a portion of the sentiment tweets not used in training, as a validation set.
+
+ We chose to use a relatively simple classifier model (logistic regression) and stop training at
 
@@
 
-Conclusions go here.
+- Moving towards HIV outbreak prediction.
+
+- Automatically identifying PrEP adoption/adherence sentiment in US population.
 

### 2016-04-19 draft/draft.tex
finally locked in all results, can now focus entirely on writing a draft, cool

@@
 This paper contributes a data mining and machine learning strategy that monitors Twitter social media data.
-Our results show that we can identify trends over time, and positive and negative PrEP related tweets.
-These results can be used by public health professionals to inform and protect at risk individuals from HIV.
+Our results show that we can identify PrEP and HIV discussion trends over time, and positive and negative PrEP related tweets.
+These results can be used by public health professionals to inform and protect at-risk individuals from HIV.
 
@@
 
-We excluded non-English tweets, and also tweets that did not originate in contiguous United States time zones.
+We excluded tweets that did not originate in contiguous United States time zones.
 A subset of the tweets we collected had geolocation data available.
 We found that tweets were largely concentrated on US and Canadian metro areas (Figure 1).
-
-% Prior to topic modelling, tweets were cleaned of high and low frequency words, and transformed by Term Frequency Inverse Document Frequency (TFIDF) processing.
 
@@
 
-% TODO work this section Tuesday
-
-The first analyses that we performed sought to identify certain keywords, hashtags, tweets and users, that were discussing HIV and PrEP related contexts.
+The first analysis that we performed sought to identify certain keywords, hashtags, tweets and users, that were discussed in HIV and PrEP related contexts.
 Word2Vec and the related method, Paragraph2Vec are unsupervised machine learning methods that have performed well at embedding natural language in a semantic vector space.
 In our analysis, Word2Vec allows us to determine semantically similar words to a query word, while Paragraph2Vec allows us to determine similar tweets, users and hashtags to a query hashtag.
-
-% want to do a tSNE plot, but only on things that are relatively dissimilar. For example do HIV, truvada, STDs, testing related, awareness related, ... and throw away or merge labels
 
@@
 \centering
-\caption{Cosine Similarity to 'PrEP'}
+\caption{Cosine Similarity to word-vector 'PrEP'}
 \begin{tabular}{|l|c|} \hline
 Related Word & Cosine Similarity to 'PrEP'\\ \hline
+truvada & 0.796666\\ \hline
+DoingIt & 0.738141\\ \hline
+WorldAIDSDay & 0.720910\\ \hline
+NancyReagan & 0.717667\\ \hline
+NBHAAD & 0.705061\\ \hline
+ART & 0.704300\\ \hline
+HLM2016AIDS & 0.698698\\ \hline
+ICASA2015 & 0.693117\\ \hline
+HIV & 0.692860\\ \hline
+OneConversation & 0.688427\\ \hline
 \hline\end{tabular}
@@
 \centering
-\caption{Cosine Similarity to '\#truvada'}
+\caption{Cosine Similarity to doc-vector '\#PrEP'}
 \begin{tabular}{|l|c|} \hline
-Related Hashtag/Tweet & Cosine Similarity to '\#truvada'\\ \hline
+Related Hashtag/Tweet & Cosine Similarity to '\#PrEP'\\ \hline
+\#lgbtmedia16 & 0.739128\\ \hline
+\#hiv & 	0.727602 \\ \hline
+\#whereisprep & 0.707165 \\ \hline
+\#truvada & 0.696113 \\ \hline
+\#hivprevention & 0.636068 \\ \hline
+tweet-702179860983189504 & 0.630055\\ \hline
+user-711275699529764864 & 0.629254\\ \hline
+tweet-708519265540907010 & 0.628778 \\ \hline
+tweet-712032637024653313 & 0.628646 \\ \hline
+\#harrogatehour & 0.628547 \\ \hline
 \hline\end{tabular}
@@
 
-% show PCA for each table above (remember to mention percent varience)
+% example tweets that show up related to Prep that are informative, and misinformative:
+% tweet-702179860983189504 "#StoneColdVideoTODAY if You see this 13 symptoms. Do HIV Test Immediately. Must Read"
+% tweet-708519265540907010 "Checkout why PrEP is hurting the cause amp # JoinTheConversation # LGBTQIA"
+
+% figure 3
+\begin{figure*}
+\centering
+\includegraphics[height=4in, width=6in]{tSNE_word}
+\caption{tSNE plot of relevant word-vectors}
+\end{figure*}
 
@@
 We used Dynamic Topic Modelling (DTM) to identify how certain topics change over time.
-In DTM, documents are grouped in several corpuses that represent different points in time.
+In DTM, documents are grouped in several corpuses that represent successive points in time.
 Latent Dirichlet Analysis (LDA) is then performed on each corpus, to extract a topic distribution.
-The posterior distribution from time $t_n$ is used as the prior for time $t_{n+1}$.
-We specified 10 topics and used each week's worth of tweets over a 30 week period as our time points.
-
-% might want to explain at a high level how DTM works here
+The posterior topic distribution from time $t_n$ is used as the prior for time $t_{n+1}$.
+This lets the model determine a topic model for each time point that is dependent both on the set of tweets from that time point, and on the time point's document distribution.
+We specified 10 topics and used each week's worth of tweets, over a 30 week period from the 47th week of 2015 to the 14th week of 2016, as our time points.
 
 We identified two topics that showed relevant trends.
-In topic 5 we see that the keyword 'prep' remains relatively constant, while 'prevention' and 'truvada' decline over time.
-'hivaids' increases and then decreases in magnitude over the course of the time series (Figure 3).
-These dynamics may indicate short term events in hivaids and PrEP-related conversation on twitter over the time period studied.
+In topic 5 we see that the keyword 'PrEP' increases over time, while 'prevention', 'drug' and 'risk' remain constant (Figure 3).
+The term 'pill', also from topic 5, declines overtime.
+These dynamics may indicate that PrEP discussion is becoming more prevalent.
+Other HIV prevention related words such as 'pill', 'prevention' and 'drug' which serve as a form of negative controls.
+They are related to PrEP semantically, and are thus in the same topic.
+Yet the fact that they are not increasing, shows us that the increase in PrEP discussion is PrEP-specific.
+
+However, it is hard to tell from these data though, whether the increased level of PrEP discussion is leading to increased levels of informed patients, medical providers, and adherence.
+It is possible that stigma, and misinformation is leading to greater levels of PrEP discussion on twitter.
+We will get more specific, granular understanding of the PrEP discourse in our sentiment analysis section below.
 
@@
 \includegraphics[height=2.5in, width=3.5in]{DTMfig1}
-\caption{DTM topic 5, word prevalence over time. Date is YYYY-WW.}
+\caption{DTM topic 5 (PrEP related topic) word prevalence over time. Date is YYYY-WW.}
 \end{figure}
 
+We found at least one other DTM topic that showed interesting behaviour.
 We found that topic 4 captured several keywords related to World AIDS Day (Figure 4).
-We can see that all of these terms peak in the 47th week of 2015 and then decline into 2016.
+We can see that 'WorldAIDSDay', and 'can' peak in the 47th week of 2015 and then decline into 2016.
 This correlates well with the actual date of World AIDS Day, December 1st.
-Furthermore,while December 1st is World AIDS day, the whole month of December is AIDS Awareness month.
-We are clearly seeing the word 'awareness' peak later and last longer that the word 'WorldAIDSDay' implying that it is correlated to the whole month of December.
-While we aren't specifically interested in World AIDS Day, or AIDS awareness month, to inform our understanding of PrEP discussion, this observation validates our ability to identify temporal events using DTM.
+Furthermore, while December 1st is World AIDS day, the whole month of December is AIDS Awareness Month.
+We can clearly see the words 'raise' and 'awareness' peak later and last longer that the word 'WorldAIDSDay' implying that it is correlated to the whole month of December.
+While our PrEP investigation isn't specifically interested in World AIDS Day, or AIDS awareness month, this observation validates our ability to accurately identify temporal events using DTM.
 
@@
 \includegraphics[height=2.5in, width=3.5in]{DTMfig2}
-\caption{DTM topic 5, word prevalence over time. Date is YYYY-WW.}
+\caption{DTM topic 4 (WorldAIDSDay related topic) word prevalence over time. Date is YYYY-WW.}
 \end{figure}
 
-These results demonstrate our ability to extract relevant HIV and PrEP related information from twitter that accurately captures time-dependant fluctuations.
-Public health professionals should be able to monitor these temporal trends to determine the relative interest in PrEP related social media discourse.
-This could lead to a system for early detection of HIV outbreak detection, or other serious developments.
+Together, the DTM results demonstrate our ability to extract relevant HIV and PrEP related information from twitter that accurately captures time-dependant fluctuations.
+Public health professionals should be able to monitor these temporal trends to determine the relative interest in PrEP, and other HIV related keywords as they are discussed over time.
+This method could even lead to a system for early detection of HIV outbreaks, or other serious developments.
 
 \subsection{User Timeline Analysis}
+
+% Prior to topic modelling, tweets were cleaned of high and low frequency words, and transformed by Term Frequency Inverse Document Frequency (TFIDF) processing.
 
@@
 % figure 5
-\begin{figure}
+\begin{figure*}
 \centering
@@
 \caption{Clustermap of users vs. topics for the top 300 users related to PrEP.}
-\end{figure}
+\end{figure*}
 
@@
 \centering
-\caption{Topic modeling on PrEP-related users\' timelines.}
+\caption{Topic modeling on PrEP-related users' timelines.}
 \begin{tabular}{|l|c|c|c|c|c|c|c|c|c|c|} \hline
-Topic Number & Word 0 & Word 1 & Word 2 & Word 3 & Word 4 & Word 5 & Word 6 & Word 7 & Word 8 & Word 9\\ \hline
-0 & hivaids & condoms & bitcoin & stigma & cdcstd & kanyewest & nyhaad & entrepreneur & realestate & blacklivesmatter\\ \hline
-1 & ang & ng & tcot & ako & sa & ko & pjnet & realdonaldtrump & gopdebate & cruzcrew\\ \hline
-2 & fertility & infertility & meme & mxico & rp & deactivate & rail & roc & offensive & feedly\\ \hline
-3 & colombia & pozlivingbc & fe & repostapp & sprite & bccfe & thewalkingdead & npinchat & interior & wellness\\ \hline
-4 & businessinsider & stacks & noh & teaparty & sk & holi & alzheimers & caregiver & asa & guru\\ \hline
-5 & armenia & wordpress & georgia & topping & lgbtqia & yah & faction & checkout & narendramodi & examination\\ \hline
-6 & knitting & lista & naral & gust & worldbank & bigdata & haiku & vdeo & mhealth & hah\\ \hline
-7 & nigga & niggas & bernie & lmao & nhsengland & bitches & bae & uniteblue & il & gop\\ \hline
-8 & socialmedia & seo & socialmediamarketing & der & und & entrepreneur & ist & nowplaying & foxbusiness & enews\\ \hline
-9 & collage & mileycyrus & undetectable & ddlovato & casa & cnet & qotd & vacations & nashville & heros \\ \hline
-
+Topic Number & Word 0 & Word 1 & Word 2 & Word 3 & Word 4 & Word 5\\ \hline
+0 & wordpress & dentists & rb & aquarius & faction & reconnect\\ \hline
+1 & empirefox & crooks & csr & payroll & ch & allin\\ \hline
+2 & vdeo & pra & gust & lgbtqia & rail & undetectable\\ \hline
+3 & hivaids & cdcstd & stigma & blacklivesmatter & realestate & getcovered\\ \hline
+4 & nigga & niggas & realdonaldtrump & lmao & cruz & gop\\ \hline
+5 & fertility & infertility & armenia & collage & nig & deactivate\\ \hline
+6 & packaging & buenas & amigo & bu & birthcontrol & reservations \\ \hline
+7 & mga & ka & socialmedia & lang & entrepreneur & naman\\ \hline
+8 & infosec & bigdata & multimedia & stl & fx & malware\\ \hline
+9 & nhsengland & sosa & tw & knitting & worldbank & thtorguk\\ \hline
 \hline\end{tabular}
@@
 % do a top positive tweets table (also with tweet ID and log prob of classification)
+% table 4
+\begin{table*}
+\centering
+\caption{Positive Sentiment Tweets.}
+\begin{tabular}{|p{2cm}|p{12cm}|} \hline
+Category & Text\\ \hline
+General & "RT TOPublicHealth The Works provides testing for HIV anonymous \& rapid test available . Call 416-392-0520 for more info"\\ \hline
+General & "RT FCAA ejaforg announced 5.4 million in grants to support orgs addressing \#HIV in new \& innovative ways!"\\ \hline
+General & "RT HillaryClinton A note on the fight against HIV and AIDS and the people who really started the conversation."\\ \hline
+
+PrEP specific & "He won't use condoms because intimacy means more than his health. but he's discovered PrEP. thank goodness."\\ \hline
+PrEP specific & "PrEP Queensland Aids Council, \#HIV Foundation, Queensland."\\ \hline
+PrEP specific & "RT JDatTheBody At the core of our programs is belief that young ppl can succeed in take PrEP for HIV prevention. \#NHPC2015"\\ \hline
+
+Truvada specific & "RT CDC\_HIVAIDS Expanding testing, treatment, \& \#PrEP could prevent up to 185k new \#HIV infections"\\ \hline
+Truvada specific & "Another reason 4 \#Ireland \& \#UK 2 immediately approve \#truvada \& \#PrEP 2 stop \#HIV infections . arleavitt AodhanORiordain MerchantsQuayIR"\\ \hline
+Truvada specific & "RT EvanJPeterson For \#worldAIDSday my early \#PrEP arcticle in strangerslog, art by leviathanleague \#hiv \#truvada \#truvadawhore"\\ \hline
+
+\hline\end{tabular}
+\end{table*}
 
 % do a top negative tweets table (also with tweet ID and log prob of classification)
+% table 5
+\begin{table*}
+\centering
+\caption{Negative Sentiment Tweets.}
+\begin{tabular}{|p{2cm}|p{12cm}|} \hline
+Category & Text\\ \hline
+General & "Also, how fucking vile of Hillary to say. Reagan did fucking NOTHING during the AIDS epidemic until it was too late. What a stupid old hag."\\ \hline
+General & "I wonder why he beat her ass when she was tryna leave like she wasn't gone be running back when she found out she had HIV \& nobody want her"\\ \hline
+General & "Aaannd. Hillary Clinton breathes a sigh of relief that Twitter has left its outrage of her AIDS comments behind to tend to Drumpf debacle."\\ \hline
+
+PrEP specific & "RT gaston\_croupier \#Truvada patent's not expired yet but it is sold online as a generic drug? There's something rotten in internet \#PrEP h"\\ \hline
+PrEP specific & "Equality\_MI Syph \& Hep C have gone up 550 in Gay Men bc many feel tht bc they're on PrEP, they don't need condoms. HIV isn't the only STI."\\ \hline
+PrEP specific & "Xaviom8 in interviews he says he was adherent. strain was highly resistant, and Truvada wouldn't have blocked it anyways. PrEP didn't fail."\\ \hline
+
+Truvada specific & "not surprised at all that someone got HIV on truvada. people get pregnant on birth control. tomato-condoms are still important-tomahto"\\ \hline
+Truvada specific & "Now reading that truvada does not protect against certain strains of the HIV virus. Yet people want to take that risk.."\\ \hline
+Truvada specific & "I think I have conjunctivitis unless truvada cured it overnight cuz im not feeling as horrible today as last night"\\ \hline
+
+\hline\end{tabular}
+\end{table*}
+
+% there is viable information in the LDA topic modeling on positive and negative tweets
 

### 2016-04-21 draft/draft.tex
today's update for the draft

@@
 While medically effective, PrEP suffers from high drug costs, HIV-related social stigma, and under-informed health providers and patients.
-This paper contributes a data mining and machine learning strategy that monitors Twitter social media data.
-Our results show that we can identify PrEP and HIV discussion trends over time, and positive and negative PrEP related tweets.
+This paper contributes a data mining and machine learning strategy that monitors Twitter social media data to determine HIV and PrEP discussion trends.
+Our results show that we can identify PrEP and HIV discussion dynamics over time, and positive and negative PrEP-related tweets.
 These results can be used by public health professionals to inform and protect at-risk individuals from HIV.
@@
 
- Talk about how it's harder to get feedback/ account for HIV infections compared with CDC baseline data for flu.
+ Talk about how it's harder to get feedback/ account for HIV infections compared with CDC baseline data for flu. Talk about twitter-specifc issues such as bots and slang.
 
@@
 
+We trained a Word2Vec model, and queried for the top 10 word-vectors related to the term PrEP (Table 1).
+We found several HIV related events, WorldAIDSDay, HLM2016AIDS, ICASA2015, as well as the PrEP drug Truvada, and the term HIV.
+In addition, we found the acronym ART which refers to Anti-Retroviral Therapy.
+DoingIt, and OneConversation, are ongoing efforts led by the Center for Disease Control (CDC) to spread awareness and reduce the spread of HIV.
+NBHAAD is an organization that is committed to increasing awareness for HIV within the Black community (TODO: look up if there is some special connection between HIV and Black community).
+Nancy Reagan, who died in early 2016, was mentioned in conjunction with her efforts to combat HIV in the 1980's.
+Together these results show us a high-level view of the important components of the national PrEP conversation on Twitter.
+
 % table 1 - w2v PrEP
@@
 \end{table}
+
+Doc2Vec allows us to identify the top users, tweets, and hashtags associated with \#prep.
+Note that on Twitter, hashtags are not case sensitive.
+Querying for the top 10 document-level entities associated with \#prep, we again see several PrEP and HIV related hashtags including \#hiv, \#hivprevention, \#truvada, and \#whereisprep.
+We also see a LGBT-related hashtag, \#lgbtmedia16, which indicates a distinct awareness of PrEP in the Gay community.
+This may reflect the known levels of HIV transmission in gay men (TODO: cite something here).
+
+Interestingly, we also found 3 tweets and 1 user in the top 10 doc2vec results for \#prep.
+Tweet 702179860983189504 has content spreading HIV prevention awareness: "\#StoneColdVideoTODAY if You see this 13 symptoms.
+Do HIV Test Immediately.
+Must Read".
+Conversely tweet 708519265540907010 has content that calls into doubt the usefulness of PrEP: "Checkout why PrEP is hurting the cause \& \#JoinTheConversation \#LGBTQIA".
+User 711275699529764864 is a twitter spam bot with no particular connection to PrEP.
+Together the Doc2Vec results show that we can monitor and identify PrEP-related hashtags and tweets.
+The most PrEP related tweets, the content of the above tweets were popular on twitter over the period of data that we collected.
+When they were retweeted, doc2vec weighted them more highly similar to \#prep.
+Thus with this method we demonstrate a way to identify and monitor the most viral tweets related to PrEP.
+As the discussion changes, public health professionals can use this information to quickly identify the most important viral sentiment in the online PrEP conversation.
 
@@
 
-% example tweets that show up related to Prep that are informative, and misinformative:
-% tweet-702179860983189504 "#StoneColdVideoTODAY if You see this 13 symptoms. Do HIV Test Immediately. Must Read"
-% tweet-708519265540907010 "Checkout why PrEP is hurting the cause amp # JoinTheConversation # LGBTQIA"
+Finally we wanted to visualize the relative similarities of these PrEP-related keywords in a low dimensional space.
+We took several keywords that we had identified in our PrEP related queries, along with other HIV-prevention related terms, and visualised their word-vectors in 2 dimensions using tSNE (Figure 2)(TODO: citation for tSNE.).
+
+We several trends.
+Notably the pharmaceutical based HIV therapies all cluster together (ART, PrEP, truvada), the AIDS awareness events cluster together (WorldAIDSDay, NBHAAD) and so do the sexually transmitted disease keywords (HIV, AIDS, STD).
+These results may provide another mechanism for researchers to visualize and identify relevant trends in PrEP-related keywords.
 
@@
 We identified users that were most similar to PrEP according to our Paragraph2Vec results, and downloaded their most recent 3000 tweets.
-We took the top 300 users that had at least 200 words in the combined tweets of their tweet history.
+We took the top 400 users that had at least 200 words in the combined tweets of their tweet history.
 For each user, we concatenated all of their tweets, and performed LDA topic modelling on the set of user-time line documents.
@@
 \includegraphics[height=2.5in, width=3.5in]{user_timeline_clustermap}
-\caption{Clustermap of users vs. topics for the top 300 users related to PrEP.}
+\caption{Clustermap of users vs. topics for the top 400 users related to PrEP.}
 \end{figure*}
@@
 PrEP specific & "RT gaston\_croupier \#Truvada patent's not expired yet but it is sold online as a generic drug? There's something rotten in internet \#PrEP h"\\ \hline
-PrEP specific & "Equality\_MI Syph \& Hep C have gone up 550 in Gay Men bc many feel tht bc they're on PrEP, they don't need condoms. HIV isn't the only STI."\\ \hline
+PrEP specific & "Equality\_MI Syph \& Hep C have gone up 550\% in Gay Men bc many feel tht bc they're on PrEP, they don't need condoms. HIV isn't the only STI."\\ \hline
 PrEP specific & "Xaviom8 in interviews he says he was adherent. strain was highly resistant, and Truvada wouldn't have blocked it anyways. PrEP didn't fail."\\ \hline
@@
 - Automatically identifying PrEP adoption/adherence sentiment in US population.
+
+- A lot of information on twitter is from bots, they only cost \$ per bot.
+This along with the character limit and slang makes twitter hard to use, but we've shown that it can be used.
+In fact twitter bots are slowly making twitter unusable because free advertising and marketing.
+Maybe in a future project we make twitter bots to spread information about PrEP.
 

### 2016-04-23 draft/draft.tex
finish results first draft

@@
 \documentclass{sig-alternate-05-2015}
+
+\usepackage [english]{babel}
+\usepackage [autostyle, english = american]{csquotes}
+\MakeOuterQuote{"}
 
@@
 While medically effective, PrEP suffers from high drug costs, HIV-related social stigma, and under-informed health providers and patients.
-This paper contributes a data mining and machine learning strategy that monitors Twitter social media data to determine HIV and PrEP discussion trends.
+This paper describes a data mining and machine learning strategy that monitors Twitter social media data to determine HIV and PrEP discussion trends.
 Our results show that we can identify PrEP and HIV discussion dynamics over time, and positive and negative PrEP-related tweets.
@@
 \section{Introduction}
-Example citation (needed right now to compile):\cite{Lamport:LaTeX}
+Example citation (needed right now to compile):
 
@@
 
-We sought to determine trends in HIV and PrEP discourse on twitter, to inform and coordinate public health efforts aiming to promote PrEP adoption and adherence for at-risk individuals.
+We sought to determine trends in HIV and PrEP discourse on twitter to inform and coordinate public health efforts aiming to promote PrEP adoption and adherence for at-risk individuals.
 We collected 624,569 tweets containing at least one of the following words 'HIV', 'AIDS', 'truvada', 'prophylaxis', 'imtesting', 'PrEP' from Twitter's streaming API.
@@
 The tweets were and cleaned of exotic characters.
+Before performing topic analysis, we excluded words that were mentioned fewer than 10 times, or more than 0.3 times the number of documents.
+We also performed Term Frequency Inverse Document Frequency (TF-IDF) normalization.
 
 We excluded tweets that did not originate in contiguous United States time zones.
-A subset of the tweets we collected had geolocation data available.
+14204 of the tweets we collected (about 2\%) had geolocation coordinates available.
 We found that tweets were largely concentrated on US and Canadian metro areas (Figure 1).
+The tweets did not seem to be over represented in any geographical region of the US.
 
@@
 \centering
-\includegraphics[height=2.5in, width=3.5in]{map}
+\includegraphics[height=3in, width=4in]{map}
 \caption{Plot of geolocated tweets.}
@@
 We trained a Word2Vec model, and queried for the top 10 word-vectors related to the term PrEP (Table 1).
-We found several HIV related events, WorldAIDSDay, HLM2016AIDS, ICASA2015, as well as the PrEP drug Truvada, and the term HIV.
+We found several HIV/AIDS related events, WorldAIDSDay, HLM2016AIDS, ICASA2015, as well as the PrEP drug Truvada, and the term HIV.
 In addition, we found the acronym ART which refers to Anti-Retroviral Therapy.
 DoingIt, and OneConversation, are ongoing efforts led by the Center for Disease Control (CDC) to spread awareness and reduce the spread of HIV.
-NBHAAD is an organization that is committed to increasing awareness for HIV within the Black community (TODO: look up if there is some special connection between HIV and Black community).
+NBHAAD is an organization that is committed to increasing awareness for HIV within the Black community.
 Nancy Reagan, who died in early 2016, was mentioned in conjunction with her efforts to combat HIV in the 1980's.
@@
 We also see a LGBT-related hashtag, \#lgbtmedia16, which indicates a distinct awareness of PrEP in the Gay community.
-This may reflect the known levels of HIV transmission in gay men (TODO: cite something here).
+This may reflect the known levels of HIV transmission in men who have sex with men~\cite{centers2014hiv}.
 
@@
 Conversely tweet 708519265540907010 has content that calls into doubt the usefulness of PrEP: "Checkout why PrEP is hurting the cause \& \#JoinTheConversation \#LGBTQIA".
-User 711275699529764864 is a twitter spam bot with no particular connection to PrEP.
+User 711275699529764864 appears to be a twitter spam bot with no obvious connection to PrEP.
 Together the Doc2Vec results show that we can monitor and identify PrEP-related hashtags and tweets.
@@
 Thus with this method we demonstrate a way to identify and monitor the most viral tweets related to PrEP.
-As the discussion changes, public health professionals can use this information to quickly identify the most important viral sentiment in the online PrEP conversation.
+As the discussion changes, public health professionals can use this information to quickly identify the most relevant viral sentiment in the online PrEP conversation.
 
@@
 
-Finally we wanted to visualize the relative similarities of these PrEP-related keywords in a low dimensional space.
-We took several keywords that we had identified in our PrEP related queries, along with other HIV-prevention related terms, and visualised their word-vectors in 2 dimensions using tSNE (Figure 2)(TODO: citation for tSNE.).
+Finally we wanted to visualize the relative similarities of several PrEP-related keywords in a low dimensional space.
+We took keywords that we had identified in our PrEP related queries, along with other HIV-prevention related terms, and visualised their word-vectors in 2 dimensions using tSNE~\cite{van2008visualizing} (Figure 2.
 
 We several trends.
-Notably the pharmaceutical based HIV therapies all cluster together (ART, PrEP, truvada), the AIDS awareness events cluster together (WorldAIDSDay, NBHAAD) and so do the sexually transmitted disease keywords (HIV, AIDS, STD).
+Notably the pharmaceutical based HIV therapies all cluster together (ART, PrEP, truvada) and the AIDS awareness events cluster together (WorldAIDSDay, NBHAAD, ICASA2015).
+Words that are related to HIV discussion, but also used in other contexts (undetectable, testing, awareness) are further away from the HIV/AIDS word-clusters.
 These results may provide another mechanism for researchers to visualize and identify relevant trends in PrEP-related keywords.
@@
 In DTM, documents are grouped in several corpuses that represent successive points in time.
-Latent Dirichlet Analysis (LDA) is then performed on each corpus, to extract a topic distribution.
+Latent Dirichlet Analysis (LDA) is performed on each corpus, to extract a topic distribution.
 The posterior topic distribution from time $t_n$ is used as the prior for time $t_{n+1}$.
-This lets the model determine a topic model for each time point that is dependent both on the set of tweets from that time point, and on the time point's document distribution.
+This lets the DTM model determine a topic model for each time point that is dependent both on the set of tweets from that time point, and on the previous time point's document distribution.
 We specified 10 topics and used each week's worth of tweets, over a 30 week period from the 47th week of 2015 to the 14th week of 2016, as our time points.
@@
 These dynamics may indicate that PrEP discussion is becoming more prevalent.
-Other HIV prevention related words such as 'pill', 'prevention' and 'drug' which serve as a form of negative controls.
-They are related to PrEP semantically, and are thus in the same topic.
-Yet the fact that they are not increasing, shows us that the increase in PrEP discussion is PrEP-specific.
+This growing trend would be consistent with the fact that while PrEP is still not widely known about among patients and healthcare providers, information about PrEP is slowly building into national awareness.
 
-However, it is hard to tell from these data though, whether the increased level of PrEP discussion is leading to increased levels of informed patients, medical providers, and adherence.
+Other HIV prevention related words such as 'pill', 'prevention' and 'drug' serve as a form of negative controls.
+They are related to PrEP, but also used in other medical contexts.
+The fact that they are not increasing, shows us that the increase in PrEP discussion is PrEP-specific.
+
+However, it is hard to tell from these data whether the increased level of PrEP discussion is leading to increased levels of informed patients, medical providers, and adherence.
 It is possible that stigma, and misinformation is leading to greater levels of PrEP discussion on twitter.
-We will get more specific, granular understanding of the PrEP discourse in our sentiment analysis section below.
+We will get more specific, granular understanding of the PrEP discourse in our sentiment analysis section below (see section "Sentiment Classification").
 
@@
 We found that topic 4 captured several keywords related to World AIDS Day (Figure 4).
-We can see that 'WorldAIDSDay', and 'can' peak in the 47th week of 2015 and then decline into 2016.
+We can see that "WorldAIDSDay", and "Can" peak in the 47th week of 2015 and then decline into 2016.
 This correlates well with the actual date of World AIDS Day, December 1st.
 Furthermore, while December 1st is World AIDS day, the whole month of December is AIDS Awareness Month.
-We can clearly see the words 'raise' and 'awareness' peak later and last longer that the word 'WorldAIDSDay' implying that it is correlated to the whole month of December.
-While our PrEP investigation isn't specifically interested in World AIDS Day, or AIDS awareness month, this observation validates our ability to accurately identify temporal events using DTM.
+We can clearly see the words 'raise' and 'awareness' peak later and last longer than the word 'WorldAIDSDay' implying that it is correlated to the whole month of December.
+While our PrEP investigation isn't specifically interested in World AIDS Day, or AIDS Awareness Month, this observation validates our ability to accurately identify temporal events using DTM.
 
@@
 
-Together, the DTM results demonstrate our ability to extract relevant HIV and PrEP related information from twitter that accurately captures time-dependant fluctuations.
+Together, the DTM results demonstrate our ability to extract relevant HIV and PrEP related information from Twitter that accurately captures time-dependant fluctuations.
 Public health professionals should be able to monitor these temporal trends to determine the relative interest in PrEP, and other HIV related keywords as they are discussed over time.
-This method could even lead to a system for early detection of HIV outbreaks, or other serious developments.
 
@@
 
-% Prior to topic modelling, tweets were cleaned of high and low frequency words, and transformed by Term Frequency Inverse Document Frequency (TFIDF) processing.
-
-% TODO work this section (re download and re-run) Tuesday
-
 We wanted to identify what Twitter users that mentioned PrEP were discussing in their other tweets.
 We identified users that were most similar to PrEP according to our Paragraph2Vec results, and downloaded their most recent 3000 tweets.
-We took the top 400 users that had at least 200 words in the combined tweets of their tweet history.
-For each user, we concatenated all of their tweets, and performed LDA topic modelling on the set of user-time line documents.
-
-When we examine a clustermap of users vs.
-topics, we see that the majority of these users are discussing topics 5, 1, and 4 (Figure 5).
-When we look up the top words in the corresponding topic distributions, we see that topics 1 and 4 seem to be related to republican party politics.
+We took the top 500 users that had at least 200 words in the combined tweets of their tweet history.
+For each user, we concatenated all of their tweets, and performed LDA topic modelling on the resulting set of user-timeline documents (Figure 5).
 
@@
 \centering
-\includegraphics[height=2.5in, width=3.5in]{user_timeline_clustermap}
+\includegraphics[height=2.5in, width=4.5in]{LDA_user_timelines}
 \caption{Clustermap of users vs. topics for the top 400 users related to PrEP.}
@@
 
-% table 3
-\begin{table*}
-\centering
-\caption{Topic modeling on PrEP-related users' timelines.}
-\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|c|} \hline
-Topic Number & Word 0 & Word 1 & Word 2 & Word 3 & Word 4 & Word 5\\ \hline
-0 & wordpress & dentists & rb & aquarius & faction & reconnect\\ \hline
-1 & empirefox & crooks & csr & payroll & ch & allin\\ \hline
-2 & vdeo & pra & gust & lgbtqia & rail & undetectable\\ \hline
-3 & hivaids & cdcstd & stigma & blacklivesmatter & realestate & getcovered\\ \hline
-4 & nigga & niggas & realdonaldtrump & lmao & cruz & gop\\ \hline
-5 & fertility & infertility & armenia & collage & nig & deactivate\\ \hline
-6 & packaging & buenas & amigo & bu & birthcontrol & reservations \\ \hline
-7 & mga & ka & socialmedia & lang & entrepreneur & naman\\ \hline
-8 & infosec & bigdata & multimedia & stl & fx & malware\\ \hline
-9 & nhsengland & sosa & tw & knitting & worldbank & thtorguk\\ \hline
-\hline\end{tabular}
-\end{table*}
+We performed LDA on the users' timelines using the pyLDAvis python package from graphlab~\cite{low2014graphlab}.
+We specified 100 topics, and found that only one of them was related to HIV (topic number13, see Figure 5) representing about 2\% of the marginal topic distribution.
+Topic 13 contained top terms "hivaids", "pepfar", "stigma" and "aidsgov".
+PEPFAR is a governmental organization, The United States President's Emergency Plan for AIDS Relief, that is focused on combating the spread of AIDS internationally.
+Interestingly we don't see PrEP in the top 30 terms in topic 13.
+This indicates that among twitter users that talk about PrEP, HIV is a small part of their discussion, and PrEP an even smaller part of their discussion.
 
-Together these results suggest that PrEP users are involved in political discussions, and are internationally focused.
+We investigated some of the other major topics from users' timelines, and found discussions of other STD's (topics 20, 29 and 17) and other health related terms (topics 12, and 25).
+The other health and STD-related topics clustered closely with topic 13 in Principle Component space.
+Some of the STD-related topics included terms related to LGBTQ, including the social networking platform Gridr in topic 17.
+Other terms related to STD's include prevention terms such as "CDC", "condoms", and "gettested".
+Topic 19 is nearby these STD-related topics in Principle Component space, and contains terms related to healthcare and political issues such as "Obamacare" and "ACA" (Affordable Care Act).
+This connection between HIV and other STD prevention, and political discourse may be relevant in PrEP-based HIV prevention efforts, considering there is in some cases no clear precedent for how preventative therapies like PrEP are covered by health insurance (TODO: find something to cite).
+
+One of the top words from the HIV-related topic, topic 13, was the term "stigma", the term "endstigma" was also found in topic 17.
+Previous studies have shown a variety of stigmas associated and HIV have hampered prevention efforts (TODO: cite something).
+Our observation of stigma-related terms corroborates that there is some discussion of stigma in the context of HIV on Twitter.
+Public health professionals may be able use the prevalence of the term "stigma" as a way to monitor the efficacy of efforts to end HIV related stigmas.
 
@@
 
-Lastly we trained a classifier to classify the sentiment of HIV and PrEP related tweets either positive or negative.
+Previously, we used analyses to summarize the whole Twitter corpus to produce high level trends.
+For our final analysis, we sought to get a deeper understanding of the data at the individual tweet level.
+Thus we trained a classifier to classify the sentiment of HIV and PrEP related tweets either positive or negative.
 This classifier would allow public health professionals to quickly identify positive and negative PrEP related tweets to guide HIV prevention efforts.
@@
 
- We chose to use a relatively simple classifier model (logistic regression) and stop training at
-
+We chose to use a relatively simple classifier model (logistic regression) and stop training at 20 iterations of stochasic gradient decent over the corpus, because we wanted to prevent the possibility that we over trained on our training data.
+This was especially important because our training and testing data, while both sets of tweets, were separate datasets.
 We then used this classifier to classify our PrEP related tweets into positive or negative labels.
-We reported the most positive, and most negative tweets, by log(probability), on our full dataset, and on tweets that specifically mention either 'prep' or 'truvada' (Table 4).
+We identified the most positive, and most negative tweets, by log(probability), on our full dataset, and on tweets that specifically mention either 'prep' or 'truvada'.
+We provided the text from the top 3 positive and negative tweets from each dataset (Table 3, Table 4).
 
 % do a top positive tweets table (also with tweet ID and log prob of classification)
-% table 4
+% table 3
 \begin{table*}
@@
 \caption{Positive Sentiment Tweets.}
-\begin{tabular}{|p{2cm}|p{12cm}|} \hline
+\begin{tabular}{|p{2.5cm}|p{12cm}|} \hline
 Category & Text\\ \hline
@@
 % do a top negative tweets table (also with tweet ID and log prob of classification)
-% table 5
+% table 4
 \begin{table*}
@@
 \caption{Negative Sentiment Tweets.}
-\begin{tabular}{|p{2cm}|p{12cm}|} \hline
+\begin{tabular}{|p{2.5cm}|p{12cm}|} \hline
 Category & Text\\ \hline
@@
 
-% there is viable information in the LDA topic modeling on positive and negative tweets
+While the sentiment classification doesn't have perfect accuracy, we can see positive tweets disseminating information about the efficacy and benefits of PrEP related preventions (Table 3).
+The positive tweets indicate that PrEP public health efforts have had some effect diseminating PrEP information on Twitter.
+
+The negative tweets may be more important than the positive tweets to guide future public health policy corrections.
+The negative tweets contain concerns that Truvada may not block HIV transmission in all cases (Table 4).
+There also seems to be concern that use of Truvada may increase the transmission of non-HIV STDs such as Hepatitis C because PrEP users stop using condoms.
+This may indicate that public health professionals need to stress that PrEP users should not stop wearing condoms when they spread PrEP related information.
+
+Another negative tweet contains questions over weather Truvada is available as a generic drug.
+This may indicate that in some cases, patients are aware of PrEP, but do not have access to it, either because it is not avaliable through their healthcare provider, or because it is not affordable.
+
+Finally we see some contention over national political leadership in the effort to prevent HIV.
+While political discussions can often get heated, especially on Twitter, the contention can harm concerted efforts to provide consent governmental leadership in HIV prevention.
+Public health officials may consider stressing that unity in health policy at the federal level is important to protect the population from the spread of HIV.
 

### 2016-04-26 draft/draft.tex
finish rough intro

@@
 
-\usepackage [english]{babel}
-\usepackage [autostyle, english = american]{csquotes}
-\MakeOuterQuote{"}
+%\usepackage [english]{babel}
+%\usepackage [autostyle, english = american]{csquotes}
+%\MakeOuterQuote{"}
 
@@
 Patrick Breen\\
-       \affaddr{The Institute of Bioinformatics}\\
+       \affaddr{Institute of Bioinformatics}\\
        \affaddr{The University of Georgia}\\
@@
 Shannon Quinn\titlenote{Corresponding author.}\\
-       \affaddr{Institute of Computer Science}\\
+       \affaddr{Department of Computer Science}\\
        \affaddr{University of Georgia}\\
@@
 
-Pre-Exposure Prophylaxis (PrEP) is a recently developed therapy for the prevention of Human Immunodeficiency Virus (HIV).
-The treatment is available as a pill named Truvada and is taken once a day for as much as 99\% protection from infection when exposed to HIV.
+Pre-Exposure Prophylaxis (PrEP) is a recently developed therapy for the prevention of Human Immunodeficiency Virus (HIV) transmission.
+The treatment is available as a pill named Truvada and is taken once a day by HIV negative individuals for as much as 99\% protection when exposed to HIV.
 While medically effective, PrEP suffers from high drug costs, HIV-related social stigma, and under-informed health providers and patients.
-This paper describes a data mining and machine learning strategy that monitors Twitter social media data to determine HIV and PrEP discussion trends.
-Our results show that we can identify PrEP and HIV discussion dynamics over time, and positive and negative PrEP-related tweets.
-These results can be used by public health professionals to inform and protect at-risk individuals from HIV.
+Data mining of social media has proven effective in the monitoring of HIV in the US, but no study has investigated PrEP using social media.
+This paper describes a data mining and machine learning strategy using natural language processing that monitors Twitter social media data to identify PrEP discussion trends.
+Our results show that we can identify PrEP and HIV discussion dynamics over time, and PrEP-related tweets with positive and negative sentiment.
+These results can be used by public health professionals to monitor PrEP discussion trends, and identify strategies to improve HIV prevention.
 
@@
 %
-% TODO: this section
+
 \begin{CCSXML}
-
+TODO: this section
 \end{CCSXML}
@@
 
-\keywords{ Social Media, Topic Modelling, Document Embedding}
+\keywords{ Social Media, HIV, Topic Modelling, Document Classification}
 
 \section{Introduction}
-Example citation (needed right now to compile):
+Pre-exposure prophylaxis (PrEP) is an HIV prevention method marketed in the form of a pill named Truvada.
+Truvada was approved by the Food and Drug Administration (FDA) in 2012 to prevent sexually acquired HIV infection after several positive trials~\cite{grant2010preexposure,thigpen2012antiretroviral} showed that it was safe and effective.
+Despite minimal side effects, and risk protection of up to 99\%, PrEP suffers from uncertain health insurance compensation, the risk of spreading HIV drug resistance and uninformed health providers and patients~\cite{liu2014early}.
+Truvada must be taken once a day for full protection.
+In some individuals, adherence is difficult to maintain~\cite{van2012unraveling}, leading to loss of Truvada's effectiveness.
+While public health officials can spread information and monitor the effectiveness of PrEP at the clinic-level, scaled-up data mining on social media data may provide more complete information on PrEP at the national level.
 
-Introduce and literature review of:
-1) PrEP, HIV, Twitter
+Twitter has been used as a source of data for large scale opinion mining in public health monitoring contexts to predict the spread of influenza~\cite{aramaki2011twitter}, predict postpartum depression~\cite{de2013predicting}, and examine tobacco use~\cite{myslin2013using}.
+Recently it has also been used for the study of HIV~\cite{young2014methods,young2013online}.
+These studies of HIV have focused on county-level HIV prevalence prediction, and general HIV discussion monitoring, but they have not focused on PrEP related discussion.
+Furthermore, existing HIV social media analyses have not taken full advantage of natural language processing (NLP) techniques to discover semantic information in unstructured text~\cite{young2015big}.
 
- - social impact issues, efficacy, adherence issues, other STDs, Austin (Scott County) Indiana Outbreak as example
+Tweets from twitter consist of short 140 character text messages that may also contain hashtag annotations.
 
- - High cost of actual drug medication, and unclear health insurance situation.
+One recently developed tool for NLP, called Word2Vec, is a connectionist method that embeds words as word-vectors in a semantic space that captures substitution-similarity~\cite{mikolov2013efficient}.
+There are several forms of Word2Vec, though the most popular version, Skip-gram Negative Sampling (SGNS), has been shown to perform well at producing word-vectors that capture important word relationships.
+This includes most notably word analogies.
 
- - Many health providers do not know about drug.
+Word2Vec is also used as a preprocessing step for additional analyses that start from pre-trained word-vectors.
+Doc2Vec~\cite{le2014distributed} is a method that produces a document-vector for each document, and each document-level identifier.
+In the case of a tweet-corpus, document identifiers might include for example document ID, hashtags, and the user who created the document.
+Each of these document-level identifiers is embedded in a similarity space, allowing one to identify similar tweets, hastags and users.
 
- - specifically other papers that did mining Twitter for HIV
+Latent Dirichlet Allocation~\cite{blei2003latent} (LDA) is used to identify a small set of latent topics present in an unstructured corpus.
+LDA is a graphical model that generates documents from a set of latent topics.
+A topic is a probability distribution over words that captures a set of related words.
+LDA models are often inferred in practice using Bayesian inference via either collapsed Gibbs sampling or Variational Bayesian inference.
+Inspection of the resulting topics allows one to identify relevant terms and the context in which they occur in the corpus.
 
- - Here is a paper that did twitter data mining for flu prediction:
+Dynamic Topic Modeling~\cite{blei2006dynamic} (DTM) is an extension of LDA that produces a seried of topic models over time.
+Briefly, the documents in the corpus are divided into several corpuses that are successive in time.
+LDA is performed on each corpus, to extract a topic distribution.
+The posterior topic distribution from time $t_n$ is used as the prior for time $t_{n+1}$.
+This lets the DTM model determine a topic model for each time point that is dependent both on the set of tweets from that time point, and on the previous time point's document distribution.
 
- %http://snap.stanford.edu/soma2010/papers/soma2010_16.pdf
-
- Talk about how it's harder to get feedback/ account for HIV infections compared with CDC baseline data for flu. Talk about twitter-specifc issues such as bots and slang.
-
-2) Word2Vec, Doc2Vec
-
- - theory and application examples
-
-3) Dynamic Topic models, Latent Dirichlet allocation
-
-- theory and application examples
+In this paper we answer the acknowledged need to harness large scale data in the battle against HIV~\cite{young2015big}.
+We use the above NLP techniques to extract PrEP-related semantic information from a Twitter corpus dataset.
+We identify critical PrEP related terms, users, hashtags and tweets.
+We identify PrEP discussion trends over time, and identify other topics that people who tweet about PrEP also tweet about.
+Finally we train a sentiment classifier that automatically identifies PrEP related tweets with positive and negative sentiment.
+Together these results, and these approaches can be used by public health officials to identify the national PrEP discussion and respond to issues as they arise.
 
 \section{Results}
-
 We sought to determine trends in HIV and PrEP discourse on twitter to inform and coordinate public health efforts aiming to promote PrEP adoption and adherence for at-risk individuals.
-We collected 624,569 tweets containing at least one of the following words 'HIV', 'AIDS', 'truvada', 'prophylaxis', 'imtesting', 'PrEP' from Twitter's streaming API.
+We collected 624,569 tweets containing at least one of the following words 'HIV', 'AIDS', 'truvada', 'prophylaxis', 'imtesting', 'PrEP' from Twitter's streaming API (TODO: how to cite Twitter streaming API?).
 The tweets were restricted to English language, and the collection dates spanned from the 47th week of 2015 to the 14th week of 2016.
-The tweets were and cleaned of exotic characters.
+The tweets were cleaned of exotic characters.
 Before performing topic analysis, we excluded words that were mentioned fewer than 10 times, or more than 0.3 times the number of documents.
@@
 \centering
-\caption{Cosine Similarity to word-vector 'PrEP'}
+\caption{Cosine Similarity to word-vector PrEP}
 \begin{tabular}{|l|c|} \hline
-Related Word & Cosine Similarity to 'PrEP'\\ \hline
+Related Word & Cosine Similarity to PrEP\\ \hline
 truvada & 0.796666\\ \hline
@@
 This may reflect the known levels of HIV transmission in men who have sex with men~\cite{centers2014hiv}.
+Together the Doc2Vec results show that we can monitor and identify PrEP-related hashtags and tweets.
 
@@
 User 711275699529764864 appears to be a twitter spam bot with no obvious connection to PrEP.
-Together the Doc2Vec results show that we can monitor and identify PrEP-related hashtags and tweets.
-The most PrEP related tweets, the content of the above tweets were popular on twitter over the period of data that we collected.
-When they were retweeted, doc2vec weighted them more highly similar to \#prep.
 Thus with this method we demonstrate a way to identify and monitor the most viral tweets related to PrEP.
@@
 \centering
-\caption{Cosine Similarity to doc-vector '\#PrEP'}
+\caption{Cosine Similarity to doc-vector \#PrEP}
 \begin{tabular}{|l|c|} \hline
-Related Hashtag/Tweet & Cosine Similarity to '\#PrEP'\\ \hline
+Related Hashtag/Tweet & Cosine Similarity to \#PrEP\\ \hline
 \#lgbtmedia16 & 0.739128\\ \hline
@@
 Words that are related to HIV discussion, but also used in other contexts (undetectable, testing, awareness) are further away from the HIV/AIDS word-clusters.
-These results may provide another mechanism for researchers to visualize and identify relevant trends in PrEP-related keywords.
+These results provide another mechanism for researchers to visualize and identify relevant trends in PrEP-related keywords.
 
@@
 We used Dynamic Topic Modelling (DTM) to identify how certain topics change over time.
-In DTM, documents are grouped in several corpuses that represent successive points in time.
-Latent Dirichlet Analysis (LDA) is performed on each corpus, to extract a topic distribution.
-The posterior topic distribution from time $t_n$ is used as the prior for time $t_{n+1}$.
-This lets the DTM model determine a topic model for each time point that is dependent both on the set of tweets from that time point, and on the previous time point's document distribution.
 We specified 10 topics and used each week's worth of tweets, over a 30 week period from the 47th week of 2015 to the 14th week of 2016, as our time points.
@@
 This growing trend would be consistent with the fact that while PrEP is still not widely known about among patients and healthcare providers, information about PrEP is slowly building into national awareness.
+A study in New York City in 2011 indicated that only 36\% of high risk individuals were aware of PrEP~\cite{mehta2011awareness}.
 
-Other HIV prevention related words such as 'pill', 'prevention' and 'drug' serve as a form of negative controls.
+Other HIV prevention related words such as 'pill', 'prevention' and 'drug' serve as negative controls.
 They are related to PrEP, but also used in other medical contexts.
@@
 \centering
-\includegraphics[height=2.5in, width=4.5in]{LDA_user_timelines}
+\includegraphics[height=2.5in, width=5in]{LDA_user_timelines}
 \caption{Clustermap of users vs. topics for the top 400 users related to PrEP.}
@@
 PEPFAR is a governmental organization, The United States President's Emergency Plan for AIDS Relief, that is focused on combating the spread of AIDS internationally.
-Interestingly we don't see PrEP in the top 30 terms in topic 13.
+Interestingly, we don't see PrEP in the top 30 terms in topic 13.
 This indicates that among twitter users that talk about PrEP, HIV is a small part of their discussion, and PrEP an even smaller part of their discussion.
@@
 We investigated some of the other major topics from users' timelines, and found discussions of other STD's (topics 20, 29 and 17) and other health related terms (topics 12, and 25).
-The other health and STD-related topics clustered closely with topic 13 in Principle Component space.
-Some of the STD-related topics included terms related to LGBTQ, including the social networking platform Gridr in topic 17.
+The other health and STD-related topics clustered closely with topic 13 in Principle Component (PC) space.
+Some of the STD-related topics included terms related to LGBTQ, including the social networking platform Grindr in topic 17.
 Other terms related to STD's include prevention terms such as "CDC", "condoms", and "gettested".
-Topic 19 is nearby these STD-related topics in Principle Component space, and contains terms related to healthcare and political issues such as "Obamacare" and "ACA" (Affordable Care Act).
-This connection between HIV and other STD prevention, and political discourse may be relevant in PrEP-based HIV prevention efforts, considering there is in some cases no clear precedent for how preventative therapies like PrEP are covered by health insurance (TODO: find something to cite).
+Topic 19 is nearby these STD-related topics in PC space, and contains terms related to healthcare and political issues such as "Obamacare" and "ACA" (Affordable Care Act).
+This connection between HIV and other STD prevention, and political discourse may be relevant in PrEP-based HIV prevention efforts, considering there is in some cases no clear precedent for how preventative therapies like PrEP are covered by health insurance~\cite{liu2014early}.
 
 One of the top words from the HIV-related topic, topic 13, was the term "stigma", the term "endstigma" was also found in topic 17.
-Previous studies have shown a variety of stigmas associated and HIV have hampered prevention efforts (TODO: cite something).
-Our observation of stigma-related terms corroborates that there is some discussion of stigma in the context of HIV on Twitter.
+Previous studies have shown a variety of stigmas associated and HIV have hampered prevention efforts~\cite{liu2014early}.
+Our observation of stigma related terms corroborates that there is some discussion of stigma in the context of HIV on Twitter.
 Public health professionals may be able use the prevalence of the term "stigma" as a way to monitor the efficacy of efforts to end HIV related stigmas.
@@
 \subsection{Sentiment Classification}
-
-% TODO work this section Tuesday (give example positive and negative tweets)
 
@@
 
-We chose to use a relatively simple classifier model (logistic regression) and stop training at 20 iterations of stochasic gradient decent over the corpus, because we wanted to prevent the possibility that we over trained on our training data.
+We chose to use a relatively simple classifier model (logistic regression) and stop training at 20 iterations of stochastic gradient decent over the corpus, because we wanted to prevent the possibility that we overtrained on our training data.
 This was especially important because our training and testing data, while both sets of tweets, were separate datasets.
-We then used this classifier to classify our PrEP related tweets into positive or negative labels.
-We identified the most positive, and most negative tweets, by log(probability), on our full dataset, and on tweets that specifically mention either 'prep' or 'truvada'.
+We then used this classifier to classify our PrEP related tweets into positive or negative sentiment labels.
+We identified the most positive, and most negative tweets, by log probability, on our full dataset, and on tweets that specifically mention either PrEP or Truvada.
 We provided the text from the top 3 positive and negative tweets from each dataset (Table 3, Table 4).
 
-% do a top positive tweets table (also with tweet ID and log prob of classification)
+% do a top positive tweets table (also with tweet ID)
 % table 3
@@
 
-% do a top negative tweets table (also with tweet ID and log prob of classification)
+% do a top negative tweets table (also with tweet ID)
 % table 4
@@
 While the sentiment classification doesn't have perfect accuracy, we can see positive tweets disseminating information about the efficacy and benefits of PrEP related preventions (Table 3).
-The positive tweets indicate that PrEP public health efforts have had some effect diseminating PrEP information on Twitter.
+The positive tweets indicate that PrEP public health efforts have had some effect disseminating PrEP information on Twitter.
 
@@
 The negative tweets contain concerns that Truvada may not block HIV transmission in all cases (Table 4).
-There also seems to be concern that use of Truvada may increase the transmission of non-HIV STDs such as Hepatitis C because PrEP users stop using condoms.
+There also seems to be concern that use of Truvada may increase the transmission of non-HIV STDs such as Hepatitis C because some PrEP users stop using condoms.
 This may indicate that public health professionals need to stress that PrEP users should not stop wearing condoms when they spread PrEP related information.
@@
 Another negative tweet contains questions over weather Truvada is available as a generic drug.
-This may indicate that in some cases, patients are aware of PrEP, but do not have access to it, either because it is not avaliable through their healthcare provider, or because it is not affordable.
+This may indicate that in some cases, patients are aware of PrEP, but do not have access to it, either because it is not available through their healthcare provider, or because it is not affordable.
 
@@
 % produce the bibliography for the citations in your paper.
-\bibliographystyle{abbrv}
-\bibliography{sigproc}  % sigproc.bib is the name of the Bibliography in this case
+
+  % sigproc.bib is the name of the Bibliography in this case
 % You must have a proper ".bib" file
@@
 
-\subsection{References}
+\bibliographystyle{abbrv}
+\bibliography{draft}
 

### 2016-05-03 draft/draft.tex
add references and clean draft

@@
 %\MakeOuterQuote{"}
-
+\usepackage{lineno}
 \begin{document}
-
+\linenumbers
 % Copyright
@@
 While medically effective, PrEP suffers from high drug costs, HIV-related social stigma, and under-informed health providers and patients.
-Data mining of social media has proven effective in the monitoring of HIV in the US, but no study has investigated PrEP using social media.
-This paper describes a data mining and machine learning strategy using natural language processing that monitors Twitter social media data to identify PrEP discussion trends.
+Data mining of social media has proven effective in the monitoring of HIV in the United States, but no study has investigated PrEP using social media.
+This paper describes a data mining and machine learning strategy using natural language processing (NLP) that monitors Twitter social media data to identify PrEP discussion trends.
 Our results show that we can identify PrEP and HIV discussion dynamics over time, and PrEP-related tweets with positive and negative sentiment.
@@
 \section{Introduction}
-Pre-exposure prophylaxis (PrEP) is an HIV prevention method marketed in the form of a pill named Truvada.
+Pre-exposure prophylaxis (PrEP), a treatment for the prevention of Immunodeficiency Virus (HIV), is marketed under the trade name Truvada.
 Truvada was approved by the Food and Drug Administration (FDA) in 2012 to prevent sexually acquired HIV infection after several positive trials~\cite{grant2010preexposure,thigpen2012antiretroviral} showed that it was safe and effective.
-Despite minimal side effects, and risk protection of up to 99\%, PrEP suffers from uncertain health insurance compensation, the risk of spreading HIV drug resistance and uninformed health providers and patients~\cite{liu2014early}.
+Despite minimal side effects, and risk protection of up to 99\%, PrEP suffers from uncertain health insurance compensation, the risk of producing drug resistant strains and uninformed health providers and patients~\cite{liu2014early}.
 Truvada must be taken once a day for full protection.
@@
 
+Tweets from twitter consist of short 140 character text messages that may also contain hashtag annotations.
 Twitter has been used as a source of data for large scale opinion mining in public health monitoring contexts to predict the spread of influenza~\cite{aramaki2011twitter}, predict postpartum depression~\cite{de2013predicting}, and examine tobacco use~\cite{myslin2013using}.
@@
 Furthermore, existing HIV social media analyses have not taken full advantage of natural language processing (NLP) techniques to discover semantic information in unstructured text~\cite{young2015big}.
-
-Tweets from twitter consist of short 140 character text messages that may also contain hashtag annotations.
 
@@
 A topic is a probability distribution over words that captures a set of related words.
-LDA models are often inferred in practice using Bayesian inference via either collapsed Gibbs sampling or Variational Bayesian inference.
+LDA models are often inferred in practice using Bayesian inference either via collapsed Gibbs sampling or Variational Bayesian inference.
 Inspection of the resulting topics allows one to identify relevant terms and the context in which they occur in the corpus.
 
-Dynamic Topic Modeling~\cite{blei2006dynamic} (DTM) is an extension of LDA that produces a seried of topic models over time.
+Dynamic Topic Modelling~\cite{blei2006dynamic} (DTM) is an extension of LDA that produces a seried of topic models over time.
 Briefly, the documents in the corpus are divided into several corpuses that are successive in time.
-LDA is performed on each corpus, to extract a topic distribution.
+LDA is performed on each corpus to extract a topic distribution.
 The posterior topic distribution from time $t_n$ is used as the prior for time $t_{n+1}$.
-This lets the DTM model determine a topic model for each time point that is dependent both on the set of tweets from that time point, and on the previous time point's document distribution.
+This lets the DTM model determine a topic model for each time point that is dependent both on the set of tweets from that time point, and on the previous time point's topic distribution.
 
-In this paper we answer the acknowledged need to harness large scale data in the battle against HIV~\cite{young2015big}.
+In this paper we respond to the acknowledged need to harness large scale data in the battle against HIV~\cite{young2015big}.
 We use the above NLP techniques to extract PrEP-related semantic information from a Twitter corpus dataset.
 We identify critical PrEP related terms, users, hashtags and tweets.
-We identify PrEP discussion trends over time, and identify other topics that people who tweet about PrEP also tweet about.
-Finally we train a sentiment classifier that automatically identifies PrEP related tweets with positive and negative sentiment.
-Together these results, and these approaches can be used by public health officials to identify the national PrEP discussion and respond to issues as they arise.
+We identify PrEP discussion trends over time, and identify other topics that people who tweet about PrEP, also tweet about.
+Finally we train a sentiment classifier that automatically identifies PrEP-related tweets with positive and negative sentiment.
+Together these results, and these approaches, can be used by public health officials to identify the national PrEP discussion and respond to issues as they arise.
 
@@
 We sought to determine trends in HIV and PrEP discourse on twitter to inform and coordinate public health efforts aiming to promote PrEP adoption and adherence for at-risk individuals.
-We collected 624,569 tweets containing at least one of the following words 'HIV', 'AIDS', 'truvada', 'prophylaxis', 'imtesting', 'PrEP' from Twitter's streaming API (TODO: how to cite Twitter streaming API?).
+We collected 624,569 tweets containing at least one of the following words 'HIV', 'AIDS', 'truvada', 'prophylaxis', 'imtesting', 'PrEP' from Twitter's streaming API.
 The tweets were restricted to English language, and the collection dates spanned from the 47th week of 2015 to the 14th week of 2016.
@@
 We excluded tweets that did not originate in contiguous United States time zones.
-14204 of the tweets we collected (about 2\%) had geolocation coordinates available.
-We found that tweets were largely concentrated on US and Canadian metro areas (Figure 1).
+A subset of 14,204 tweets (about 2\%) had geolocation coordinates available.
+We found that these tweets were largely concentrated on US and Canadian metro areas (Figure 1).
 The tweets did not seem to be over represented in any geographical region of the US.
@@
 Nancy Reagan, who died in early 2016, was mentioned in conjunction with her efforts to combat HIV in the 1980's.
-Together these results show us a high-level view of the important components of the national PrEP conversation on Twitter.
+Together these results show us a high-level view of the important components of the national PrEP conversation on Twitter over the collection period.
 
@@
 Conversely tweet 708519265540907010 has content that calls into doubt the usefulness of PrEP: "Checkout why PrEP is hurting the cause \& \#JoinTheConversation \#LGBTQIA".
+
+TODO: investigate those tweets, especially "Checkout why PrEP is hurting the cause"
+
 User 711275699529764864 appears to be a twitter spam bot with no obvious connection to PrEP.
-Thus with this method we demonstrate a way to identify and monitor the most viral tweets related to PrEP.
+Thus while we observe some noise, our results demonstrate a way to quickly identify and monitor the most viral tweets related to PrEP.
 As the discussion changes, public health professionals can use this information to quickly identify the most relevant viral sentiment in the online PrEP conversation.
@@
 \begin{tabular}{|l|c|} \hline
-Related Hashtag/Tweet & Cosine Similarity to \#PrEP\\ \hline
+Related hashtag/Tweet & Cosine Similarity to \#PrEP\\ \hline
 \#lgbtmedia16 & 0.739128\\ \hline
@@
 Finally we wanted to visualize the relative similarities of several PrEP-related keywords in a low dimensional space.
-We took keywords that we had identified in our PrEP related queries, along with other HIV-prevention related terms, and visualised their word-vectors in 2 dimensions using tSNE~\cite{van2008visualizing} (Figure 2.
+We took keywords that we had identified in our PrEP related queries, along with other HIV-prevention related terms, and visualised their word-vectors in 2 dimensions using t-distributed Stochastic Neighbour Embedding(tSNE)~\cite{van2008visualizing} (Figure 2.
 
-We several trends.
+We identified several trends.
 Notably the pharmaceutical based HIV therapies all cluster together (ART, PrEP, truvada) and the AIDS awareness events cluster together (WorldAIDSDay, NBHAAD, ICASA2015).
@@
 We found at least one other DTM topic that showed interesting behaviour.
-We found that topic 4 captured several keywords related to World AIDS Day (Figure 4).
+We observed that topic 4 captured several keywords related to World AIDS Day (Figure 4).
 We can see that "WorldAIDSDay", and "Can" peak in the 47th week of 2015 and then decline into 2016.
@@
 We can clearly see the words 'raise' and 'awareness' peak later and last longer than the word 'WorldAIDSDay' implying that it is correlated to the whole month of December.
-While our PrEP investigation isn't specifically interested in World AIDS Day, or AIDS Awareness Month, this observation validates our ability to accurately identify temporal events using DTM.
+While our PrEP investigation isn't specifically interested in World AIDS Day, or AIDS Awareness Month, this observation serves as a control to validate our ability to accurately identify temporal events using DTM.
 
@@
 We wanted to identify what Twitter users that mentioned PrEP were discussing in their other tweets.
-We identified users that were most similar to PrEP according to our Paragraph2Vec results, and downloaded their most recent 3000 tweets.
-We took the top 500 users that had at least 200 words in the combined tweets of their tweet history.
+We identified users that were most similar to PrEP according to our Paragraph2Vec results, and downloaded their recent tweet history, up to their last 3000 tweets.
+We selected top 500 users that had at least 200 words in the combined tweets of their tweet history.
 For each user, we concatenated all of their tweets, and performed LDA topic modelling on the resulting set of user-timeline documents (Figure 5).
@@
 We performed LDA on the users' timelines using the pyLDAvis python package from graphlab~\cite{low2014graphlab}.
-We specified 100 topics, and found that only one of them was related to HIV (topic number13, see Figure 5) representing about 2\% of the marginal topic distribution.
+We specified 100 topics, and found that only one of them was related to HIV (topic number 13, see Figure 5) representing about 2\% of the marginal topic distribution.
 Topic 13 contained top terms "hivaids", "pepfar", "stigma" and "aidsgov".
@@
 
-We chose to use a relatively simple classifier model (logistic regression) and stop training at 20 iterations of stochastic gradient decent over the corpus, because we wanted to prevent the possibility that we overtrained on our training data.
+We chose to use a relatively simple classifier model (logistic regression) and stop training at 20 epochs of stochastic gradient decent over the corpus, because we wanted to prevent the possibility that we overtrained on our training data.
 This was especially important because our training and testing data, while both sets of tweets, were separate datasets.
-We then used this classifier to classify our PrEP related tweets into positive or negative sentiment labels.
+We then used this trained classifier to classify our PrEP related tweets into positive or negative sentiment labels.
 We identified the most positive, and most negative tweets, by log probability, on our full dataset, and on tweets that specifically mention either PrEP or Truvada.
-We provided the text from the top 3 positive and negative tweets from each dataset (Table 3, Table 4).
+We provide the text from the top three positive and negative tweets from each of the three datasets (Table 3, Table 4).
 
@@
 
-While the sentiment classification doesn't have perfect accuracy, we can see positive tweets disseminating information about the efficacy and benefits of PrEP related preventions (Table 3).
-The positive tweets indicate that PrEP public health efforts have had some effect disseminating PrEP information on Twitter.
+While the sentiment classification doesn't have perfect sentiment accuracy, we can see in general that the positive tweets are disseminating information about the efficacy and benefits of PrEP related preventions (Table 3).
+The positive tweets indicate that PrEP public health informational efforts have had some effect disseminating PrEP information on Twitter.
 
@@
 There also seems to be concern that use of Truvada may increase the transmission of non-HIV STDs such as Hepatitis C because some PrEP users stop using condoms.
-This may indicate that public health professionals need to stress that PrEP users should not stop wearing condoms when they spread PrEP related information.
+This may indicate that public health professionals need to stress that PrEP users continue to wear condoms for full protection against other diseases in PrEP-related health information.
 
-Another negative tweet contains questions over weather Truvada is available as a generic drug.
-This may indicate that in some cases, patients are aware of PrEP, but do not have access to it, either because it is not available through their healthcare provider, or because it is not affordable.
+Another negative tweet questions whether Truvada is available as a generic drug.
+PrEP is currently only available through Gilead's Truvada, though a generic may be available as soon as 2017~\cite{truvadagenericblog}.
+Current patients must deal with uncertain drug prices, which vary from \$14,000 to \$70~\cite{truvadagenericblog}, and have in some cases, uncertain medical insurance reimbursement status.
+This tweet highlights both the difficulty of aquiring affordable PrEP medication, and also a level of conflicting information circulating on social media.
 
@@
 Public health officials may consider stressing that unity in health policy at the federal level is important to protect the population from the spread of HIV.
+
+TODO: investigate the reference to  \#truvadawhore which came up in the sentiment tweets above.
 

### 2016-05-05 draft/draft.tex
update draft

@@
 Data mining of social media has proven effective in the monitoring of HIV in the United States, but no study has investigated PrEP using social media.
-This paper describes a data mining and machine learning strategy using natural language processing (NLP) that monitors Twitter social media data to identify PrEP discussion trends.
+This paper describes a data mining and machine learning strategy using natural language processing (NLP), that monitors Twitter social media data to identify PrEP discussion trends.
 Our results show that we can identify PrEP and HIV discussion dynamics over time, and PrEP-related tweets with positive and negative sentiment.
@@
 
-Tweets from twitter consist of short 140 character text messages that may also contain hashtag annotations.
+Tweets from Twitter consist of short 140 character text messages that may also contain hashtag annotations.
 Twitter has been used as a source of data for large scale opinion mining in public health monitoring contexts to predict the spread of influenza~\cite{aramaki2011twitter}, predict postpartum depression~\cite{de2013predicting}, and examine tobacco use~\cite{myslin2013using}.
@@
 A topic is a probability distribution over words that captures a set of related words.
-LDA models are often inferred in practice using Bayesian inference either via collapsed Gibbs sampling or Variational Bayesian inference.
+LDA models are often inferred in practice using Bayesian inference either via collapsed Gibbs sampling or Variational Bayesian methods.
 Inspection of the resulting topics allows one to identify relevant terms and the context in which they occur in the corpus.
 
-Dynamic Topic Modelling~\cite{blei2006dynamic} (DTM) is an extension of LDA that produces a seried of topic models over time.
+Dynamic Topic Modelling~\cite{blei2006dynamic} (DTM) is an extension of LDA that produces a series of topic models over time.
 Briefly, the documents in the corpus are divided into several corpuses that are successive in time.
@@
 \centering
-\caption{Cosine Similarity to word-vector PrEP}
+\caption{Cosine similarity to word-vector "PrEP"}
 \begin{tabular}{|l|c|} \hline
-Related Word & Cosine Similarity to PrEP\\ \hline
+Related word & cosine similarity to PrEP\\ \hline
 truvada & 0.796666\\ \hline
@@
 
-TODO: investigate those tweets, especially "Checkout why PrEP is hurting the cause"
+We investigated the blog article linked to tweet 708519265540907010\cite{prephurtingcause}.
+The article, authored by Steven Banning, an HIV positive individual, expresses concerns about how new HIV treatments, like PrEP are being adopted by the HIV community.
+Steven notes that treatments for HIV positive individuals, and treatments to prevent HIV such as PrEP have made HIV a much more treatable disease than it was in the 1980's.
+These medical advances may have led in part to some unintended medical and social consequences.
+Steven notes that the rise of drug-resistant HIV strains has increased, in part due to HIV patients not adhering to to consistent treatment plans.
+He also points out the recent social trend of "bug chasers" individuals who are actively seeking to acquire and spread HIV strains.
+Perhaps the widespread availability of effective HIV medications have desensitized people to a healthy fear of the disease.
 
-User 711275699529764864 appears to be a twitter spam bot with no obvious connection to PrEP.
+User 711275699529764864 appears to be a Twitter spam bot with no obvious connection to PrEP.
+Unfortunately, bots are commonly used on Twitter for advertising and marketing purposes, and sometimes hinder pertinent information retrieval.
 Thus while we observe some noise, our results demonstrate a way to quickly identify and monitor the most viral tweets related to PrEP.
@@
 \centering
-\caption{Cosine Similarity to doc-vector \#PrEP}
+\caption{Cosine similarity to document-vector "\#PrEP"}
 \begin{tabular}{|l|c|} \hline
-Related hashtag/Tweet & Cosine Similarity to \#PrEP\\ \hline
+Related hashtag/tweet & cosine similarity to \#PrEP\\ \hline
 \#lgbtmedia16 & 0.739128\\ \hline
@@
 \centering
-\caption{Positive Sentiment Tweets.}
+\caption{Positive sentiment tweets.}
 \begin{tabular}{|p{2.5cm}|p{12cm}|} \hline
@@
 \centering
-\caption{Negative Sentiment Tweets.}
+\caption{Negative sentiment tweets.}
 \begin{tabular}{|p{2.5cm}|p{12cm}|} \hline
 Category & Text\\ \hline
-General & "Also, how fucking vile of Hillary to say. Reagan did fucking NOTHING during the AIDS epidemic until it was too late. What a stupid old hag."\\ \hline
-General & "I wonder why he beat her ass when she was tryna leave like she wasn't gone be running back when she found out she had HIV \& nobody want her"\\ \hline
+General & "Also, how f***ing vile of Hillary to say. Reagan did f***ing NOTHING during the AIDS epidemic until it was too late. What a stupid old hag."\\ \hline
+General & "I wonder why he beat her a** when she was tryna leave like she wasn't gone be running back when she found out she had HIV \& nobody want her"\\ \hline
 General & "Aaannd. Hillary Clinton breathes a sigh of relief that Twitter has left its outrage of her AIDS comments behind to tend to Drumpf debacle."\\ \hline
@@
 Current patients must deal with uncertain drug prices, which vary from \$14,000 to \$70~\cite{truvadagenericblog}, and have in some cases, uncertain medical insurance reimbursement status.
-This tweet highlights both the difficulty of aquiring affordable PrEP medication, and also a level of conflicting information circulating on social media.
+This tweet highlights both the difficulty of acquiring affordable PrEP medication, and also a level of conflicting information circulating on social media.
 
@@
 
-TODO: investigate the reference to  \#truvadawhore which came up in the sentiment tweets above.
+The last tweet in the positive tweets table (Table 3), referencing the hashtag "\#truvadawhore", links to a blog article written by Evan Peterson titled "The Case for PrEP, or How I Learned to Stop Worrying and Love HIV-Positive Guys"~\cite{caseforprep}.
+Evan is an HIV-negative individual who adheres to a daily PrEP regimen to protect himself from HIV.
+Even finds that for him the side effects and inconveniences associated with taking daily Truvada are worth the protection, noting that he also practices safe sex, and gets tested regularly.
+Evan addresses the hashtag \#truvadawhore, which originated with a Huffington Post article titled "Truvada Whores?"~\cite{truvadawhore} which expressed concern toward the increased sexual risk taking of some Truvada patients.
+Even notes that for HIV-negative Truvada patients like him, who are careful about the risks they are taking, taking Truvada may actually provide more than just a medical protection.
+Truvada users may also be more informed than at risk people who do not use Truvada, because they are more educated and responsible with respect to their sexual health.
 
@@
 
-- Moving towards HIV outbreak prediction.
+In this article we describe a variety of NLP techniques that were used to analyse a tweet corpus to monitor the social media discussion for HIV prevention.
+We identified several notable trends.
+Firstly, we found that PrEP discussion is increasing on social media, Secondly we found that people who mention PrEP also talk about general health, STDs, stigma, and politics.
 
-- Automatically identifying PrEP adoption/adherence sentiment in US population.
+Our sentiment analysis identified both positive and negative PrEP and HIV related tweets.
+We identified two important arguments for an against PrEP.
+One as demonstrated by blog author Steven Banning hypothesises that PrEP overall could lead to unintended, and unhealthy risk seeking recklessness.
+The contrary hypothesis, described by blog author Even Peterson, suggests that PrEP adoption is a product of healthy, responsible at-risk individuals who are gaining HIV protection in an effective form.
+These opposing arguments were identified automatically using large scale social media data.
+Further investigation and data analysis, of social media data, or other health data may be able to quantify PrEP and Truvada's effectiveness in the ongoing effort to prevent HIV infection.
 
-- A lot of information on twitter is from bots, they only cost \$ per bot.
-This along with the character limit and slang makes twitter hard to use, but we've shown that it can be used.
-In fact twitter bots are slowly making twitter unusable because free advertising and marketing.
-Maybe in a future project we make twitter bots to spread information about PrEP.
+Future analyses may also take advantage of the rich Twitter API.
+An additional refinement of the analyses presented here may take a more active approach.
+Rather than simple passive data collection, we may build a twitter bot to interact with HIV and PrEP-tweeters, or conduct a distributed health survey.
+Finally, future HIV and PrEP research may benefit from the incorporation of multiple data sources, either social media sources, health information sources, or both.
 

### 2016-05-15 draft/draft.tex
edit draft

@@
 
-\title{ Mining HIV Trends in Social Media Data}
+\title{ Mining Pre-Exposure Prophylaxis Trends in Social Media Data}
 %
@@
 \begin{CCSXML}
-TODO: this section
+<ccs2012>
+<concept>
+<concept_id>10010405.10010444.10010449</concept_id>
+<concept_desc>Applied computing~Health informatics</concept_desc>
+<concept_significance>500</concept_significance>
+</concept>
+<concept>
+<concept_id>10010147.10010257.10010293.10010309.10011671</concept_id>
+<concept_desc>Computing methodologies~Latent Dirichlet allocation</concept_desc>
+<concept_significance>300</concept_significance>
+</concept>
+<concept>
+<concept_id>10010147.10010257.10010293.10010319</concept_id>
+<concept_desc>Computing methodologies~Learning latent representations</concept_desc>
+<concept_significance>300</concept_significance>
+</concept>
+</ccs2012>
 \end{CCSXML}
+
+\ccsdesc[500]{Applied computing~Health informatics}
+\ccsdesc[300]{Computing methodologies~Latent Dirichlet allocation}
+\ccsdesc[300]{Computing methodologies~Learning latent representations}
+
+\ccsdesc[500]{Applied computing~Health informatics}
 
@@
 
-\keywords{ Social Media, HIV, Topic Modelling, Document Classification}
+\keywords{ Social Media, HIV, Topic Modeling, Document Classification}
 
@@
 Truvada was approved by the Food and Drug Administration (FDA) in 2012 to prevent sexually acquired HIV infection after several positive trials~\cite{grant2010preexposure,thigpen2012antiretroviral} showed that it was safe and effective.
-Despite minimal side effects, and risk protection of up to 99\%, PrEP suffers from uncertain health insurance compensation, the risk of producing drug resistant strains and uninformed health providers and patients~\cite{liu2014early}.
+Despite minimal side effects, and risk protection of up to 99\%, PrEP suffers from uncertain health insurance compensation, the risk of producing drug resistant strains, and uninformed health providers and patients~\cite{liu2014early}.
 Truvada must be taken once a day for full protection.
@@
 Tweets from Twitter consist of short 140 character text messages that may also contain hashtag annotations.
-Twitter has been used as a source of data for large scale opinion mining in public health monitoring contexts to predict the spread of influenza~\cite{aramaki2011twitter}, predict postpartum depression~\cite{de2013predicting}, and examine tobacco use~\cite{myslin2013using}.
+Twitter has been used as a source of data for large scale opinion mining in public health monitoring contexts, to predict the spread of influenza~\cite{aramaki2011twitter}, predict postpartum depression~\cite{de2013predicting}, and examine tobacco use~\cite{myslin2013using}.
 Recently it has also been used for the study of HIV~\cite{young2014methods,young2013online}.
-These studies of HIV have focused on county-level HIV prevalence prediction, and general HIV discussion monitoring, but they have not focused on PrEP related discussion.
+These studies of HIV have focused on county-level HIV prevalence prediction, and general HIV discussion monitoring, but they have not focused on PrEP-related discussion.
 Furthermore, existing HIV social media analyses have not taken full advantage of natural language processing (NLP) techniques to discover semantic information in unstructured text~\cite{young2015big}.
@@
 In the case of a tweet-corpus, document identifiers might include for example document ID, hashtags, and the user who created the document.
-Each of these document-level identifiers is embedded in a similarity space, allowing one to identify similar tweets, hastags and users.
+Each of these document-level identifiers is embedded in a similarity space, allowing one to identify similar tweets, hastags, and users.
 
@@
 A topic is a probability distribution over words that captures a set of related words.
-LDA models are often inferred in practice using Bayesian inference either via collapsed Gibbs sampling or Variational Bayesian methods.
+LDA models are often inferred in practice using Bayesian inference either via collapsed Gibbs sampling or variational Bayesian methods.
 Inspection of the resulting topics allows one to identify relevant terms and the context in which they occur in the corpus.
 
-Dynamic Topic Modelling~\cite{blei2006dynamic} (DTM) is an extension of LDA that produces a series of topic models over time.
-Briefly, the documents in the corpus are divided into several corpuses that are successive in time.
+Dynamic Topic Modeling~\cite{blei2006dynamic} (DTM) is an extension of LDA that produces a series of topic models over time.
+Briefly, the documents in the corpus are divided into several corpora that are successive in time.
 LDA is performed on each corpus to extract a topic distribution.
@@
 Finally we train a sentiment classifier that automatically identifies PrEP-related tweets with positive and negative sentiment.
-Together these results, and these approaches, can be used by public health officials to identify the national PrEP discussion and respond to issues as they arise.
+Together these results, and these approaches, can be used by public health officials to identify trends in the national PrEP discussion and respond to public health issues as they arise.
 
@@
 We sought to determine trends in HIV and PrEP discourse on twitter to inform and coordinate public health efforts aiming to promote PrEP adoption and adherence for at-risk individuals.
-We collected 624,569 tweets containing at least one of the following words 'HIV', 'AIDS', 'truvada', 'prophylaxis', 'imtesting', 'PrEP' from Twitter's streaming API.
+We collected 624,569 tweets containing at least one of the following words 'HIV', 'AIDS', 'truvada', 'prophylaxis', 'imtesting', or 'PrEP' from Twitter's streaming API.
 The tweets were restricted to English language, and the collection dates spanned from the 47th week of 2015 to the 14th week of 2016.
@@
 
+% figure 1
 \begin{figure}
@@
 The first analysis that we performed sought to identify certain keywords, hashtags, tweets and users, that were discussed in HIV and PrEP related contexts.
-Word2Vec and the related method, Paragraph2Vec are unsupervised machine learning methods that have performed well at embedding natural language in a semantic vector space.
-In our analysis, Word2Vec allows us to determine semantically similar words to a query word, while Paragraph2Vec allows us to determine similar tweets, users and hashtags to a query hashtag.
+Word2Vec and the related method, Doc2Vec are unsupervised machine learning methods that have performed well at embedding natural language in a semantic vector space.
+In our analysis, Word2Vec allows us to determine semantically similar words to a query word, while Doc2Vec allows us to determine similar tweets, users and hashtags to a query hashtag.
 
@@
 \begin{tabular}{|l|c|} \hline
-Related word & cosine similarity to PrEP\\ \hline
+Related word & Cosine similarity to PrEP\\ \hline
 truvada & 0.796666\\ \hline
@@
 Doc2Vec allows us to identify the top users, tweets, and hashtags associated with \#prep.
-Note that on Twitter, hashtags are not case sensitive.
+Note that on Twitter, hashtags are not case-sensitive.
 Querying for the top 10 document-level entities associated with \#prep, we again see several PrEP and HIV related hashtags including \#hiv, \#hivprevention, \#truvada, and \#whereisprep.
-We also see a LGBT-related hashtag, \#lgbtmedia16, which indicates a distinct awareness of PrEP in the Gay community.
-This may reflect the known levels of HIV transmission in men who have sex with men~\cite{centers2014hiv}.
+We also see an LGBT-related hashtag, \#lgbtmedia16, which indicates a distinct awareness of PrEP in the Gay community.
+This may reflect the elevated levels of HIV transmission in men who have sex with men~\cite{centers2014hiv}.
 Together the Doc2Vec results show that we can monitor and identify PrEP-related hashtags and tweets.
@@
 Steven notes that the rise of drug-resistant HIV strains has increased, in part due to HIV patients not adhering to to consistent treatment plans.
-He also points out the recent social trend of "bug chasers" individuals who are actively seeking to acquire and spread HIV strains.
-Perhaps the widespread availability of effective HIV medications have desensitized people to a healthy fear of the disease.
+He also points out the recent social trend of "bug chasers," individuals who are actively seeking to acquire and spread HIV strains.
+Steven Banning suggests that the widespread availability of effective HIV medications, may have desensitized healthy fear of the disease in some individuals.
 
@@
 Unfortunately, bots are commonly used on Twitter for advertising and marketing purposes, and sometimes hinder pertinent information retrieval.
-Thus while we observe some noise, our results demonstrate a way to quickly identify and monitor the most viral tweets related to PrEP.
+Thus while we observe some noise, our results demonstrate a method to quickly identify and monitor the most viral tweets related to PrEP.
 As the discussion changes, public health professionals can use this information to quickly identify the most relevant viral sentiment in the online PrEP conversation.
@@
 \begin{tabular}{|l|c|} \hline
-Related hashtag/tweet & cosine similarity to \#PrEP\\ \hline
+Related hashtag/tweet & Cosine similarity to \#PrEP\\ \hline
 \#lgbtmedia16 & 0.739128\\ \hline
@@
 Finally we wanted to visualize the relative similarities of several PrEP-related keywords in a low dimensional space.
-We took keywords that we had identified in our PrEP related queries, along with other HIV-prevention related terms, and visualised their word-vectors in 2 dimensions using t-distributed Stochastic Neighbour Embedding(tSNE)~\cite{van2008visualizing} (Figure 2.
+We took keywords that we had identified in our PrEP related queries, along with other HIV-prevention related terms, and visualized their word-vectors in 2 dimensions using t-distributed Stochastic Neighborhood Embedding(tSNE)~\cite{van2008visualizing} (Figure 2).
 
@@
 Words that are related to HIV discussion, but also used in other contexts (undetectable, testing, awareness) are further away from the HIV/AIDS word-clusters.
-These results provide another mechanism for researchers to visualize and identify relevant trends in PrEP-related keywords.
+These results demonstrate another mechanism for researchers to visualize and identify relevant trends in PrEP-related keywords.
 
-% figure 3
+% figure 2
 \begin{figure*}
@@
 Next we sought to identify some temporal trends in PrEP related trends.
-We used Dynamic Topic Modelling (DTM) to identify how certain topics change over time.
+We used Dynamic Topic Modeling (DTM) to identify how certain topics change over time.
 We specified 10 topics and used each week's worth of tweets, over a 30 week period from the 47th week of 2015 to the 14th week of 2016, as our time points.
@@
 These dynamics may indicate that PrEP discussion is becoming more prevalent.
-This growing trend would be consistent with the fact that while PrEP is still not widely known about among patients and healthcare providers, information about PrEP is slowly building into national awareness.
+This growing trend would be consistent with the fact that while PrEP is still not widely known about among patients and healthcare providers, information about PrEP is slowly entering into national awareness.
 A study in New York City in 2011 indicated that only 36\% of high risk individuals were aware of PrEP~\cite{mehta2011awareness}.
@@
 
-We found at least one other DTM topic that showed interesting behaviour.
+We found at least one other DTM topic that showed interesting behavior.
 We observed that topic 4 captured several keywords related to World AIDS Day (Figure 4).
@@
 Furthermore, while December 1st is World AIDS day, the whole month of December is AIDS Awareness Month.
-We can clearly see the words 'raise' and 'awareness' peak later and last longer than the word 'WorldAIDSDay' implying that it is correlated to the whole month of December.
+We can clearly see the words 'raise' and 'awareness' peak later and last longer than the word 'WorldAIDSDay' indicating that these words are correlated to the whole month of December.
 While our PrEP investigation isn't specifically interested in World AIDS Day, or AIDS Awareness Month, this observation serves as a control to validate our ability to accurately identify temporal events using DTM.
@@
 
-Together, the DTM results demonstrate our ability to extract relevant HIV and PrEP related information from Twitter that accurately captures time-dependant fluctuations.
+Together, the DTM results demonstrate our ability to extract relevant HIV and PrEP related information from Twitter that accurately captures time-dependent fluctuations.
 Public health professionals should be able to monitor these temporal trends to determine the relative interest in PrEP, and other HIV related keywords as they are discussed over time.
@@
 We wanted to identify what Twitter users that mentioned PrEP were discussing in their other tweets.
-We identified users that were most similar to PrEP according to our Paragraph2Vec results, and downloaded their recent tweet history, up to their last 3000 tweets.
-We selected top 500 users that had at least 200 words in the combined tweets of their tweet history.
-For each user, we concatenated all of their tweets, and performed LDA topic modelling on the resulting set of user-timeline documents (Figure 5).
+We identified users that were most similar to PrEP using our Doc2Vec results, then downloaded their recent tweet history, up to their last 3000 tweets.
+We selected the top 500 users that had at least 200 total words in the combined tweets of their tweet history.
+For each user, we concatenated their timeline of tweets, and performed LDA topic modeling on the resulting set of user-timeline documents (Figure 5).
 
@@
 \includegraphics[height=2.5in, width=5in]{LDA_user_timelines}
-\caption{Clustermap of users vs. topics for the top 400 users related to PrEP.}
+\caption{Clustermap of users vs. topics for the top 500 users related to PrEP.}
 \end{figure*}
@@
 Topic 19 is nearby these STD-related topics in PC space, and contains terms related to healthcare and political issues such as "Obamacare" and "ACA" (Affordable Care Act).
-This connection between HIV and other STD prevention, and political discourse may be relevant in PrEP-based HIV prevention efforts, considering there is in some cases no clear precedent for how preventative therapies like PrEP are covered by health insurance~\cite{liu2014early}.
+This connection between HIV, other STD prevention topics, and political discourse may be relevant in PrEP-based HIV prevention efforts, considering there is in some cases no clear precedent for how preventative therapies like PrEP are covered by health insurance~\cite{liu2014early}.
 
@@
 For our final analysis, we sought to get a deeper understanding of the data at the individual tweet level.
-Thus we trained a classifier to classify the sentiment of HIV and PrEP related tweets either positive or negative.
+Thus we trained a classifier to classify the sentiment of HIV and PrEP related tweets to be either positive or negative.
 This classifier would allow public health professionals to quickly identify positive and negative PrEP related tweets to guide HIV prevention efforts.
-We obtained a set of 1.6 million tweets with sentiment labels, either positive or negative from Sanders Analytics (http://www.sananalytics.com/lab/twitter-sentiment/).
+We obtained a set of 1.6 million tweets with binary sentiment labels from Sanders Analytics~\cite{sentimentdata}.
 Then we trained a simple logistic regression classifier on 1.2 million paragraph-vectors from the sentiment dataset.
@@
 There also seems to be concern that use of Truvada may increase the transmission of non-HIV STDs such as Hepatitis C because some PrEP users stop using condoms.
-This may indicate that public health professionals need to stress that PrEP users continue to wear condoms for full protection against other diseases in PrEP-related health information.
+This may indicate that public health professionals need to stress that PrEP users should continue to wear condoms for full protection against other diseases when disseminating PrEP-related health information.
 
@@
 Evan is an HIV-negative individual who adheres to a daily PrEP regimen to protect himself from HIV.
-Even finds that for him the side effects and inconveniences associated with taking daily Truvada are worth the protection, noting that he also practices safe sex, and gets tested regularly.
+Evan finds that for himself, the side effects and inconveniences associated with taking daily Truvada are worth the protection, noting that he also practices safe sex, and gets tested regularly.
 Evan addresses the hashtag \#truvadawhore, which originated with a Huffington Post article titled "Truvada Whores?"~\cite{truvadawhore} which expressed concern toward the increased sexual risk taking of some Truvada patients.
-Even notes that for HIV-negative Truvada patients like him, who are careful about the risks they are taking, taking Truvada may actually provide more than just a medical protection.
-Truvada users may also be more informed than at risk people who do not use Truvada, because they are more educated and responsible with respect to their sexual health.
+Evan notes that many HIV-negative individuals on Truvada like him who know that they may be exposed to HIV, are responsible and cautious about the risks they are taking.
+Individuals on Truvada may also be more informed than at risk people who do not use Truvada, because they are more educated and responsible with respect to their sexual health.
+Further large scale quantitative measurements will be needed to determine whether or not taking Truvada correlates with at risk behaviors.
 
@@
 
-In this article we describe a variety of NLP techniques that were used to analyse a tweet corpus to monitor the social media discussion for HIV prevention.
+In this article we use a variety of NLP techniques to analyze a tweet corpus in order to monitor the national social media discussion for HIV prevention.
 We identified several notable trends.
@@
 
-Our sentiment analysis identified both positive and negative PrEP and HIV related tweets.
-We identified two important arguments for an against PrEP.
-One as demonstrated by blog author Steven Banning hypothesises that PrEP overall could lead to unintended, and unhealthy risk seeking recklessness.
+By picking out the most relevant tweets to PrEP, and also classifying tweets as positive or negative, we quickly identified a handful of specific tweets that highlight important parts of the online PrEP discussion.
+We identified two important arguments for and against PrEP.
+One, as explored by blog author Steven Banning hypothesizes that PrEP adoption could lead to unintended, and unhealthy risk seeking behavior.
 The contrary hypothesis, described by blog author Even Peterson, suggests that PrEP adoption is a product of healthy, responsible at-risk individuals who are gaining HIV protection in an effective form.
@@
 An additional refinement of the analyses presented here may take a more active approach.
-Rather than simple passive data collection, we may build a twitter bot to interact with HIV and PrEP-tweeters, or conduct a distributed health survey.
-Finally, future HIV and PrEP research may benefit from the incorporation of multiple data sources, either social media sources, health information sources, or both.
+Rather than simple passive data collection, we could build a twitter bot to interact with HIV and PrEP-tweeters, or conduct a social media based health survey.
+Finally, future HIV and PrEP research may benefit from the incorporation of multiple data sources, either multiple social media sources, multiple health information sources, or both.
 

### 2016-05-15 draft/draft.tex
fix typo

@@
 One, as explored by blog author Steven Banning hypothesizes that PrEP adoption could lead to unintended, and unhealthy risk seeking behavior.
-The contrary hypothesis, described by blog author Even Peterson, suggests that PrEP adoption is a product of healthy, responsible at-risk individuals who are gaining HIV protection in an effective form.
+The contrary hypothesis, described by blog author Evan Peterson, suggests that PrEP adoption is a product of healthy, responsible at-risk individuals who are gaining HIV protection in an effective form.
 These opposing arguments were identified automatically using large scale social media data.

### 2016-05-16 draft/draft.tex
update draft

@@
 
-\title{ Mining Pre-Exposure Prophylaxis Trends in Social Media Data}
+\title{ Mining Pre-Exposure Prophylaxis Trends in Social Media}
 %
@@
 % 2nd. author
+\alignauthor
+Jane Kelly\\
+       \affaddr{Georgia Department of Public Health}\\
+       \affaddr{Atlanta, Georgia}\\
+       \email{Jane.Kelly@dph.ga.gov}
+\and
+% 3rd author
+\alignauthor
+Timothy Heckman\\
+       \affaddr{College of Public Health}\\
+       \affaddr{University of Georgia}\\
+       \affaddr{Athens, Georgia}\\
+       \email{heckman@uga.edu}
+% 4th author
 \alignauthor
@@
 
-One recently developed tool for NLP, called Word2Vec, is a connectionist method that embeds words as word-vectors in a semantic space that captures substitution-similarity~\cite{mikolov2013efficient}.
-There are several forms of Word2Vec, though the most popular version, Skip-gram Negative Sampling (SGNS), has been shown to perform well at producing word-vectors that capture important word relationships.
+One recently developed tool for NLP, called word2vec, is a connectionist method that embeds words as word-vectors in a semantic space that captures substitution-similarity~\cite{mikolov2013efficient}.
+There are several forms of word2vec, though the most popular version, Skip-gram Negative Sampling (SGNS), has been shown to perform well at producing word-vectors that capture important word relationships.
 This includes most notably word analogies.
 
-Word2Vec is also used as a preprocessing step for additional analyses that start from pre-trained word-vectors.
-Doc2Vec~\cite{le2014distributed} is a method that produces a document-vector for each document, and each document-level identifier.
+Word2vec is also used as a preprocessing step for additional analyses that start from pre-trained word-vectors.
+Doc2vec~\cite{le2014distributed} is a method that produces a document-vector for each document, and each document-level identifier.
 In the case of a tweet-corpus, document identifiers might include for example document ID, hashtags, and the user who created the document.
@@
 The first analysis that we performed sought to identify certain keywords, hashtags, tweets and users, that were discussed in HIV and PrEP related contexts.
-Word2Vec and the related method, Doc2Vec are unsupervised machine learning methods that have performed well at embedding natural language in a semantic vector space.
-In our analysis, Word2Vec allows us to determine semantically similar words to a query word, while Doc2Vec allows us to determine similar tweets, users and hashtags to a query hashtag.
+Word2vec and the related method, doc2vec are unsupervised machine learning methods that have performed well at embedding natural language in a semantic vector space.
+In our analysis, word2vec allows us to determine semantically similar words to a query word, while doc2vec allows us to determine similar tweets, users and hashtags to a query hashtag.
 
-We trained a Word2Vec model, and queried for the top 10 word-vectors related to the term PrEP (Table 1).
+We trained a word2vec model, and queried for the top 10 word-vectors related to the term PrEP (Table 1).
 We found several HIV/AIDS related events, WorldAIDSDay, HLM2016AIDS, ICASA2015, as well as the PrEP drug Truvada, and the term HIV.
@@
 \centering
-\caption{Cosine similarity to word-vector "PrEP"}
+\caption{Cosine similarity to word-vector ``PrEP"}
 \begin{tabular}{|l|c|} \hline
@@
 
-Doc2Vec allows us to identify the top users, tweets, and hashtags associated with \#prep.
+Doc2vec allows us to identify the top users, tweets, and hashtags associated with \#prep.
 Note that on Twitter, hashtags are not case-sensitive.
@@
 This may reflect the elevated levels of HIV transmission in men who have sex with men~\cite{centers2014hiv}.
-Together the Doc2Vec results show that we can monitor and identify PrEP-related hashtags and tweets.
+Together the doc2vec results show that we can monitor and identify PrEP-related hashtags and tweets.
 
 Interestingly, we also found 3 tweets and 1 user in the top 10 doc2vec results for \#prep.
-Tweet 702179860983189504 has content spreading HIV prevention awareness: "\#StoneColdVideoTODAY if You see this 13 symptoms.
+Tweet 702179860983189504 has content spreading HIV prevention awareness: ``\#StoneColdVideoTODAY if You see this 13 symptoms.
 Do HIV Test Immediately.
 Must Read".
-Conversely tweet 708519265540907010 has content that calls into doubt the usefulness of PrEP: "Checkout why PrEP is hurting the cause \& \#JoinTheConversation \#LGBTQIA".
+Conversely tweet 708519265540907010 has content that calls into doubt the usefulness of PrEP: ``Checkout why PrEP is hurting the cause \& \#JoinTheConversation \#LGBTQIA".
 
@@
 Steven notes that the rise of drug-resistant HIV strains has increased, in part due to HIV patients not adhering to to consistent treatment plans.
-He also points out the recent social trend of "bug chasers," individuals who are actively seeking to acquire and spread HIV strains.
+He also points out the recent social trend of ``bug chasers," individuals who are actively seeking to acquire and spread HIV strains.
 Steven Banning suggests that the widespread availability of effective HIV medications, may have desensitized healthy fear of the disease in some individuals.
@@
 \centering
-\caption{Cosine similarity to document-vector "\#PrEP"}
+\caption{Cosine similarity to document-vector ``\#PrEP"}
 \begin{tabular}{|l|c|} \hline
@@
 It is possible that stigma, and misinformation is leading to greater levels of PrEP discussion on twitter.
-We will get more specific, granular understanding of the PrEP discourse in our sentiment analysis section below (see section "Sentiment Classification").
+We will get more specific, granular understanding of the PrEP discourse in our sentiment analysis section below (see section ``Sentiment Classification").
 
@@
 We observed that topic 4 captured several keywords related to World AIDS Day (Figure 4).
-We can see that "WorldAIDSDay", and "Can" peak in the 47th week of 2015 and then decline into 2016.
+We can see that ``WorldAIDSDay", and ``Can" peak in the 47th week of 2015 and then decline into 2016.
 This correlates well with the actual date of World AIDS Day, December 1st.
@@
 We wanted to identify what Twitter users that mentioned PrEP were discussing in their other tweets.
-We identified users that were most similar to PrEP using our Doc2Vec results, then downloaded their recent tweet history, up to their last 3000 tweets.
+We identified users that were most similar to PrEP using our doc2vec results, then downloaded their recent tweet history, up to their last 3000 tweets.
 We selected the top 500 users that had at least 200 total words in the combined tweets of their tweet history.
@@
 We specified 100 topics, and found that only one of them was related to HIV (topic number 13, see Figure 5) representing about 2\% of the marginal topic distribution.
-Topic 13 contained top terms "hivaids", "pepfar", "stigma" and "aidsgov".
+Topic 13 contained top terms ``hivaids", ``pepfar", ``stigma" and ``aidsgov".
 PEPFAR is a governmental organization, The United States President's Emergency Plan for AIDS Relief, that is focused on combating the spread of AIDS internationally.
@@
 Some of the STD-related topics included terms related to LGBTQ, including the social networking platform Grindr in topic 17.
-Other terms related to STD's include prevention terms such as "CDC", "condoms", and "gettested".
-Topic 19 is nearby these STD-related topics in PC space, and contains terms related to healthcare and political issues such as "Obamacare" and "ACA" (Affordable Care Act).
+Other terms related to STD's include prevention terms such as ``CDC", ``condoms", and ``gettested".
+Topic 19 is nearby these STD-related topics in PC space, and contains terms related to healthcare and political issues such as ``Obamacare" and ``ACA" (Affordable Care Act).
 This connection between HIV, other STD prevention topics, and political discourse may be relevant in PrEP-based HIV prevention efforts, considering there is in some cases no clear precedent for how preventative therapies like PrEP are covered by health insurance~\cite{liu2014early}.
 
-One of the top words from the HIV-related topic, topic 13, was the term "stigma", the term "endstigma" was also found in topic 17.
+One of the top words from the HIV-related topic, topic 13, was the term ``stigma", the term ``endstigma" was also found in topic 17.
 Previous studies have shown a variety of stigmas associated and HIV have hampered prevention efforts~\cite{liu2014early}.
 Our observation of stigma related terms corroborates that there is some discussion of stigma in the context of HIV on Twitter.
-Public health professionals may be able use the prevalence of the term "stigma" as a way to monitor the efficacy of efforts to end HIV related stigmas.
+Public health professionals may be able use the prevalence of the term ``stigma" as a way to monitor the efficacy of efforts to end HIV related stigmas.
 
@@
 Category & Text\\ \hline
-General & "RT TOPublicHealth The Works provides testing for HIV anonymous \& rapid test available . Call 416-392-0520 for more info"\\ \hline
-General & "RT FCAA ejaforg announced 5.4 million in grants to support orgs addressing \#HIV in new \& innovative ways!"\\ \hline
-General & "RT HillaryClinton A note on the fight against HIV and AIDS and the people who really started the conversation."\\ \hline
+General & ``RT TOPublicHealth The Works provides testing for HIV anonymous \& rapid test available . Call 416-392-0520 for more info"\\ \hline
+General & ``RT FCAA ejaforg announced 5.4 million in grants to support orgs addressing \#HIV in new \& innovative ways!"\\ \hline
+General & ``RT HillaryClinton A note on the fight against HIV and AIDS and the people who really started the conversation."\\ \hline
 
-PrEP specific & "He won't use condoms because intimacy means more than his health. but he's discovered PrEP. thank goodness."\\ \hline
-PrEP specific & "PrEP Queensland Aids Council, \#HIV Foundation, Queensland."\\ \hline
-PrEP specific & "RT JDatTheBody At the core of our programs is belief that young ppl can succeed in take PrEP for HIV prevention. \#NHPC2015"\\ \hline
+PrEP specific & ``He won't use condoms because intimacy means more than his health. but he's discovered PrEP. thank goodness."\\ \hline
+PrEP specific & ``PrEP Queensland Aids Council, \#HIV Foundation, Queensland."\\ \hline
+PrEP specific & ``RT JDatTheBody At the core of our programs is belief that young ppl can succeed in take PrEP for HIV prevention. \#NHPC2015"\\ \hline
 
-Truvada specific & "RT CDC\_HIVAIDS Expanding testing, treatment, \& \#PrEP could prevent up to 185k new \#HIV infections"\\ \hline
-Truvada specific & "Another reason 4 \#Ireland \& \#UK 2 immediately approve \#truvada \& \#PrEP 2 stop \#HIV infections . arleavitt AodhanORiordain MerchantsQuayIR"\\ \hline
-Truvada specific & "RT EvanJPeterson For \#worldAIDSday my early \#PrEP arcticle in strangerslog, art by leviathanleague \#hiv \#truvada \#truvadawhore"\\ \hline
+Truvada specific & ``RT CDC\_HIVAIDS Expanding testing, treatment, \& \#PrEP could prevent up to 185k new \#HIV infections"\\ \hline
+Truvada specific & ``Another reason 4 \#Ireland \& \#UK 2 immediately approve \#truvada \& \#PrEP 2 stop \#HIV infections . arleavitt AodhanORiordain MerchantsQuayIR"\\ \hline
+Truvada specific & ``RT EvanJPeterson For \#worldAIDSday my early \#PrEP arcticle in strangerslog, art by leviathanleague \#hiv \#truvada \#truvadawhore"\\ \hline
 
@@
 Category & Text\\ \hline
-General & "Also, how f***ing vile of Hillary to say. Reagan did f***ing NOTHING during the AIDS epidemic until it was too late. What a stupid old hag."\\ \hline
-General & "I wonder why he beat her a** when she was tryna leave like she wasn't gone be running back when she found out she had HIV \& nobody want her"\\ \hline
-General & "Aaannd. Hillary Clinton breathes a sigh of relief that Twitter has left its outrage of her AIDS comments behind to tend to Drumpf debacle."\\ \hline
+General & ``Also, how f***ing vile of Hillary to say. Reagan did f***ing NOTHING during the AIDS epidemic until it was too late. What a stupid old hag."\\ \hline
+General & ``I wonder why he beat her a** when she was tryna leave like she wasn't gone be running back when she found out she had HIV \& nobody want her"\\ \hline
+General & ``Aaannd. Hillary Clinton breathes a sigh of relief that Twitter has left its outrage of her AIDS comments behind to tend to Drumpf debacle."\\ \hline
 
-PrEP specific & "RT gaston\_croupier \#Truvada patent's not expired yet but it is sold online as a generic drug? There's something rotten in internet \#PrEP h"\\ \hline
-PrEP specific & "Equality\_MI Syph \& Hep C have gone up 550\% in Gay Men bc many feel tht bc they're on PrEP, they don't need condoms. HIV isn't the only STI."\\ \hline
-PrEP specific & "Xaviom8 in interviews he says he was adherent. strain was highly resistant, and Truvada wouldn't have blocked it anyways. PrEP didn't fail."\\ \hline
+PrEP specific & ``RT gaston\_croupier \#Truvada patent's not expired yet but it is sold online as a generic drug? There's something rotten in internet \#PrEP h"\\ \hline
+PrEP specific & ``Equality\_MI Syph \& Hep C have gone up 550\% in Gay Men bc many feel tht bc they're on PrEP, they don't need condoms. HIV isn't the only STI."\\ \hline
+PrEP specific & ``Xaviom8 in interviews he says he was adherent. strain was highly resistant, and Truvada wouldn't have blocked it anyways. PrEP didn't fail."\\ \hline
 
-Truvada specific & "not surprised at all that someone got HIV on truvada. people get pregnant on birth control. tomato-condoms are still important-tomahto"\\ \hline
-Truvada specific & "Now reading that truvada does not protect against certain strains of the HIV virus. Yet people want to take that risk.."\\ \hline
-Truvada specific & "I think I have conjunctivitis unless truvada cured it overnight cuz im not feeling as horrible today as last night"\\ \hline
+Truvada specific & ``not surprised at all that someone got HIV on truvada. people get pregnant on birth control. tomato-condoms are still important-tomahto"\\ \hline
+Truvada specific & ``Now reading that truvada does not protect against certain strains of the HIV virus. Yet people want to take that risk.."\\ \hline
+Truvada specific & ``I think I have conjunctivitis unless truvada cured it overnight cuz im not feeling as horrible today as last night"\\ \hline
 
@@
 
-The last tweet in the positive tweets table (Table 3), referencing the hashtag "\#truvadawhore", links to a blog article written by Evan Peterson titled "The Case for PrEP, or How I Learned to Stop Worrying and Love HIV-Positive Guys"~\cite{caseforprep}.
+The last tweet in the positive tweets table (Table 3), referencing the hashtag ``\#truvadawhore", links to a blog article written by Evan Peterson titled ``The Case for PrEP, or How I Learned to Stop Worrying and Love HIV-Positive Guys"~\cite{caseforprep}.
 Evan is an HIV-negative individual who adheres to a daily PrEP regimen to protect himself from HIV.
 Evan finds that for himself, the side effects and inconveniences associated with taking daily Truvada are worth the protection, noting that he also practices safe sex, and gets tested regularly.
-Evan addresses the hashtag \#truvadawhore, which originated with a Huffington Post article titled "Truvada Whores?"~\cite{truvadawhore} which expressed concern toward the increased sexual risk taking of some Truvada patients.
+Evan addresses the hashtag \#truvadawhore, which originated with a Huffington Post article titled ``Truvada Whores?"~\cite{truvadawhore} which expressed concern toward the increased sexual risk taking of some Truvada patients.
 Evan notes that many HIV-negative individuals on Truvada like him who know that they may be exposed to HIV, are responsible and cautious about the risks they are taking.

### 2016-05-20 draft/draft.tex
revise draft

@@
 Our results show that we can identify PrEP and HIV discussion dynamics over time, and PrEP-related tweets with positive and negative sentiment.
-These results can be used by public health professionals to monitor PrEP discussion trends, and identify strategies to improve HIV prevention.
+These results can be used by public health professionals to monitor PrEP discussion trends and identify strategies to improve HIV prevention.
 
@@
 Word2vec is also used as a preprocessing step for additional analyses that start from pre-trained word-vectors.
-Doc2vec~\cite{le2014distributed} is a method that produces a document-vector for each document, and each document-level identifier.
-In the case of a tweet-corpus, document identifiers might include for example document ID, hashtags, and the user who created the document.
+Doc2vec~\cite{le2014distributed} is one such method that uses pre-trained word-vectors to produce a document-vector for each document-level attribute.
+In the case of a tweet-corpus, document identifiers might include tweet ID, hashtags, and the user who created the tweet.
 Each of these document-level identifiers is embedded in a similarity space, allowing one to identify similar tweets, hastags, and users.
@@
 We identify critical PrEP related terms, users, hashtags and tweets.
-We identify PrEP discussion trends over time, and identify other topics that people who tweet about PrEP, also tweet about.
+We identify PrEP discussion trends over time, and identify other topics that co-occur with who tweet about PrEP.
 Finally we train a sentiment classifier that automatically identifies PrEP-related tweets with positive and negative sentiment.
@@
 \section{Results}
-We sought to determine trends in HIV and PrEP discourse on twitter to inform and coordinate public health efforts aiming to promote PrEP adoption and adherence for at-risk individuals.
+We sought to determine trends in HIV and PrEP discourse on Twitter to inform and coordinate public health efforts aiming to promote PrEP adoption and adherence for at-risk individuals.
 We collected 624,569 tweets containing at least one of the following words 'HIV', 'AIDS', 'truvada', 'prophylaxis', 'imtesting', or 'PrEP' from Twitter's streaming API.
@@
 The first analysis that we performed sought to identify certain keywords, hashtags, tweets and users, that were discussed in HIV and PrEP related contexts.
-Word2vec and the related method, doc2vec are unsupervised machine learning methods that have performed well at embedding natural language in a semantic vector space.
+Word2vec and the related method, doc2vec, are unsupervised machine learning methods that have performed well at embedding natural language in a semantic vector space.
 In our analysis, word2vec allows us to determine semantically similar words to a query word, while doc2vec allows us to determine similar tweets, users and hashtags to a query hashtag.
@@
 The article, authored by Steven Banning, an HIV positive individual, expresses concerns about how new HIV treatments, like PrEP are being adopted by the HIV community.
-Steven notes that treatments for HIV positive individuals, and treatments to prevent HIV such as PrEP have made HIV a much more treatable disease than it was in the 1980's.
+Steven notes that treatments for HIV positive individuals, and treatments to prevent HIV such as PrEP, have made HIV a much more treatable disease than it was in the 1980's.
 These medical advances may have led in part to some unintended medical and social consequences.
@@
 He also points out the recent social trend of ``bug chasers," individuals who are actively seeking to acquire and spread HIV strains.
-Steven Banning suggests that the widespread availability of effective HIV medications, may have desensitized healthy fear of the disease in some individuals.
+Steven Banning suggests that the widespread availability of effective HIV medications, may have desensitized a healthy sense of fear of the disease in some individuals.
 
@@
 We identified two topics that showed relevant trends.
-In topic 5 we see that the keyword 'PrEP' increases over time, while 'prevention', 'drug' and 'risk' remain constant (Figure 3).
-The term 'pill', also from topic 5, declines overtime.
+In topic 5 we see that the keyword `PrEP' increases over time, while `prevention', `drug' and `risk' remain constant (Figure 3).
+The term `pill', also from topic 5, declines overtime.
 These dynamics may indicate that PrEP discussion is becoming more prevalent.
@@
 
-Other HIV prevention related words such as 'pill', 'prevention' and 'drug' serve as negative controls.
+Other HIV prevention related words such as `pill', `prevention' and `drug' serve as negative controls.
 They are related to PrEP, but also used in other medical contexts.
@@
 Furthermore, while December 1st is World AIDS day, the whole month of December is AIDS Awareness Month.
-We can clearly see the words 'raise' and 'awareness' peak later and last longer than the word 'WorldAIDSDay' indicating that these words are correlated to the whole month of December.
+We can clearly see the words `raise' and `awareness' peak later and last longer than the word `WorldAIDSDay' indicating that these words are correlated to the whole month of December.
 While our PrEP investigation isn't specifically interested in World AIDS Day, or AIDS Awareness Month, this observation serves as a control to validate our ability to accurately identify temporal events using DTM.
@@
 \includegraphics[height=2.5in, width=5in]{LDA_user_timelines}
-\caption{Clustermap of users vs. topics for the top 500 users related to PrEP.}
+\caption{LDA topic modeling for the top 500 users related to PrEP.}
 \end{figure*}
@@
 Our observation of stigma related terms corroborates that there is some discussion of stigma in the context of HIV on Twitter.
-Public health professionals may be able use the prevalence of the term ``stigma" as a way to monitor the efficacy of efforts to end HIV related stigmas.
+Public health professionals may be able use the prevalence of the term ``endstigma" as a way to monitor the efficacy of efforts to end HIV related stigmas.
 
@@
 
-Previously, we used analyses to summarize the whole Twitter corpus to produce high level trends.
+Previously, we used analyses to summarize the whole Twitter corpus to extract high level trends.
 For our final analysis, we sought to get a deeper understanding of the data at the individual tweet level.
@@
 This was especially important because our training and testing data, while both sets of tweets, were separate datasets.
-We then used this trained classifier to classify our PrEP related tweets into positive or negative sentiment labels.
-We identified the most positive, and most negative tweets, by log probability, on our full dataset, and on tweets that specifically mention either PrEP or Truvada.
+We used this trained classifier to classify our PrEP related tweets into positive or negative sentiment labels.
+We identified the most positive, and the most negative tweets, by log probability, on our full dataset, and positive and negative tweets that specifically mention either PrEP or Truvada.
 We provide the text from the top three positive and negative tweets from each of the three datasets (Table 3, Table 4).
@@
 While the sentiment classification doesn't have perfect sentiment accuracy, we can see in general that the positive tweets are disseminating information about the efficacy and benefits of PrEP related preventions (Table 3).
-The positive tweets indicate that PrEP public health informational efforts have had some effect disseminating PrEP information on Twitter.
+The positive tweets indicate that PrEP public health informational efforts have had some effect disseminating useful PrEP information on Twitter.
 
@@
 Finally we see some contention over national political leadership in the effort to prevent HIV.
-While political discussions can often get heated, especially on Twitter, the contention can harm concerted efforts to provide consent governmental leadership in HIV prevention.
+While political discussions can often get heated, especially on Twitter, the contention can harm concerted efforts to provide consistent governmental leadership in HIV prevention.
 Public health officials may consider stressing that unity in health policy at the federal level is important to protect the population from the spread of HIV.
@@
 Evan addresses the hashtag \#truvadawhore, which originated with a Huffington Post article titled ``Truvada Whores?"~\cite{truvadawhore} which expressed concern toward the increased sexual risk taking of some Truvada patients.
-Evan notes that many HIV-negative individuals on Truvada like him who know that they may be exposed to HIV, are responsible and cautious about the risks they are taking.
-Individuals on Truvada may also be more informed than at risk people who do not use Truvada, because they are more educated and responsible with respect to their sexual health.
-Further large scale quantitative measurements will be needed to determine whether or not taking Truvada correlates with at risk behaviors.
+Evan provides a rebuttal, noting that many HIV-negative individuals on Truvada, including himself and people he knows, are responsible and cautious about the risks they are taking.
+He explains that taking daily Truvada may actually be an indication that individuals are more educated and responsible with respect to their sexual health.
+Further large scale quantitative measurements, including large scale medical surveys, will be needed to determine whether or not taking Truvada correlates positively or negatively with risk-taking behaviors.
 
@@
 We identified several notable trends.
-Firstly, we found that PrEP discussion is increasing on social media, Secondly we found that people who mention PrEP also talk about general health, STDs, stigma, and politics.
+We found that PrEP discussion activity is increasing on social media, and also that people who mention PrEP also talk about general health, STDs, stigma, and politics.
 
@@
 One, as explored by blog author Steven Banning hypothesizes that PrEP adoption could lead to unintended, and unhealthy risk seeking behavior.
-The contrary hypothesis, described by blog author Evan Peterson, suggests that PrEP adoption is a product of healthy, responsible at-risk individuals who are gaining HIV protection in an effective form.
+The contrary hypothesis, described by blog author Evan Peterson, suggests that PrEP adoption is a product of healthy, responsible at-risk individuals who are gaining an effective form of HIV protection.
 These opposing arguments were identified automatically using large scale social media data.
-Further investigation and data analysis, of social media data, or other health data may be able to quantify PrEP and Truvada's effectiveness in the ongoing effort to prevent HIV infection.
+Further investigation and data analysis, of social media data together with other health data may be able to quantify PrEP and Truvada's effectiveness in the ongoing effort to prevent HIV infection.
 
-Future analyses may also take advantage of the rich Twitter API.
-An additional refinement of the analyses presented here may take a more active approach.
-Rather than simple passive data collection, we could build a twitter bot to interact with HIV and PrEP-tweeters, or conduct a social media based health survey.
-Finally, future HIV and PrEP research may benefit from the incorporation of multiple data sources, either multiple social media sources, multiple health information sources, or both.
+Future analyses may also take further advantage of the rich Twitter API.
+Rather than simple passive data collection, we could build a twitter bot to interact with HIV and PrEP-tweeters, to conduct a large scale social-media-based health survey.
 
@@
 
-Acknowledgements (optional) go here.
+We would like to acknowledge the Twitter streaming API, which we used to collect HIV and PrEP related tweets over a 30 week period from late 2015 to early 2016.
+Also, we used the gensim python library for our working implementations of word2vec, doc2vec, LDA, and DTM.
+A repository containing the scripts used in this analysis (but no data) is available at https://github.com/quinngroup/sm\_w2v.
 

### 2016-08-03 IEEEtran/bare_conf.tex

--- 2016-05-20 draft/draft.tex
@@
-% This is "sig-alternate.tex" V2.1 April 2013
-% This file should be compiled with V2.5 of "sig-alternate.cls" May 2012
+%% bare_conf.tex
+%% V1.4b
+%% 2015/08/26
+%% by Michael Shell
+%% See:
+%% http://www.michaelshell.org/
+%% for current contact information.
+%%
+%% This is a skeleton file demonstrating the use of IEEEtran.cls
+%% (requires IEEEtran.cls version 1.8b or later) with an IEEE
+%% conference paper.
+%%
+%% Support sites:
+%% http://www.michaelshell.org/tex/ieeetran/
+%% http://www.ctan.org/pkg/ieeetran
+%% and
+%% http://www.ieee.org/
+
+%%*************************************************************************
+%% Legal Notice:
+%% This code is offered as-is without any warranty either expressed or
+%% implied; without even the implied warranty of MERCHANTABILITY or
+%% FITNESS FOR A PARTICULAR PURPOSE! 
+%% User assumes all risk.
+%% In no event shall the IEEE or any contributor to this code be liable for
+%% any damages or losses, including, but not limited to, incidental,
+%% consequential, or any other damages, resulting from the use or misuse
+%% of any information contained here.
+%%
+%% All comments are the opinions of their respective authors and are not
+%% necessarily endorsed by the IEEE.
+%%
+%% This work is distributed under the LaTeX Project Public License (LPPL)
+%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
+%% distributed and modified. A copy of the LPPL, version 1.3, is included
+%% in the base LaTeX documentation of all distributions of LaTeX released
+%% 2003/12/01 or later.
+%% Retain all contribution notices and credits.
+%% ** Modified files should be clearly indicated as such, including  **
+%% ** renaming them and changing author support contact information. **
+%%*************************************************************************
+
+% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
+% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
+% *** with production work. The IEEE's font choices and paper sizes can   ***
+% *** trigger bugs that do not appear when using other class files.       ***                          ***
+% The testflow support page is at:
+% http://www.michaelshell.org/tex/testflow/
+
+\documentclass[conference]{IEEEtran}
+% Some Computer Society conferences also require the compsoc mode option,
+% but others use the standard conference format.
 %
-% This example file demonstrates the use of the 'sig-alternate.cls'
-% V2.5 LaTeX2e document class file. It is for those submitting
-% articles to ACM Conference Proceedings WHO DO NOT WISH TO
-% STRICTLY ADHERE TO THE SIGS (PUBS-BOARD-ENDORSED) STYLE.
-% The 'sig-alternate.cls' file will produce a similar-looking,
-% albeit, 'tighter' paper resulting in, invariably, fewer pages.
+% If IEEEtran.cls has not been installed into the LaTeX system files,
+% manually specify the path to it like:
+% \documentclass[conference]{../sty/IEEEtran}
+
+% Some very useful LaTeX packages include:
+% (uncomment the ones you want to load)
+
+% *** MISC UTILITY PACKAGES ***
 %
-% ----------------------------------------------------------------------------------------------------------------
-% This .tex file (and associated .cls V2.5) produces:
-%       1) The Permission Statement
-%       2) The Conference (location) Info information
-%       3) The Copyright Line with ACM data
-%       4) NO page numbers
+%\usepackage{ifpdf}
+% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
+% compilation based on whether the output is pdf or dvi.
+% usage:
+% \ifpdf
+%   % pdf code
+% \else
+%   % dvi code
+% \fi
+% The latest version of ifpdf.sty can be obtained from:
+% http://www.ctan.org/pkg/ifpdf
+% Also, note that IEEEtran.cls V1.7 and later provides a builtin
+% \ifCLASSINFOpdf conditional that works the same way.
+% When switching from latex to pdflatex and vice-versa, the compiler may
+% have to be run twice to clear warning/error messages.
+
+% *** CITATION PACKAGES ***
 %
-% as against the acm_proc_article-sp.cls file which
-% DOES NOT produce 1) thru' 3) above.
+%\usepackage{cite}
+% cite.sty was written by Donald Arseneau
+% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
+% \cite{} output to follow that of the IEEE. Loading the cite package will
+% result in citation numbers being automatically sorted and properly
+% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
+% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
+% \cite will automatically add leading space, if needed. Use cite.sty's
+% noadjust option (cite.sty V3.8 and later) if you want to turn this off
+% such as if a citation ever needs to be enclosed in parenthesis.
+% cite.sty is already installed on most LaTeX systems. Be sure and use
+% version 5.0 (2009-03-20) and later if using hyperref.sty.
+% The latest version can be obtained at:
+% http://www.ctan.org/pkg/cite
+% The documentation is contained in the cite.sty file itself.
+
+% *** GRAPHICS RELATED PACKAGES ***
 %
-% Using 'sig-alternate.cls' you have control, however, from within
-% the source .tex file, over both the CopyrightYear
-% (defaulted to 200X) and the ACM Copyright Data
-% (defaulted to X-XXXXX-XX-X/XX/XX).
-% e.g.
-% \CopyrightYear{2007} will cause 2007 to appear in the copyright line.
-% \crdata{0-12345-67-8/90/12} will cause 0-12345-67-8/90/12 to appear in the copyright line.
+\usepackage[pdftex]{graphicx}
+  % declare the path(s) where your graphic files are
+% \graphicspath{./figs/}
+  % and their extensions so you won't have to specify these with
+  % every instance of \includegraphics
+\DeclareGraphicsExtensions{.pdf,.jpeg,.png}
+
+\ifCLASSINFOpdf
+  % \usepackage[pdftex]{graphicx}
+  % declare the path(s) where your graphic files are
+  % \graphicspath{{../pdf/}{../jpeg/}}
+  % and their extensions so you won't have to specify these with
+  % every instance of \includegraphics
+  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
+\else
+  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
+  % will default to the driver specified in the system graphics.cfg if no
+  % driver is specified.
+  % \usepackage[dvips]{graphicx}
+  % declare the path(s) where your graphic files are
+  % \graphicspath{{../eps/}}
+  % and their extensions so you won't have to specify these with
+  % every instance of \includegraphics
+  % \DeclareGraphicsExtensions{.eps}
+\fi
+% graphicx was written by David Carlisle and Sebastian Rahtz. It is
+% required if you want graphics, photos, etc. graphicx.sty is already
+% installed on most LaTeX systems. The latest version and documentation
+% can be obtained at: 
+% http://www.ctan.org/pkg/graphicx
+% Another good source of documentation is "Using Imported Graphics in
+% LaTeX2e" by Keith Reckdahl which can be found at:
+% http://www.ctan.org/pkg/epslatex
 %
-% ---------------------------------------------------------------------------------------------------------------
-% This .tex source is an example which *does* use
-% the .bib file (from which the .bbl file % is produced).
-% REMEMBER HOWEVER: After having produced the .bbl file,
-% and prior to final submission, you *NEED* to 'insert'
-% your .bbl file into your source .tex file so as to provide
-% ONE 'self-contained' source file.
+% latex, and pdflatex in dvi mode, support graphics in encapsulated
+% postscript (.eps) format. pdflatex in pdf mode supports graphics
+% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
+% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
+% not a bitmapped formats (.jpeg, .png). The IEEE frowns on bitmapped formats
+% which can result in "jaggedy"/blurry rendering of lines and letters as
+% well as large increases in file sizes.
 %
-% ================= IF YOU HAVE QUESTIONS =======================
-% Questions regarding the SIGS styles, SIGS policies and
-% procedures, Conferences etc. should be sent to
-% Adrienne Griscti (griscti@acm.org)
+% You can find documentation about the pdfTeX application at:
+% http://www.tug.org/applications/pdftex
+
+% *** MATH PACKAGES ***
 %
-% Technical questions _only_ to
-% Gerald Murray (murray@hq.acm.org)
-% ===============================================================
+%\usepackage{amsmath}
+% A popular package from the American Mathematical Society that provides
+% many useful and powerful commands for dealing with mathematics.
 %
-% For tracking purposes - this is V2.0 - May 2012
+% Note that the amsmath package sets \interdisplaylinepenalty to 10000
+% thus preventing page breaks from occurring within multiline equations. Use:
+%\interdisplaylinepenalty=2500
+% after loading amsmath to restore such page breaks as IEEEtran.cls normally
+% does. amsmath.sty is already installed on most LaTeX systems. The latest
+% version and documentation can be obtained at:
+% http://www.ctan.org/pkg/amsmath
 
-\documentclass{sig-alternate-05-2015}
+% *** SPECIALIZED LIST PACKAGES ***
+%
+%\usepackage{algorithmic}
+% algorithmic.sty was written by Peter Williams and Rogerio Brito.
+% This package provides an algorithmic environment fo describing algorithms.
+% You can use the algorithmic environment in-text or within a figure
+% environment to provide for a floating algorithm. Do NOT use the algorithm
+% floating environment provided by algorithm.sty (by the same authors) or
+% algorithm2e.sty (by Christophe Fiorio) as the IEEE does not use dedicated
+% algorithm float types and packages that provide these will not provide
+% correct IEEE style captions. The latest version and documentation of
+% algorithmic.sty can be obtained at:
+% http://www.ctan.org/pkg/algorithms
+% Also of interest may be the (relatively newer and more customizable)
+% algorithmicx.sty package by Szasz Janos:
+% http://www.ctan.org/pkg/algorithmicx
 
-%\usepackage [english]{babel}
-%\usepackage [autostyle, english = american]{csquotes}
-%\MakeOuterQuote{"}
-\usepackage{lineno}
+% *** ALIGNMENT PACKAGES ***
+%
+%\usepackage{array}
+% Frank Mittelbach's and David Carlisle's array.sty patches and improves
+% the standard LaTeX2e array and tabular environments to provide better
+% appearance and additional user controls. As the default LaTeX2e table
+% generation code is lacking to the point of almost being broken with
+% respect to the quality of the end results, all users are strongly
+% advised to use an enhanced (at the very least that provided by array.sty)
+% set of table tools. array.sty is already installed on most systems. The
+% latest version and documentation can be obtained at:
+% http://www.ctan.org/pkg/array
+
+% IEEEtran contains the IEEEeqnarray family of commands that can be used to
+% generate multiline equations as well as matrices, tables, etc., of high
+% quality.
+
+% *** SUBFIGURE PACKAGES ***
+%\ifCLASSOPTIONcompsoc
+%  \usepackage[caption=false,font=normalsize,labelfont=sf,textfont=sf]{subfig}
+%\else
+%  \usepackage[caption=false,font=footnotesize]{subfig}
+%\fi
+% subfig.sty, written by Steven Douglas Cochran, is the modern replacement
+% for subfigure.sty, the latter of which is no longer maintained and is
+% incompatible with some LaTeX packages including fixltx2e. However,
+% subfig.sty requires and automatically loads Axel Sommerfeldt's caption.sty
+% which will override IEEEtran.cls' handling of captions and this will result
+% in non-IEEE style figure/table captions. To prevent this problem, be sure
+% and invoke subfig.sty's "caption=false" package option (available since
+% subfig.sty version 1.3, 2005/06/28) as this is will preserve IEEEtran.cls
+% handling of captions.
+% Note that the Computer Society format requires a larger sans serif font
+% than the serif footnote size font used in traditional IEEE formatting
+% and thus the need to invoke different subfig.sty package options depending
+% on whether compsoc mode has been enabled.
+%
+% The latest version and documentation of subfig.sty can be obtained at:
+% http://www.ctan.org/pkg/subfig
+
+% *** FLOAT PACKAGES ***
+%
+%\usepackage{fixltx2e}
+% fixltx2e, the successor to the earlier fix2col.sty, was written by
+% Frank Mittelbach and David Carlisle. This package corrects a few problems
+% in the LaTeX2e kernel, the most notable of which is that in current
+% LaTeX2e releases, the ordering of single and double column floats is not
+% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
+% single column figure to be placed prior to an earlier double column
+% figure.
+% Be aware that LaTeX2e kernels dated 2015 and later have fixltx2e.sty's
+% corrections already built into the system in which case a warning will
+% be issued if an attempt is made to load fixltx2e.sty as it is no longer
+% needed.
+% The latest version and documentation can be found at:
+% http://www.ctan.org/pkg/fixltx2e
+
+%\usepackage{stfloats}
+% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
+% the ability to do double column floats at the bottom of the page as well
+% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
+% LaTeX2e). It also provides a command:
+%\fnbelowfloat
+% to enable the placement of footnotes below bottom floats (the standard
+% LaTeX2e kernel puts them above bottom floats). This is an invasive package
+% which rewrites many portions of the LaTeX2e float routines. It may not work
+% with other packages that modify the LaTeX2e float routines. The latest
+% version and documentation can be obtained at:
+% http://www.ctan.org/pkg/stfloats
+% Do not use the stfloats baselinefloat ability as the IEEE does not allow
+% \baselineskip to stretch. Authors submitting work to the IEEE should note
+% that the IEEE rarely uses double column equations and that authors should try
+% to avoid such use. Do not be tempted to use the cuted.sty or midfloat.sty
+% packages (also by Sigitas Tolusis) as the IEEE does not format its papers in
+% such ways.
+% Do not attempt to use stfloats with fixltx2e as they are incompatible.
+% Instead, use Morten Hogholm'a dblfloatfix which combines the features
+% of both fixltx2e and stfloats:
+%
+% \usepackage{dblfloatfix}
+% The latest version can be found at:
+% http://www.ctan.org/pkg/dblfloatfix
+
+% *** PDF, URL AND HYPERLINK PACKAGES ***
+%
+\usepackage{url}
+% url.sty was written by Donald Arseneau. It provides better support for
+% handling and breaking URLs. url.sty is already installed on most LaTeX
+% systems. The latest version and documentation can be obtained at:
+% http://www.ctan.org/pkg/url
+% Basically, \url{my_url_here}.
+
+% *** Do not adjust lengths that control margins, column widths, etc. ***
+% *** Do not use packages that alter fonts (such as pslatex).         ***
+% There should be no need to do such things with IEEEtran.cls V1.6 and later.
+% (Unless specifically asked to do so by the journal or conference you plan
+% to submit to, of course. )
+
+% correct bad hyphenation here
+\hyphenation{op-tical net-works semi-conduc-tor}
+
 \begin{document}
-\linenumbers
-% Copyright
-\setcopyright{acmcopyright}
-%\setcopyright{acmlicensed}
-%\setcopyright{rightsretained}
-%\setcopyright{usgov}
-%\setcopyright{usgovmixed}
-%\setcopyright{cagov}
-%\setcopyright{cagovmixed}
+%
+% paper title
+% Titles are generally capitalized except for words such as a, an, and, as,
+% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
+% not capitalized unless they are the first or last word of the title.
+% Linebreaks \\ can be used within to get better formatting as desired.
+% Do not put math or special symbols in the title.
+\title{Mining Pre-Exposure Prophylaxis Trends \\ in Social Media}
 
-% DOI
-\doi{10.475/123_4}
+% author names and affiliations
+% use a multiple column layout for up to three different
+% affiliations
+%\author{\IEEEauthorblockN{Michael Shell}
+%\IEEEauthorblockA{School of Electrical and\\Computer Engineering\\
+%Georgia Institute of Technology\\
+%Atlanta, Georgia 30332--0250\\
+%Email: http://www.michaelshell.org/contact.html}
+%\and
+%\IEEEauthorblockN{Homer Simpson}
+%\IEEEauthorblockA{Twentieth Century Fox\\
+%Springfield, USA\\
+%Email: homer@thesimpsons.com}
+%\and
+%\IEEEauthorblockN{James Kirk\\ and Montgomery Scott}
+%\IEEEauthorblockA{Starfleet Academy\\
+%San Francisco, California 96678--2391\\
+%Telephone: (800) 555--1212\\
+%Fax: (888) 555--1212}}
 
-% ISBN
-\isbn{123-4567-24-567/08/06}
+% conference papers do not typically use \thanks and this command
+% is locked out in conference mode. If really needed, such as for
+% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
+% after \documentclass
 
-%Conference
-\conferenceinfo{PLDI '13}{June 16--19, 2013, Seattle, WA, USA}
+% for over three affiliations, or if they all won't fit within the width
+% of the page, use this alternative format:
+% 
+%\author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
+%Homer Simpson\IEEEauthorrefmark{2},
+%James Kirk\IEEEauthorrefmark{3}, 
+%Montgomery Scott\IEEEauthorrefmark{3} and
+%Eldon Tyrell\IEEEauthorrefmark{4}}
+%\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
+%Georgia Institute of Technology,
+%Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
+%\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
+%Email: homer@thesimpsons.com}
+%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
+%Telephone: (800) 555--1212, Fax: (888) 555--1212}
+%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}
 
-\acmPrice{\$15.00}
+% use for special paper notices
+%\IEEEspecialpapernotice{(Invited Paper)}
 
-%
-% --- Author Metadata here ---
-\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
-%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
-%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
-% --- End of Author Metadata ---
+% make the title area
+\maketitle
 
-\title{ Mining Pre-Exposure Prophylaxis Trends in Social Media}
-%
-% You need the command \numberofauthors to handle the 'placement
-% and alignment' of the authors beneath the title.
-%
-% For aesthetic reasons, we recommend 'three authors at a time'
-% i.e. three 'name/affiliation blocks' be placed beneath the title.
-%
-% NOTE: You are NOT restricted in how many 'rows' of
-% "name/affiliations" may appear. We just ask that you restrict
-% the number of 'columns' to three.
-%
-% Because of the available 'opening page real-estate'
-% we ask you to refrain from putting more than six authors
-% (two rows with three columns) beneath the article title.
-% More than six makes the first-page appear very cluttered indeed.
-%
-% Use the \alignauthor commands to handle the names
-% and affiliations for an 'aesthetic maximum' of six authors.
-% Add names, affiliations, addresses for
-% the seventh etc. author(s) as the argument for the
-% \additionalauthors command.
-% These 'additional authors' will be output/set for you
-% without further effort on your part as the last section in
-% the body of your article BEFORE References or any Appendices.
-
-\numberofauthors{2} %  in this sample file, there are a *total*
-% of EIGHT authors. SIX appear on the 'first-page' (for formatting
-% reasons) and the remaining two appear in the \additionalauthors section.
-%
-\author{
-% You can go ahead and credit any number of authors here,
-% e.g. one 'row of three' or two rows (consisting of one row of three
-% and a second row of one, two or three).
-%
-% The command \alignauthor (no curly braces needed) should
-% precede each author name, affiliation/snail-mail address and
-% e-mail address. Additionally, tag each line of
-% affiliation/address with \affaddr, and tag the
-% e-mail address with \email.
-%
-% 1st. author
-\alignauthor
-Patrick Breen\\
-       \affaddr{Institute of Bioinformatics}\\
-       \affaddr{The University of Georgia}\\
-       \affaddr{Athens, Georgia}\\
-       \email{pbreen@uga.edu}       
-% 2nd. author
-\alignauthor
-Jane Kelly\\
-       \affaddr{Georgia Department of Public Health}\\
-       \affaddr{Atlanta, Georgia}\\
-       \email{Jane.Kelly@dph.ga.gov}
-\and
-% 3rd author
-\alignauthor
-Timothy Heckman\\
-       \affaddr{College of Public Health}\\
-       \affaddr{University of Georgia}\\
-       \affaddr{Athens, Georgia}\\
-       \email{heckman@uga.edu}
-% 4th author
-\alignauthor
-Shannon Quinn\titlenote{Corresponding author.}\\
-       \affaddr{Department of Computer Science}\\
-       \affaddr{University of Georgia}\\
-       \affaddr{Athens, Georgia}\\
-       \email{squinn@cs.uga.edu}
-}
-
-\maketitle
+% As a general rule, do not put math, special symbols or citations
+% in the abstract
 \begin{abstract}
 
-Pre-Exposure Prophylaxis (PrEP) is a recently developed therapy for the prevention of Human Immunodeficiency Virus (HIV) transmission.
-The treatment is available as a pill named Truvada and is taken once a day by HIV negative individuals for as much as 99\% protection when exposed to HIV.
-While medically effective, PrEP suffers from high drug costs, HIV-related social stigma, and under-informed health providers and patients.
-Data mining of social media has proven effective in the monitoring of HIV in the United States, but no study has investigated PrEP using social media.
-This paper describes a data mining and machine learning strategy using natural language processing (NLP), that monitors Twitter social media data to identify PrEP discussion trends.
-Our results show that we can identify PrEP and HIV discussion dynamics over time, and PrEP-related tweets with positive and negative sentiment.
-These results can be used by public health professionals to monitor PrEP discussion trends and identify strategies to improve HIV prevention.
-
-%These methods may also be useful to identify and preempt HIV outbreaks before they reach epidemic levels.
+Pre-Exposure Prophylaxis (PrEP) is a ground-breaking biomedical approach to curbing the transmission of Human Immunodeficiency Virus (HIV).
+Truvada, the most common form of PrEP, is a combination of tenofovir and emtricitabine and is a once-daily oral mediation taken by HIV-seronegative persons at elevated risk for HIV infection.
+When taken reliably every day, PrEP can reduce one's risk for HIV infection by as much as 99\%.
+While highly efficacious, PrEP is expensive, somewhat stigmatized, and many health care providers remain uninformed about its benefits.
+Data mining of social media can monitor the spread of HIV in the United States, but no study has investigated PrEP use and sentiment via social media.
+This paper describes a data mining and machine learning strategy using natural language processing (NLP) that monitors Twitter social media data to identify PrEP discussion trends.
+Results showed that we can identify PrEP and HIV discussion dynamics over time, and assign PrEP-related tweets positive or negative sentiment.
+Results can enable public health professionals to monitor PrEP discussion trends and identify strategies to improve HIV prevention via PrEP.
 
@@
 
+% no keywords
+
+% For peer review papers, you can put extra information on the cover
+% page as needed:
+% \ifCLASSOPTIONpeerreview
+% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
+% \fi
 %
-% The code below should be generated by the tool at
-% http://dl.acm.org/ccs.cfm
-% Please copy and paste the code instead of the example below. 
-%
-
-\begin{CCSXML}
-<ccs2012>
-<concept>
-<concept_id>10010405.10010444.10010449</concept_id>
-<concept_desc>Applied computing~Health informatics</concept_desc>
-<concept_significance>500</concept_significance>
-</concept>
-<concept>
-<concept_id>10010147.10010257.10010293.10010309.10011671</concept_id>
-<concept_desc>Computing methodologies~Latent Dirichlet allocation</concept_desc>
-<concept_significance>300</concept_significance>
-</concept>
-<concept>
-<concept_id>10010147.10010257.10010293.10010319</concept_id>
-<concept_desc>Computing methodologies~Learning latent representations</concept_desc>
-<concept_significance>300</concept_significance>
-</concept>
-</ccs2012>
-\end{CCSXML}
-
-\ccsdesc[500]{Applied computing~Health informatics}
-\ccsdesc[300]{Computing methodologies~Latent Dirichlet allocation}
-\ccsdesc[300]{Computing methodologies~Learning latent representations}
-
-\ccsdesc[500]{Applied computing~Health informatics}
-
-%
-% End generated code
-%
-
-%
-%  Use this command to print the description
-%
-\printccsdesc
-
-% We no longer use \terms command
-%\terms{Theory}
-
-\keywords{ Social Media, HIV, Topic Modeling, Document Classification}
+% For peerreview papers, this IEEEtran command inserts a page break and
+% creates the second title. It will be ignored for other modes.
+\IEEEpeerreviewmaketitle
 
 \section{Introduction}
-Pre-exposure prophylaxis (PrEP), a treatment for the prevention of Immunodeficiency Virus (HIV), is marketed under the trade name Truvada.
-Truvada was approved by the Food and Drug Administration (FDA) in 2012 to prevent sexually acquired HIV infection after several positive trials~\cite{grant2010preexposure,thigpen2012antiretroviral} showed that it was safe and effective.
-Despite minimal side effects, and risk protection of up to 99\%, PrEP suffers from uncertain health insurance compensation, the risk of producing drug resistant strains, and uninformed health providers and patients~\cite{liu2014early}.
-Truvada must be taken once a day for full protection.
-In some individuals, adherence is difficult to maintain~\cite{van2012unraveling}, leading to loss of Truvada's effectiveness.
-While public health officials can spread information and monitor the effectiveness of PrEP at the clinic-level, scaled-up data mining on social media data may provide more complete information on PrEP at the national level.
 
-Tweets from Twitter consist of short 140 character text messages that may also contain hashtag annotations.
+Pre-exposure prophylaxis (PrEP), a treatment for the prevention of Human Immunodeficiency Virus (HIV), is marketed under the trade name Truvada.
+Truvada, a combination of tenofovir and emtricitabine, was approved by the Food and Drug Administration (FDA) in 2012 to prevent the transmission of HIV to seronegative persons at elevated risk for HIV infection.
+Several randomized clinical trials showed that PrEP was safe and could reduce one's risk for HIV infection by up to 99\% if taken reliably~\cite{grant2010preexposure,thigpen2012antiretroviral}.
+Despite its minimal side effects and high level of risk protection, PrEP suffers from uncertain health insurance compensation, the risk of producing drug resistant strains, and uninformed health providers and patients~\cite{liu2014early}.
+Truvada must be taken once a day for maximum protection.
+Consistent adherence to PrEP is difficult for some individuals, leading to lower protection rates~\cite{van2012unraveling}.
+While public health officials can disseminate information about and monitor the efficacy of PrEP at the clinic-level, scaled-up data mining on social media data may provide more complete information on facilitators and barriers to PrEP use at the national level.
+
+Twitter, a popular microblogging service, is the social media platform we use in this study.
+``Tweets'' from Twitter consist of short 140 character text messages that may also contain hashtag annotations.
 Twitter has been used as a source of data for large scale opinion mining in public health monitoring contexts, to predict the spread of influenza~\cite{aramaki2011twitter}, predict postpartum depression~\cite{de2013predicting}, and examine tobacco use~\cite{myslin2013using}.
@@
 Furthermore, existing HIV social media analyses have not taken full advantage of natural language processing (NLP) techniques to discover semantic information in unstructured text~\cite{young2015big}.
+
+In this paper we respond to the acknowledged need to harness large scale data in the battle against HIV~\cite{young2015big}.
+We make extensive use of NLP techniques to extract PrEP-related semantic information from a Twitter corpus dataset.
+We identify critical PrEP related terms, users, hashtags and tweets.
+We identify PrEP discussion trends over time, and identify other topics that co-occur with who tweet about PrEP.
+Finally we train a sentiment classifier that automatically identifies PrEP-related tweets with positive and negative sentiment.
+Together these results, and these approaches, can be used by public health officials to identify trends in the national PrEP discussion and respond to public health issues as they arise.
+
+\section{Methods and Data}
 
@@
 
-In this paper we respond to the acknowledged need to harness large scale data in the battle against HIV~\cite{young2015big}.
-We use the above NLP techniques to extract PrEP-related semantic information from a Twitter corpus dataset.
-We identify critical PrEP related terms, users, hashtags and tweets.
-We identify PrEP discussion trends over time, and identify other topics that co-occur with who tweet about PrEP.
-Finally we train a sentiment classifier that automatically identifies PrEP-related tweets with positive and negative sentiment.
-Together these results, and these approaches, can be used by public health officials to identify trends in the national PrEP discussion and respond to public health issues as they arise.
-
-\section{Results}
-We sought to determine trends in HIV and PrEP discourse on Twitter to inform and coordinate public health efforts aiming to promote PrEP adoption and adherence for at-risk individuals.
-We collected 624,569 tweets containing at least one of the following words 'HIV', 'AIDS', 'truvada', 'prophylaxis', 'imtesting', or 'PrEP' from Twitter's streaming API.
+We collected 624,569 tweets containing at least one of the following words `HIV', `AIDS', `truvada', `prophylaxis', `imtesting', or `PrEP' from Twitter's streaming API.
 The tweets were restricted to English language, and the collection dates spanned from the 47th week of 2015 to the 14th week of 2016.
-The tweets were cleaned of exotic characters.
+The tweets were cleaned of exotic characters (non-punctuation, non-alphanumeric characters).
 Before performing topic analysis, we excluded words that were mentioned fewer than 10 times, or more than 0.3 times the number of documents.
@@
 A subset of 14,204 tweets (about 2\%) had geolocation coordinates available.
-We found that these tweets were largely concentrated on US and Canadian metro areas (Figure 1).
+We found that these tweets were largely concentrated on US and Canadian metro areas (Fig.~\ref{fig:map}).
 The tweets did not seem to be over represented in any geographical region of the US.
+
+\section{Results}
+
+We sought to determine trends in HIV and PrEP discourse on Twitter to inform and coordinate public health efforts aiming to promote PrEP adoption and adherence for at-risk individuals.
 
@@
 \centering
-\includegraphics[height=3in, width=4in]{map}
+\includegraphics[scale=0.35]{figs/Fig1}
 \caption{Plot of geolocated tweets.}
+\label{fig:map}
 \end{figure}
@@
 
-We trained a word2vec model, and queried for the top 10 word-vectors related to the term PrEP (Table 1).
+We trained a word2vec model, and queried for the top 10 word-vectors related to the term PrEP (Table~\ref{tbl:w2v}).
 We found several HIV/AIDS related events, WorldAIDSDay, HLM2016AIDS, ICASA2015, as well as the PrEP drug Truvada, and the term HIV.
@@
 \centering
-\caption{Cosine similarity to word-vector ``PrEP"}
+\caption{Cosine similarity to word-vector ``PrEP''}
 \begin{tabular}{|l|c|} \hline
@@
 \hline\end{tabular}
+\label{tbl:w2v}
 \end{table}
@@
 
-Interestingly, we also found 3 tweets and 1 user in the top 10 doc2vec results for \#prep.
+Interestingly, we also found 3 tweets and 1 user in the top 10 doc2vec results for \#prep (Table~\ref{tbl:d2v}).
 Tweet 702179860983189504 has content spreading HIV prevention awareness: ``\#StoneColdVideoTODAY if You see this 13 symptoms.
 Do HIV Test Immediately.
-Must Read".
-Conversely tweet 708519265540907010 has content that calls into doubt the usefulness of PrEP: ``Checkout why PrEP is hurting the cause \& \#JoinTheConversation \#LGBTQIA".
+Must Read''.
+Conversely tweet 708519265540907010 has content that calls into doubt the usefulness of PrEP: ``Checkout why PrEP is hurting the cause \& \#JoinTheConversation \#LGBTQIA''.
 
-We investigated the blog article linked to tweet 708519265540907010\cite{prephurtingcause}.
+We investigated the blog article linked to tweet 708519265540907010~\cite{prephurtingcause}.
 The article, authored by Steven Banning, an HIV positive individual, expresses concerns about how new HIV treatments, like PrEP are being adopted by the HIV community.
@@
 Steven notes that the rise of drug-resistant HIV strains has increased, in part due to HIV patients not adhering to to consistent treatment plans.
-He also points out the recent social trend of ``bug chasers," individuals who are actively seeking to acquire and spread HIV strains.
+He also points out the recent social trend of ``bug chasers,'' individuals who are actively seeking to acquire and spread HIV strains.
 Steven Banning suggests that the widespread availability of effective HIV medications, may have desensitized a healthy sense of fear of the disease in some individuals.
@@
 \centering
-\caption{Cosine similarity to document-vector ``\#PrEP"}
+\caption{Cosine similarity to document-vector ``\#PrEP''}
 \begin{tabular}{|l|c|} \hline
@@
 \hline\end{tabular}
+\label{tbl:d2v}
 \end{table}
@@
 Finally we wanted to visualize the relative similarities of several PrEP-related keywords in a low dimensional space.
-We took keywords that we had identified in our PrEP related queries, along with other HIV-prevention related terms, and visualized their word-vectors in 2 dimensions using t-distributed Stochastic Neighborhood Embedding(tSNE)~\cite{van2008visualizing} (Figure 2).
+We took keywords that we had identified in our PrEP related queries, along with other HIV-prevention related terms, and visualized their word-vectors in 2 dimensions using t-distributed Stochastic Neighborhood Embedding(tSNE)~\cite{van2008visualizing} (Fig.~\ref{fig:tsne}).
 
@@
 \centering
-\includegraphics[height=4in, width=6in]{tSNE_word}
+\includegraphics[height=4in, width=6in]{figs/Fig2}
 \caption{tSNE plot of relevant word-vectors}
+\label{fig:tsne}
 \end{figure*}
@@
 We identified two topics that showed relevant trends.
-In topic 5 we see that the keyword `PrEP' increases over time, while `prevention', `drug' and `risk' remain constant (Figure 3).
+In topic 5 we see that the keyword `PrEP' increases over time, while `prevention', `drug' and `risk' remain constant (Fig.~\ref{fig:prep}).
 The term `pill', also from topic 5, declines overtime.
@@
 It is possible that stigma, and misinformation is leading to greater levels of PrEP discussion on twitter.
-We will get more specific, granular understanding of the PrEP discourse in our sentiment analysis section below (see section ``Sentiment Classification").
+We will get more specific, granular understanding of the PrEP discourse in our sentiment analysis section below (see section ``Sentiment Classification'').
 
@@
 \centering
-\includegraphics[height=2.5in, width=3.5in]{DTMfig1}
+\includegraphics[height=2.5in, width=3.5in]{figs/Fig3}
 \caption{DTM topic 5 (PrEP related topic) word prevalence over time. Date is YYYY-WW.}
+\label{fig:prep}
 \end{figure}
@@
 We found at least one other DTM topic that showed interesting behavior.
-We observed that topic 4 captured several keywords related to World AIDS Day (Figure 4).
-We can see that ``WorldAIDSDay", and ``Can" peak in the 47th week of 2015 and then decline into 2016.
+We observed that topic 4 captured several keywords related to World AIDS Day (Fig.~\ref{fig:aids}).
+We can see that ``WorldAIDSDay'', and ``Can'' peak in the 47th week of 2015 and then decline into 2016.
 This correlates well with the actual date of World AIDS Day, December 1st.
@@
 \centering
-\includegraphics[height=2.5in, width=3.5in]{DTMfig2}
+\includegraphics[height=2.5in, width=3.5in]{figs/Fig4}
 \caption{DTM topic 4 (WorldAIDSDay related topic) word prevalence over time. Date is YYYY-WW.}
+\label{fig:aids}
 \end{figure}
@@
 We selected the top 500 users that had at least 200 total words in the combined tweets of their tweet history.
-For each user, we concatenated their timeline of tweets, and performed LDA topic modeling on the resulting set of user-timeline documents (Figure 5).
+For each user, we concatenated their timeline of tweets, and performed LDA topic modeling on the resulting set of user-timeline documents (Fig.~\ref{fig:lda}).
 
@@
 \centering
-\includegraphics[height=2.5in, width=5in]{LDA_user_timelines}
+\includegraphics[scale=0.5]{figs/Fig5}
 \caption{LDA topic modeling for the top 500 users related to PrEP.}
+\label{fig:lda}
 \end{figure*}
 
-We performed LDA on the users' timelines using the pyLDAvis python package from graphlab~\cite{low2014graphlab}.
+We performed LDA on the users' timelines using the pyLDAvis python package from GraphLab~\cite{low2014graphlab}.
 We specified 100 topics, and found that only one of them was related to HIV (topic number 13, see Figure 5) representing about 2\% of the marginal topic distribution.
-Topic 13 contained top terms ``hivaids", ``pepfar", ``stigma" and ``aidsgov".
+Topic 13 contained top terms ``hivaids'', ``pepfar'', ``stigma'' and ``aidsgov''.
 PEPFAR is a governmental organization, The United States President's Emergency Plan for AIDS Relief, that is focused on combating the spread of AIDS internationally.
@@
 Some of the STD-related topics included terms related to LGBTQ, including the social networking platform Grindr in topic 17.
-Other terms related to STD's include prevention terms such as ``CDC", ``condoms", and ``gettested".
-Topic 19 is nearby these STD-related topics in PC space, and contains terms related to healthcare and political issues such as ``Obamacare" and ``ACA" (Affordable Care Act).
+Other terms related to STD's include prevention terms such as ``CDC'', ``condoms'', and ``gettested''.
+Topic 19 is nearby these STD-related topics in PC space, and contains terms related to healthcare and political issues such as ``Obamacare'' and ``ACA'' (Affordable Care Act).
 This connection between HIV, other STD prevention topics, and political discourse may be relevant in PrEP-based HIV prevention efforts, considering there is in some cases no clear precedent for how preventative therapies like PrEP are covered by health insurance~\cite{liu2014early}.
 
-One of the top words from the HIV-related topic, topic 13, was the term ``stigma", the term ``endstigma" was also found in topic 17.
+One of the top words from the HIV-related topic, topic 13, was the term ``stigma'', the term ``endstigma'' was also found in topic 17.
 Previous studies have shown a variety of stigmas associated and HIV have hampered prevention efforts~\cite{liu2014early}.
 Our observation of stigma related terms corroborates that there is some discussion of stigma in the context of HIV on Twitter.
-Public health professionals may be able use the prevalence of the term ``endstigma" as a way to monitor the efficacy of efforts to end HIV related stigmas.
+Public health professionals may be able use the prevalence of the term ``endstigma'' as a way to monitor the efficacy of efforts to end HIV related stigmas.
 
@@
 We identified the most positive, and the most negative tweets, by log probability, on our full dataset, and positive and negative tweets that specifically mention either PrEP or Truvada.
-We provide the text from the top three positive and negative tweets from each of the three datasets (Table 3, Table 4).
+We provide the text from the top three positive and negative tweets from each of the three datasets (Table~\ref{tbl:pos}, Table~\ref{tbl:neg}).
 
@@
 Category & Text\\ \hline
-General & ``RT TOPublicHealth The Works provides testing for HIV anonymous \& rapid test available . Call 416-392-0520 for more info"\\ \hline
-General & ``RT FCAA ejaforg announced 5.4 million in grants to support orgs addressing \#HIV in new \& innovative ways!"\\ \hline
-General & ``RT HillaryClinton A note on the fight against HIV and AIDS and the people who really started the conversation."\\ \hline
+General & ``RT TOPublicHealth The Works provides testing for HIV anonymous \& rapid test available . Call 416-392-0520 for more info''\\ \hline
+General & ``RT FCAA ejaforg announced 5.4 million in grants to support orgs addressing \#HIV in new \& innovative ways!''\\ \hline
+General & ``RT HillaryClinton A note on the fight against HIV and AIDS and the people who really started the conversation.''\\ \hline
 
-PrEP specific & ``He won't use condoms because intimacy means more than his health. but he's discovered PrEP. thank goodness."\\ \hline
-PrEP specific & ``PrEP Queensland Aids Council, \#HIV Foundation, Queensland."\\ \hline
-PrEP specific & ``RT JDatTheBody At the core of our programs is belief that young ppl can succeed in take PrEP for HIV prevention. \#NHPC2015"\\ \hline
+PrEP specific & ``He won't use condoms because intimacy means more than his health. but he's discovered PrEP. thank goodness.''\\ \hline
+PrEP specific & ``PrEP Queensland Aids Council, \#HIV Foundation, Queensland.''\\ \hline
+PrEP specific & ``RT JDatTheBody At the core of our programs is belief that young ppl can succeed in take PrEP for HIV prevention. \#NHPC2015''\\ \hline
 
-Truvada specific & ``RT CDC\_HIVAIDS Expanding testing, treatment, \& \#PrEP could prevent up to 185k new \#HIV infections"\\ \hline
-Truvada specific & ``Another reason 4 \#Ireland \& \#UK 2 immediately approve \#truvada \& \#PrEP 2 stop \#HIV infections . arleavitt AodhanORiordain MerchantsQuayIR"\\ \hline
-Truvada specific & ``RT EvanJPeterson For \#worldAIDSday my early \#PrEP arcticle in strangerslog, art by leviathanleague \#hiv \#truvada \#truvadawhore"\\ \hline
+Truvada specific & ``RT CDC\_HIVAIDS Expanding testing, treatment, \& \#PrEP could prevent up to 185k new \#HIV infections''\\ \hline
+Truvada specific & ``Another reason 4 \#Ireland \& \#UK 2 immediately approve \#truvada \& \#PrEP 2 stop \#HIV infections . arleavitt AodhanORiordain MerchantsQuayIR''\\ \hline
+Truvada specific & ``RT EvanJPeterson For \#worldAIDSday my early \#PrEP arcticle in strangerslog, art by leviathanleague \#hiv \#truvada \#truvadawhore''\\ \hline
 
 \hline\end{tabular}
+\label{tbl:pos}
 \end{table*}
@@
 Category & Text\\ \hline
-General & ``Also, how f***ing vile of Hillary to say. Reagan did f***ing NOTHING during the AIDS epidemic until it was too late. What a stupid old hag."\\ \hline
-General & ``I wonder why he beat her a** when she was tryna leave like she wasn't gone be running back when she found out she had HIV \& nobody want her"\\ \hline
-General & ``Aaannd. Hillary Clinton breathes a sigh of relief that Twitter has left its outrage of her AIDS comments behind to tend to Drumpf debacle."\\ \hline
+General & ``Also, how f***ing vile of Hillary to say. Reagan did f***ing NOTHING during the AIDS epidemic until it was too late. What a stupid old hag.''\\ \hline
+General & ``I wonder why he beat her a** when she was tryna leave like she wasn't gone be running back when she found out she had HIV \& nobody want her''\\ \hline
+General & ``Aaannd. Hillary Clinton breathes a sigh of relief that Twitter has left its outrage of her AIDS comments behind to tend to Drumpf debacle.''\\ \hline
 
-PrEP specific & ``RT gaston\_croupier \#Truvada patent's not expired yet but it is sold online as a generic drug? There's something rotten in internet \#PrEP h"\\ \hline
-PrEP specific & ``Equality\_MI Syph \& Hep C have gone up 550\% in Gay Men bc many feel tht bc they're on PrEP, they don't need condoms. HIV isn't the only STI."\\ \hline
-PrEP specific & ``Xaviom8 in interviews he says he was adherent. strain was highly resistant, and Truvada wouldn't have blocked it anyways. PrEP didn't fail."\\ \hline
+PrEP specific & ``RT gaston\_croupier \#Truvada patent's not expired yet but it is sold online as a generic drug? There's something rotten in internet \#PrEP h''\\ \hline
+PrEP specific & ``Equality\_MI Syph \& Hep C have gone up 550\% in Gay Men bc many feel tht bc they're on PrEP, they don't need condoms. HIV isn't the only STI.''\\ \hline
+PrEP specific & ``Xaviom8 in interviews he says he was adherent. strain was highly resistant, and Truvada wouldn't have blocked it anyways. PrEP didn't fail.''\\ \hline
 
-Truvada specific & ``not surprised at all that someone got HIV on truvada. people get pregnant on birth control. tomato-condoms are still important-tomahto"\\ \hline
-Truvada specific & ``Now reading that truvada does not protect against certain strains of the HIV virus. Yet people want to take that risk.."\\ \hline
-Truvada specific & ``I think I have conjunctivitis unless truvada cured it overnight cuz im not feeling as horrible today as last night"\\ \hline
+Truvada specific & ``not surprised at all that someone got HIV on truvada. people get pregnant on birth control. tomato-condoms are still important-tomahto''\\ \hline
+Truvada specific & ``Now reading that truvada does not protect against certain strains of the HIV virus. Yet people want to take that risk..''\\ \hline
+Truvada specific & ``I think I have conjunctivitis unless truvada cured it overnight cuz im not feeling as horrible today as last night''\\ \hline
 
 \hline\end{tabular}
+\label{tbl:neg}
 \end{table*}
 
-While the sentiment classification doesn't have perfect sentiment accuracy, we can see in general that the positive tweets are disseminating information about the efficacy and benefits of PrEP related preventions (Table 3).
+While the sentiment classification doesn't have perfect sentiment accuracy, we can see in general that the positive tweets are disseminating information about the efficacy and benefits of PrEP related preventions (Table~\ref{tbl:pos}).
 The positive tweets indicate that PrEP public health informational efforts have had some effect disseminating useful PrEP information on Twitter.
@@
 The negative tweets may be more important than the positive tweets to guide future public health policy corrections.
-The negative tweets contain concerns that Truvada may not block HIV transmission in all cases (Table 4).
+The negative tweets contain concerns that Truvada may not block HIV transmission in all cases (Table~\ref{tbl:neg}).
 There also seems to be concern that use of Truvada may increase the transmission of non-HIV STDs such as Hepatitis C because some PrEP users stop using condoms.
@@
 
-The last tweet in the positive tweets table (Table 3), referencing the hashtag ``\#truvadawhore", links to a blog article written by Evan Peterson titled ``The Case for PrEP, or How I Learned to Stop Worrying and Love HIV-Positive Guys"~\cite{caseforprep}.
+The last tweet in the positive tweets (Table~\ref{tbl:pos}), referencing the hashtag ``\#truvadawhore'', links to a blog article written by Evan Peterson titled ``The Case for PrEP, or How I Learned to Stop Worrying and Love HIV-Positive Guys''~\cite{caseforprep}.
 Evan is an HIV-negative individual who adheres to a daily PrEP regimen to protect himself from HIV.
 Evan finds that for himself, the side effects and inconveniences associated with taking daily Truvada are worth the protection, noting that he also practices safe sex, and gets tested regularly.
-Evan addresses the hashtag \#truvadawhore, which originated with a Huffington Post article titled ``Truvada Whores?"~\cite{truvadawhore} which expressed concern toward the increased sexual risk taking of some Truvada patients.
+Evan addresses the hashtag \#truvadawhore, which originated with a Huffington Post article titled ``Truvada Whores?''~\cite{truvadawhore} which expressed concern toward the increased sexual risk taking of some Truvada patients.
 Evan provides a rebuttal, noting that many HIV-negative individuals on Truvada, including himself and people he knows, are responsible and cautious about the risks they are taking.
@@
 We identified several notable trends.
-We found that PrEP discussion activity is increasing on social media, and also that people who mention PrEP also talk about general health, STDs, stigma, and politics.
+We found that PrEP discussion activity is increasing on Twitter, and also that people who mention PrEP also talk about general health, STDs, stigma, and politics.
 
-By picking out the most relevant tweets to PrEP, and also classifying tweets as positive or negative, we quickly identified a handful of specific tweets that highlight important parts of the online PrEP discussion.
+By picking out the tweets most relevant to PrEP, and classifying these tweets as positive or negative, we quickly identified core concepts important to the online PrEP discussion.
 We identified two important arguments for and against PrEP.
-One, as explored by blog author Steven Banning hypothesizes that PrEP adoption could lead to unintended, and unhealthy risk seeking behavior.
-The contrary hypothesis, described by blog author Evan Peterson, suggests that PrEP adoption is a product of healthy, responsible at-risk individuals who are gaining an effective form of HIV protection.
-These opposing arguments were identified automatically using large scale social media data.
-Further investigation and data analysis, of social media data together with other health data may be able to quantify PrEP and Truvada's effectiveness in the ongoing effort to prevent HIV infection.
+Blogger Steven Banning hypothesizes that PrEP adoption could lead to unintended consequences and unhealthy risk seeking behavior.
+The contrary hypothesis, described by blogger Evan Peterson, suggests that PrEP adherence is a product of healthy, responsible, at-risk individuals who are gaining an effective form of HIV protection.
+These opposing arguments were identified automatically using large scale data mining of social media.
+Further investigation and data analyses of social media data together with other health data may be able to quantify PrEP and Truvada's effectiveness in the ongoing effort to prevent HIV infection, as well as highlight possible strategies to maximize PrEP effectiveness.
 
 Future analyses may also take further advantage of the rich Twitter API.
-Rather than simple passive data collection, we could build a twitter bot to interact with HIV and PrEP-tweeters, to conduct a large scale social-media-based health survey.
+Rather than passively collecting data, intelligent chatbots could be deployed to interact with HIV and PrEP-tweeters.
+This would enable researchers to conduct large scale social-media-based health surveys and directly observe the dynamics of the discussion.
 
-%\end{document}  % This is where a 'short' article might terminate
+% conference papers do not normally have an appendix
 
-%ACKNOWLEDGMENTS are optional
-\section{Acknowledgments}
+% use section* for acknowledgment
+\section*{Acknowledgments}
 
-We would like to acknowledge the Twitter streaming API, which we used to collect HIV and PrEP related tweets over a 30 week period from late 2015 to early 2016.
-Also, we used the gensim python library for our working implementations of word2vec, doc2vec, LDA, and DTM.
-A repository containing the scripts used in this analysis (but no data) is available at https://github.com/quinngroup/sm\_w2v.
+The authors would like to thank many individuals for their consultations in context with the development of this study and its ongoing work.
 
+% trigger a \newpage just before the given reference
+% number - used to balance the columns on the last page
+% adjust value as needed - may need to be readjusted if
+% the document is modified later
+%\IEEEtriggeratref{8}
+% The "triggered" command can be changed if desired:
+%\IEEEtriggercmd{\enlargethispage{-5in}}
+
+% references section
+
+% can use a bibliography generated by BibTeX as a .bbl file
+% BibTeX documentation can be easily obtained at:
+% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
+% The IEEEtran BibTeX style support page is at:
+% http://www.michaelshell.org/tex/ieeetran/bibtex/
+\bibliographystyle{IEEEtran}
+% argument is your BibTeX string definitions and bibliography database(s)
+\bibliography{draft}
 %
-% The following two commands are all you need in the
-% initial runs of your .tex file to
-% produce the bibliography for the citations in your paper.
+% <OR> manually copy in the resultant .bbl file
+% set second argument of \begin to the number of references
+% (used to reserve space for the reference number labels box)
+%\begin{thebibliography}{1}
+%
+%\bibitem{IEEEhowto:kopka}
+%H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
+%  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
+%
+%\end{thebibliography}
 
-  % sigproc.bib is the name of the Bibliography in this case
-% You must have a proper ".bib" file
-%  and remember to run:
-% latex bibtex latex latex
-% to resolve all references
-%
-% ACM needs 'a single self-contained file'!
-%
-% no appendix for now...
-
-\bibliographystyle{abbrv}
-\bibliography{draft}
-
+% that's all folks
 \end{document}

### 2016-08-08 IEEEtran/bare_conf.tex
Have review comments from Tim and Jane and Patrick, ready for final revision with Shannon

@@
 % affiliations
-%\author{\IEEEauthorblockN{Michael Shell}
-%\IEEEauthorblockA{School of Electrical and\\Computer Engineering\\
-%Georgia Institute of Technology\\
-%Atlanta, Georgia 30332--0250\\
-%Email: http://www.michaelshell.org/contact.html}
-%\and
+\author{\IEEEauthorblockN{Patrick Breen}
+\IEEEauthorblockA{Institute of Bioinformatics\\
+University of Georgia\\
+Athens, Georgia\\
+Email: pbreen@uga.edu}
+\and
+\IEEEauthorblockN{Jane Kelly}
+\IEEEauthorblockA{ Georgia Department of \\Public Health\\
+Atlanta, Georgia\\
+Email: Jane.Kelly@dph.ga.gov}
+\and
+\IEEEauthorblockN{Timothy Heckman}
+\IEEEauthorblockA{College of Public Health\\
+University of Georgia\\
+Athens, Georgia\\
+Email: heckman@uga.edu}
+\and
+\IEEEauthorblockN{Shannon Quinn}
+\IEEEauthorblockA{Department of \\Computer Science\\
+University of Georgia\\
+Athens, Georgia\\
+Email: squinn@cs.uga.edu}
+}
 %\IEEEauthorblockN{Homer Simpson}
@@
 
-We trained a word2vec model, and queried for the top 10 word-vectors related to the term PrEP (Table~\ref{tbl:w2v}).
+We trained a word2vec model on the filtered dataset of 624,569 tweets, and queried for the top 10 word-vectors related to the term PrEP (Table~\ref{tbl:w2v}).
 We found several HIV/AIDS related events, WorldAIDSDay, HLM2016AIDS, ICASA2015, as well as the PrEP drug Truvada, and the term HIV.
@@
 Next we sought to identify some temporal trends in PrEP related trends.
-We used Dynamic Topic Modeling (DTM) to identify how certain topics change over time.
+We used Dynamic Topic Modeling (DTM) on our tweet corpus to identify how certain topics change over time.
 We specified 10 topics and used each week's worth of tweets, over a 30 week period from the 47th week of 2015 to the 14th week of 2016, as our time points.

### 2016-08-15 IEEEtran/bare_conf.tex
modified acknowledgements

@@
 
-The authors would like to thank many individuals for their consultations in context with the development of this study and its ongoing work.
+The authors would like to thank our collaborators in the Georgia HIV research community, including individuals at The University of Georgia, The Center for Disease control, Oak Ridge National Laboratory, Emory University, The Georgia Department of Public Health and the Kaiser Family Foundation.
 
